### 2020-01-11 docs/build/assets/AlgebraicLoop/brokenloop.tex
Added assets for docs.

\documentclass[convert={density=900,size=1080x800,outext=.png}]{standalone}
\usepackage{tikz}
\usetikzlibrary{calc, positioning}
\usetikzlibrary{arrows.meta}
\usetikzlibrary{matrix}
\usetikzlibrary{shadows}
\usepgflibrary{shapes.misc}
\usepgflibrary{{shapes.geometric}}
\usetikzlibrary{arrows,positioning,shapes}

\pgfdeclarelayer{shadow} 
\pgfsetlayers{shadow,main}
\def\shadowradius{3pt}

\def\lw{2mm}        % Arrow line width
\def\mw{2cm}        % Minimum width of component
\def\mh{1.75cm}     % Minimum height of component
\def\trianglecoordinate{2mm}    % Starting coordinate clock input triangle of components

\newcommand\drawshadowbis[1]{
    \begin{pgfonlayer}{shadow}
        \fill[inner color=black,outer color=white] ($(#1.south west)$) circle (\shadowradius);
        \fill[inner color=black ,outer color=white] ($(#1.north west)$) circle (\shadowradius);
        \fill[inner color=black ,outer color=white] ($(#1.south east)$) circle (\shadowradius);
        \fill[inner color=black,outer color=white] ($(#1.north east)$) circle (\shadowradius);
        \fill[ top color=black, bottom color=white] ($(#1.south west)+((0,-\shadowradius)$) rectangle ($(#1.south east)$);
        \fill[left color=black,right color=white] ($(#1.south east)$) rectangle ($(#1.north east)+((\shadowradius,0)$);
        \fill[bottom color=black,top color=white] ($(#1.north west)$) rectangle ($(#1.north east)+((0,\shadowradius)$);
        \fill[right color=black,left color=white] ($(#1.south west)$) rectangle ($(#1.north west)+(-\shadowradius,0)$);
    \end{pgfonlayer}
    }

\tikzset{
    border/.style = { 
        draw, rectangle, minimum width=2cm, minimum height=1.5cm, thick
    },
    pics/Component/.style n args = {2}{
        code = {
            \node [border, align=center](-edge){#1};
            \draw[thick] ([xshift=\trianglecoordinate] -edge.south) -- ([yshift=\trianglecoordinate] -edge.south);
            \draw[thick] ([xshift=-\trianglecoordinate] -edge.south) -- ([yshift=\trianglecoordinate] -edge.south);
            \draw[thick] (-edge.south) |- ++(-3mm, -4mm) node[xshift=-2mm, yshift=-1mm] {#2}; 
    }}
    }

\begin{document}
    \begin{tikzpicture}[every node/.style={font=\Large}]
        % Place the blocks 
        \draw pic (b1) {Component={Static\\System}{t}};
        \draw(3, 0) pic (b2) {Component={Dynamical\\System I}{t}};
        \draw(3, -2.5) pic (b3) {Component={Dynamical\\System II}{t}};
        \draw(0, -2.5) pic (b4) {Component={Memory}{t}};
        % Glow the blocks
        \drawshadowbis{b1-edge};
        \drawshadowbis{b2-edge};
        \drawshadowbis{b3-edge};
        \drawshadowbis{b4-edge};
        \begin{scope}[line width=1.5mm, >={Triangle[width=3mm,length=3mm]}]
            \draw[->] ([yshift=2mm, xshift=-1cm] b1-edge.west) -- ([yshift=2mm] b1-edge.west);
            \draw[->] (b1-edge.east) -- (b2-edge.west);
            \draw (b2-edge.east) -- ++(0.5cm, 0cm) coordinate (a);
            \draw[->] (a) -- ++(0.5cm, 0cm);
            \draw[->] (a) |- (b3-edge.east);
            \draw[<-] ([yshift=-2mm] b1-edge.west) -- ++(-0.5cm, 0cm) coordinate (b);
            \draw[-] ([yshift=0.75mm] b) |- (b4-edge.west);
            \draw[->] (b3-edge.west) |- (b4-edge.east);
        \end{scope}
    \end{tikzpicture}
\end{document}

### 2020-01-11 docs/build/assets/Components/components.tex
Added assets for docs.

--- 2020-01-11 docs/build/assets/AlgebraicLoop/brokenloop.tex
@@
 
-\def\lw{2mm}        % Arrow line width
+\def\lw{1mm}        % Arrow line width
 \def\mw{2cm}        % Minimum width of component
@@
     border/.style = { 
-        draw, rectangle, minimum width=2cm, minimum height=1.5cm, thick
+        draw, rectangle, minimum width=2.5cm, minimum height=2cm, thick
     },
-    pics/Component/.style n args = {2}{
+    pics/Component/.style n args={3}{
         code = {
@@
             \draw[thick] (-edge.south) |- ++(-3mm, -4mm) node[xshift=-2mm, yshift=-1mm] {#2}; 
+            \draw (-edge.south) node [yshift=-0.75*\mh, align=left, font=\large] {#3};
     }}
@@
 \begin{document}
-    \begin{tikzpicture}[every node/.style={font=\Large}]
+    \begin{tikzpicture}[every node/.style={font={\large}}]
         % Place the blocks 
-        \draw pic (b1) {Component={Static\\System}{t}};
-        \draw(3, 0) pic (b2) {Component={Dynamical\\System I}{t}};
-        \draw(3, -2.5) pic (b3) {Component={Dynamical\\System II}{t}};
-        \draw(0, -2.5) pic (b4) {Component={Memory}{t}};
+        \matrix (m) [matrix of nodes, ampersand replacement=\&, column sep = 2cm, row sep = 0.5cm, 
+            nodes={anchor=center}]{
+        \draw pic (b1) {Component={Source}{t}{$y=g(t)$}};    
+        \& 
+        \draw pic (b3) {Component={Sink}{t}{}};  
+        \&
+        \draw pic (b5) {Component={StaticSystem}{t}{$y=g(u, t)$}};    
+        \\
+        \draw pic (b9) {Component={DiscreteSistem}{k}{$x_{k+1}=f(x_k, u_k, k)$\\$\hspace*{0.4cm}y_k=g(x_k, u_k, k)$}};
+        \& 
+        \draw pic (b7) {Component={ODESystem}{t}{$\dot{x}=f(x,u,t)$\\$y=g(x,u,t)$}};
+        \& 
+        \draw pic (b2) {Component={DAESystem}{t}{$0=f(dx,x,u,t)$\\$y=g(x,u,t)$}}; 
+        \\
+        \draw pic (b4) {Component={RODESystem}{t}{$dx=f(x,u,t,W_t)dt$\\$\hspace*{0.2cm}y=g(x,u,t)$}};
+        \& 
+        \draw pic (b6) {Component={SDESystem}{t}{$dx=f(x,u,t)dt+h(x,u,t)dW_t$\\$\hspace*{0.2cm}y=g(x,u,t)$}};
+        \&
+        \draw pic (b8) {Component={DDESystem}{t}{$\dot{x}=f(x,x_\tau,u,t)$\\$y=f(x,u,t)$}}; 
+        \\
+        };
         % Glow the blocks
-        \drawshadowbis{b1-edge};
-        \drawshadowbis{b2-edge};
-        \drawshadowbis{b3-edge};
-        \drawshadowbis{b4-edge};
-        \begin{scope}[line width=1.5mm, >={Triangle[width=3mm,length=3mm]}]
-            \draw[->] ([yshift=2mm, xshift=-1cm] b1-edge.west) -- ([yshift=2mm] b1-edge.west);
-            \draw[->] (b1-edge.east) -- (b2-edge.west);
-            \draw (b2-edge.east) -- ++(0.5cm, 0cm) coordinate (a);
-            \draw[->] (a) -- ++(0.5cm, 0cm);
-            \draw[->] (a) |- (b3-edge.east);
-            \draw[<-] ([yshift=-2mm] b1-edge.west) -- ++(-0.5cm, 0cm) coordinate (b);
-            \draw[-] ([yshift=0.75mm] b) |- (b4-edge.west);
-            \draw[->] (b3-edge.west) |- (b4-edge.east);
+        \foreach \x in {1, 2, ..., 9}{
+            \drawshadowbis{b\x-edge};
+        }
+        \begin{scope}[line width=\lw, >={Triangle[width=2mm,length=2mm]}]
+            \foreach \x in {1, 2, 4, 5, 6, 7, 8, 9}{
+                \draw[line width = \lw, ->] (b\x-edge.east) -- ++(0.5cm, 0cm) node[anchor=west]{$y$};
+            }
+            \foreach \x in {2, 3, 4, 5, 6, 7, 8, 9}{
+                \draw[line width = \lw, ->] ([xshift=-0.5cm] b\x-edge.west) node[anchor=east]{$u$} -- (b\x-edge.west);
+            }
         \end{scope}

### 2020-01-11 docs/build/assets/SubsystemModel/subsystem.tex
Added assets for docs.

\documentclass[convert={density=900,size=1080x800,outext=.png}]{standalone}
\usepackage[utf8]{inputenc}
\usepackage{tikz}

\usetikzlibrary{calc, positioning}
\usetikzlibrary{arrows.meta}
\usetikzlibrary{matrix}
\usetikzlibrary{shadows}
\usepgflibrary{shapes.misc}
\usepgflibrary{{shapes.geometric}}

\pgfdeclarelayer{shadow} 
\pgfsetlayers{shadow,main}
\def\shadowradius{3pt}

\def\mw{2cm}
\def\mh{1.75cm}
\def\trianglecoordinate{2mm}

\newcommand\drawshadowbis[1]{
    \begin{pgfonlayer}{shadow}
        \fill[inner color=black,outer color=white] ($(#1.south west)$) circle (\shadowradius);
        \fill[inner color=black ,outer color=white] ($(#1.north west)$) circle (\shadowradius);
        \fill[inner color=black ,outer color=white] ($(#1.south east)$) circle (\shadowradius);
        \fill[inner color=black,outer color=white] ($(#1.north east)$) circle (\shadowradius);
        \fill[ top color=black, bottom color=white] ($(#1.south west)+((0,-\shadowradius)$) rectangle ($(#1.south east)$);
        \fill[left color=black,right color=white] ($(#1.south east)$) rectangle ($(#1.north east)+((\shadowradius,0)$);
        \fill[bottom color=black,top color=white] ($(#1.north west)$) rectangle ($(#1.north east)+((0,\shadowradius)$);
        \fill[right color=black,left color=white] ($(#1.south west)$) rectangle ($(#1.north west)+(-\shadowradius,0)$);
    \end{pgfonlayer}
    }

\tikzstyle{component} = [draw, fill=white, minimum width=\mw, minimum height=\mh, align=center]

\tikzset{
    border/.style = { 
        draw, rectangle, minimum width=\mw, minimum height=\mh, thick, align=center
    },
    Component/.pic = {
        \node [border, font=\large](-edge){#1}; 
        \draw[thick] ([xshift=\trianglecoordinate] -edge.south) -- ([yshift=\trianglecoordinate] -edge.south);
        \draw[thick] ([xshift=-\trianglecoordinate] -edge.south) -- ([yshift=\trianglecoordinate] -edge.south);
        \draw[thick] (-edge.south) |- ++(-3mm, -4mm) node[xshift=-2mm, yshift=-1mm] {T}; 
    },
}

\tikzset{
    clockborder/.style = { 
        trapezium, trapezium angle=60, minimum width=1cm, draw, very thick
    },
    Clock/.pic = {
        \node [clockborder, shape border rotate=-180](-clockedge){#1};
        \draw[very thick] (-clockedge.east) -- ++(2cm, 0cm);
        \def\sft{0.5}
        \foreach \x in {0, 0.5, 1, 1.5}{
            \draw[very thick] (\x + \sft, 0.1) -| ++(0.25cm, 0.25cm) -| ++ (0.25cm, -0.25cm);
        }
    },
}

\begin{document}
    \begin{tikzpicture}[every node/.style={font=\large}]
        % Place the blocks 
        \matrix (m) [matrix of nodes, ampersand replacement=\&, column sep = 1.5cm, row sep = 0.25cm, nodes={anchor=center}]{
             \& \draw pic (kaynak2) {Component={Source II}}; \& \&   \\[-1cm]
            \draw pic (kaynak1) {Component={Source I}};    \& \& \draw pic (statiksistem1) {Component={StaticSystem I}}; \& \draw pic (statiksistem2) {Component={StaticSystem II}}; \\
            \draw pic (kutuk1) {Component={Sink I}}; \& \& \& \draw pic (kutuk2) {Component={Sink II}}; \\
        };
        % Glow the blocks
        \foreach \x in {kaynak1, kaynak2, kutuk1, kutuk2, statiksistem1, statiksistem2}{
            \drawshadowbis{\x-edge};
        }
        % Draw connections 
        \begin{scope}[line width=2mm, >={Triangle[width=4mm,length=4mm]}]
            \draw[-] (kaynak1-edge.east) -- ++(0.75cm, 0cm) coordinate(a);
            \draw[->] ([yshift=1mm] a) |- (kutuk1-edge.east);
            \draw[->] (a) |- ([yshift=-0.25cm] statiksistem1-edge.west);
            \draw[-] (kaynak2-edge.east) -- ++(0.5cm, 0cm) coordinate(b);
            \draw[->] ([yshift=1mm] b) |- ([yshift=0.25cm] statiksistem1-edge.west);
            \draw[->] (statiksistem1-edge.east) |- (statiksistem2-edge.west);
            \draw[-] (statiksistem2-edge.east) -- ++(0.5cm, 0cm) coordinate(c);
            \draw[->] ([yshift=1mm] c) |- (kutuk2-edge.east);
        \end{scope}

        % Draw rectangle for subsystem 
        \draw[thick, dashed] ([xshift=-0.25cm, yshift=0.25cm] kaynak2-edge.north west) rectangle ([xshift=0.25cm, yshift=-0.75cm] statiksistem2-edge.south east);
        \draw (statiksistem2-edge.north west) node[yshift=1.75cm, xshift=1cm]{SubSystem};

        % \Place clock 
        \begin{scope}[shift={(-5.75cm, -4.5cm)}]
            \draw pic(clk) {Clock={T}} ;
        \end{scope}

        %  Draw rectangle 
        \draw[dashed, thick] ([xshift=-0.75*\mw, yshift=-0.25*\mh] clk-clockedge.south west) rectangle ([xshift=0.5*\mw, yshift=1.5*\mh] statiksistem2-edge.north east);
        \draw (clk-clockedge.east) node[yshift=0*\mh, xshift=6*\mw]{Model};
    \end{tikzpicture}
\end{document}

### 2020-01-11 docs/src/assets/Model/model.tex
Added assets for docs.

--- 2020-01-11 docs/build/assets/SubsystemModel/subsystem.tex
@@
 \documentclass[convert={density=900,size=1080x800,outext=.png}]{standalone}
-\usepackage[utf8]{inputenc}
 \usepackage{tikz}
@@
     Component/.pic = {
-        \node [border, font=\large](-edge){#1}; 
+        \node [border](-edge){#1}; 
         \draw[thick] ([xshift=\trianglecoordinate] -edge.south) -- ([yshift=\trianglecoordinate] -edge.south);
@@
         % Place the blocks 
-        \matrix (m) [matrix of nodes, ampersand replacement=\&, column sep = 1.5cm, row sep = 0.25cm, nodes={anchor=center}]{
-             \& \draw pic (kaynak2) {Component={Source II}}; \& \&   \\[-1cm]
-            \draw pic (kaynak1) {Component={Source I}};    \& \& \draw pic (statiksistem1) {Component={StaticSystem I}}; \& \draw pic (statiksistem2) {Component={StaticSystem II}}; \\
-            \draw pic (kutuk1) {Component={Sink I}}; \& \& \& \draw pic (kutuk2) {Component={Sink II}}; \\
+        \matrix (m) [matrix of nodes, ampersand replacement=\&, column sep = 1.5cm, row sep = -1cm]{
+                                            \& \draw pic (b1) {Component={B1}}; \&                                  \\
+        \draw pic (b2) {Component={B2}};    \&                                  \& \draw pic (b3) {Component={B3}}; \\
+                                            \& \draw pic (b4) {Component={B4}}; \&                                  \\[1.25cm]
+                                            \& \draw pic (b5) {Component={B5}}; \&                                  \\
         };
         % Glow the blocks
-        \foreach \x in {kaynak1, kaynak2, kutuk1, kutuk2, statiksistem1, statiksistem2}{
-            \drawshadowbis{\x-edge};
+        \foreach \x in {1, 2, 3, 4, 5}{
+            \drawshadowbis{b\x-edge};
         }
@@
         \begin{scope}[line width=2mm, >={Triangle[width=4mm,length=4mm]}]
-            \draw[-] (kaynak1-edge.east) -- ++(0.75cm, 0cm) coordinate(a);
-            \draw[->] ([yshift=1mm] a) |- (kutuk1-edge.east);
-            \draw[->] (a) |- ([yshift=-0.25cm] statiksistem1-edge.west);
-            \draw[-] (kaynak2-edge.east) -- ++(0.5cm, 0cm) coordinate(b);
-            \draw[->] ([yshift=1mm] b) |- ([yshift=0.25cm] statiksistem1-edge.west);
-            \draw[->] (statiksistem1-edge.east) |- (statiksistem2-edge.west);
-            \draw[-] (statiksistem2-edge.east) -- ++(0.5cm, 0cm) coordinate(c);
-            \draw[->] ([yshift=1mm] c) |- (kutuk2-edge.east);
+            \def\shiftamount{0.5mm};
+            \draw[-] (b2-edge.east) -- ++(0.5cm, 0cm) coordinate(a);
+            \draw[-] (a) -- node[midway, anchor=west]{L1} ++(0, 0.5*\mh) coordinate(b);
+            \draw[-] (a) -- node[midway, anchor=west]{L2} ++(0cm, -0.5*\mh) coordinate(c);
+            \draw[->] (b) |- (b1-edge.west);
+            \draw[->] (c) |- ([yshift=0.25cm] b4-edge.west);
+            \draw[-] (b1-edge.east) -- ++(0.4*\mw, 0cm) coordinate(d);
+            \draw[-] (b4-edge.east) -- ++(0.4*\mw, 0cm) coordinate(e);
+            \draw[-] ([yshift=1mm] d) -- node[midway, anchor=east]{L3} ++(0cm, -0.7*\mh) coordinate(f);
+            \draw[-] ([yshift=-1mm] e) -- node[midway, anchor=east]{L4} ++(0cm, 0.7*\mh) coordinate(g);
+            \draw[->] ([yshift=\shiftamount] f) |- ([yshift=2mm] b3-edge.west);
+            \draw[->] ([yshift=-\shiftamount] g) |- ([yshift=-2mm] b3-edge.west);
+            \draw (b5-edge.west) -- ++(-1cm, 0cm) coordinate (h);
+            \draw[->] ([yshift=-1mm] h) |- node[midway, anchor=east, yshift=-1.25cm]{L6}  ([yshift=-0.25cm] b4-edge.west);
+            \draw[->] ([yshift=1mm] g) |- node[midway, anchor=east, yshift=1.25cm]{L5} (b5-edge.east);
         \end{scope}
 
-        % Draw rectangle for subsystem 
-        \draw[thick, dashed] ([xshift=-0.25cm, yshift=0.25cm] kaynak2-edge.north west) rectangle ([xshift=0.25cm, yshift=-0.75cm] statiksistem2-edge.south east);
-        \draw (statiksistem2-edge.north west) node[yshift=1.75cm, xshift=1cm]{SubSystem};
-
         % \Place clock 
-        \begin{scope}[shift={(-5.75cm, -4.5cm)}]
+        \begin{scope}[shift={(-4.25cm, -4cm)}]
             \draw pic(clk) {Clock={T}} ;
@@
         %  Draw rectangle 
-        \draw[dashed, thick] ([xshift=-0.75*\mw, yshift=-0.25*\mh] clk-clockedge.south west) rectangle ([xshift=0.5*\mw, yshift=1.5*\mh] statiksistem2-edge.north east);
-        \draw (clk-clockedge.east) node[yshift=0*\mh, xshift=6*\mw]{Model};
+        \draw[dashed, thick] ([xshift=-0.25*\mw, yshift=-0.25*\mh] clk-clockedge.south west) rectangle ([xshift=2*\mw, yshift=0.25*\mh] b1-edge.north east);
+        \draw (b3-edge.south) node[yshift=-2.75*\mh, xshift=0.4*\mw]{Model};
     \end{tikzpicture}

### 2020-04-29 docs/build/assets/TaskForComponents/tasks.tex
Revised docs.

--- 2020-01-11 docs/build/assets/AlgebraicLoop/brokenloop.tex
@@
 \documentclass[convert={density=900,size=1080x800,outext=.png}]{standalone}
+\usepackage[utf8]{inputenc}
 \usepackage{tikz}
@@
     border/.style = { 
-        draw, rectangle, minimum width=2cm, minimum height=1.5cm, thick
+        draw, circle, minimum width=2cm, ultra thick
     },
-    pics/Component/.style n args = {2}{
+    pics/Task/.style={
         code = {
             \node [border, align=center](-edge){#1};
-            \draw[thick] ([xshift=\trianglecoordinate] -edge.south) -- ([yshift=\trianglecoordinate] -edge.south);
-            \draw[thick] ([xshift=-\trianglecoordinate] -edge.south) -- ([yshift=\trianglecoordinate] -edge.south);
-            \draw[thick] (-edge.south) |- ++(-3mm, -4mm) node[xshift=-2mm, yshift=-1mm] {#2}; 
     }}
@@
     \begin{tikzpicture}[every node/.style={font=\Large}]
-        % Place the blocks 
-        \draw pic (b1) {Component={Static\\System}{t}};
-        \draw(3, 0) pic (b2) {Component={Dynamical\\System I}{t}};
-        \draw(3, -2.5) pic (b3) {Component={Dynamical\\System II}{t}};
-        \draw(0, -2.5) pic (b4) {Component={Memory}{t}};
-        % Glow the blocks
-        \drawshadowbis{b1-edge};
-        \drawshadowbis{b2-edge};
-        \drawshadowbis{b3-edge};
-        \drawshadowbis{b4-edge};
-        \begin{scope}[line width=1.5mm, >={Triangle[width=3mm,length=3mm]}]
-            \draw[->] ([yshift=2mm, xshift=-1cm] b1-edge.west) -- ([yshift=2mm] b1-edge.west);
-            \draw[->] (b1-edge.east) -- (b2-edge.west);
-            \draw (b2-edge.east) -- ++(0.5cm, 0cm) coordinate (a);
-            \draw[->] (a) -- ++(0.5cm, 0cm);
-            \draw[->] (a) |- (b3-edge.east);
-            \draw[<-] ([yshift=-2mm] b1-edge.west) -- ++(-0.5cm, 0cm) coordinate (b);
-            \draw[-] ([yshift=0.75mm] b) |- (b4-edge.west);
-            \draw[->] (b3-edge.west) |- (b4-edge.east);
+        \draw (0, 0) pic (t1) {Task={B1}};
+        \draw (2.5, 0) pic (t2) {Task={B1}};
+        \draw (6.5, 0) pic (t3) {Task={B2}};
+        \draw (9,0) pic (t4) {Task={B2}};
+        \begin{scope}[line width = \lw, >={Triangle[width=4mm,length=4mm]}, ->]
+            \draw ([xshift=-1.25cm] t1-edge.west) -- node[midway, anchor=south]{L1} (t1-edge.west);
+            \draw (t2-edge.east) -- node[midway, anchor=south]{L2}  (t3-edge.west);
+            \draw[line width = \lw, ->] (t4-edge.east) -- node[midway, anchor=south]{L3} ([xshift=1cm] t4-edge.east);
         \end{scope}

### 2020-04-29 build/Jusdl.jl

@@ -1,16 +1,0 @@
-# 
-# Julia System Desciption Language
-# 
-module Jusdl
-
-# Required packages
-using Reexport
-
-# Include the submodules
-include("utilities/Utilities.jl")
-# include("connections/Connections.jl")
-# include("plugins/Plugins.jl")
-# include("components/Components.jl")
-# include("models/Models.jl")
-
-end  # module

### 2020-04-29 build/components/base/genericfields.jl

@@ -1,81 +1,0 @@
-# This file contains the generic fields of some types in Components module.
-
-import ....Jusdl.Utilities: Callback
-import ....Jusdl.Connections: Bus, Link
-
-
-@def generic_source_fields begin
-    outputfunc::OF
-    output::OB
-    trigger::T
-    handshake::H
-    callbacks::Vector{Callback}
-    id::UUID
-end
-
-@def generic_system_fields begin
-    input::IB
-    output::OB
-    trigger::T
-    handshake::H
-    callbacks::Vector{Callback}
-    id::UUID
-end
-
-@def generic_sink_fields begin
-    input::IB
-    databuf::DB
-    timebuf::TB
-    plugin::P
-    trigger::T 
-    handshake::H
-    callbacks::Vector{Callback}
-    id::UUID
-end
-
-@def generic_static_system_fields begin
-    @generic_system_fields
-    outputfunc::OF 
-end
-
-@def generic_dynamic_system_fields begin 
-    @generic_system_fields 
-    statefunc::SF 
-    outputfunc::OF 
-    state::ST 
-    inputval::IV
-    t::Float64
-    solver::S
-end
-
-################# Deprecated
-
-# @def generic_discrete_system_fields begin
-#     @generic_dynamic_system_fields
-# end
-
-# @def generic_ode_system_fields begin
-#     @generic_dynamic_system_fields
-# end
-
-# @def generic_dae_system_fields begin
-#     @generic_dynamic_system_fields
-#     stateder::ST
-#     diffvars::D
-# end
-
-# @def generic_rode_system_fields begin
-#     @generic_dynamic_system_fields
-#     noise::N
-# end
-
-# @def generic_sde_system_fields begin
-#     @generic_dynamic_system_fields
-#     noise::N
-# end
-
-# @def generic_dde_system_fields begin
-#     @generic_dynamic_system_fields
-#     history::H 
-# end
-

### 2020-04-29 build/components/base/utils.jl

@@ -1,64 +1,0 @@
-# This file includes the utility functions
-
-# """
-#     @def(name, code)
-
-# Evaluates the `code` with the `name`. This is basically used to define copy-paste code. 
-
-# # Example
-# ```jldoctest
-# julia> @def fields begin
-#     x::Int
-#     y::Float64
-#     end
-# @fields (macro with 1 method)
-
-# julia> struct Dummy
-#     @fields
-#     z::Symbol
-#     end
-
-# julia> fieldnames(Dummy)
-# (:x, :y, :z)
-
-# julia> 
-# ```
-# """
-macro def(name, code)
-    quote
-        macro $(esc(name))()
-            esc($(Meta.quot(code)))
-        end
-    end
-end
-
-# """
-#     @def_with_inputs name args code
-
-# Defines the macro `name` with arguments `args` and with the code `code`. See the examples.
-
-# Example
-# ```jldoctest
-# julia> @def_with_args myname (x, y) begin
-#            println("x ", x, " y ", y)
-#        end
-# @myname (macro with 1 method)
-
-# julia> x, y = 4,5
-# (4, 5)
-
-# julia> @myname x y
-# x 4 y 5
-
-# julia> 
-# end
-# ```
-# """
-macro def_with_args(name, args, code)
-    quote
-        macro $(esc(name))($(args)...)
-            esc($(Meta.quot(code)))
-        end
-    end
-end
-

### 2020-04-29 build/components/sinks/printer.jl

@@ -1,26 +1,0 @@
-# This file includes the printers
-
-import Base.print
-
-
-mutable struct Printer{IB, DB, TB, P, T, H} <: AbstractSink
-    @generic_sink_fields
-    function Printer(input::Bus{Union{Missing, T}}, buflen=64, plugin=nothing) where T
-        # Construct the buffers
-        timebuf = Buffer(buflen)
-        databuf = Buffer(Vector{T}, buflen)
-        trigger = Link()
-        handshake = Link{Bool}()
-        addplugin(
-            new{typeof(input), typeof(databuf), typeof(timebuf), typeof(plugin), typeof(trigger),
-            typeof(handshake)}(input, databuf, timebuf, plugin, trigger, handshake, Callback[], uuid4()), print)
-    end
-end
-
-show(io::IO, printer::Printer) = print(io, "Printer(nin:$(length(printer.input)))")
-
-##### Printer reading and writing
-print(printer::Printer, td, xd) = print("For time", "[", td[1], " ... ", td[end], "]", " => ", xd, "\n")
-
-open(printer::Printer) = printer
-close(printer::Printer) =  printer

### 2020-04-29 build/components/sinks/scope.jl

@@ -1,35 +1,0 @@
-# This file includes the scope
-
-
-mutable struct Scope{IB, DB, TB, P, T, H, PLT} <: AbstractSink
-    @generic_sink_fields
-    plt::PLT
-    function Scope(input::Bus{Union{Missing, T}}, buflen::Int=64, plugin=nothing, args...; kwargs...) where T
-        # Construct the plot 
-        plt = plot(args...; kwargs...)
-        foreach(sp -> plot!(sp, zeros(1)), plt.subplots)  # Plot initialization 
-        # Construct the buffers
-        timebuf = Buffer(buflen)
-        databuf = Buffer(Vector{T}, buflen)
-        trigger = Link()
-        handshake = Link{Bool}()
-        addplugin(
-            new{typeof(input), typeof(databuf), typeof(timebuf), typeof(plugin), typeof(trigger), typeof(handshake), 
-            typeof(plt)}(input, databuf, timebuf, plugin, trigger, handshake, Callback[], uuid4(), plt), update!)
-    end
-end
-
-show(io::IO, scp::Scope) = print(io, "Scope(nin:$(length(scp.input)))")
-
-clear(sp::Plots.Subplot) = popfirst!(sp.series_list)  # Delete the old series 
-function update!(s::Scope, x, yi)
-    y = collect(hcat(yi...)')
-    plt = s.plt
-    subplots = plt.subplots
-    clear.(subplots)
-    plot!(plt, x, y, xlim=(x[1], x[end]), label="")  # Plot the new series
-    gui()
-end
-
-close(sink::Scope) = closeall()
-open(sink::Scope) = Plots.isplotnull() ? (@warn "No current plots") : gui()

### 2020-04-29 build/components/sources/Sources.jl

@@ -1,18 +1,0 @@
-# This file includes the sources of Jusdl
-
-@reexport module Sources
-
-using UUIDs
-import ..Components.Base: AbstractSource
-import ....Jusdl.Utilities: Callback
-import ....Jusdl.Connections: Link, Bus
-import Base.show
-
-export Clock, isrunning, ispaused, isoutoftime, set!, stop!
-export FunctionGenerator, SinewaveGenerator, DampedSinewaveGenerator, SquarewaveGenerator, TriangularwaveGenerator, 
-    ConstantGenerator, RampGenerator, StepGenerator, ExponentialGenerator, DampedExponentialGenerator
-
-include("clock.jl")
-include("generators.jl")
-
-end  # module

### 2020-04-29 build/components/sources/clock.jl

@@ -1,69 +1,0 @@
-# This file constains the Clock tools for time synchronization of DsSimulator.
-
-import Base: iterate, take!, length
-
-Generator(t0::Real, dt::Real, tf::Real) = 
-    Channel(channel -> foreach(t -> put!(channel, t), t0:dt:tf), ctype=promote_type(typeof(t0), typeof(dt), typeof(tf)))
-
-mutable struct Clock{T<:Real}
-    t::T
-    dt::T
-    tf::T
-    generator::Channel{T}
-    paused::Bool
-    callbacks::Vector{Callback}
-    id::UUID
-end
-Clock(t::Real, dt::Real, tf::Real) = 
-    Clock(promote(t, dt, tf)..., Channel{promote_type(typeof(t),typeof(dt),typeof(tf))}(0), false, Callback[], uuid4())
-
-show(io::IO, clk::Clock) = print(io, 
-    "Clock(t:$(clk.t), dt:$(clk.dt), tf:$(clk.tf), paused:$(clk.paused), isrunning:$(isrunning(clk)))")
-
-##### Reading from clock
-function take!(clk::Clock)
-    if ispaused(clk)
-        @warn "Clock is paused."
-        return clk.t
-    end
-    if isoutoftime(clk)
-        @warn "Clock is out of time."
-        return clk.t
-    end
-    if !isrunning(clk)
-        @warn "Clock is not running."
-        return clk.t
-    end
-    clk.t = take!(clk.generator)
-    clk.callbacks(clk)
-    clk.t
-end
-
-##### Clock state check 
-isrunning(clk::Clock) = isready(clk.generator)
-ispaused(clk::Clock) = clk.paused
-isoutoftime(clk::Clock) = clk.t >= clk.tf
-
-##### Controlling clock.
-function set!(clk::Clock, generator::Channel=Generator(clk.t, clk.dt, clk.tf)) 
-    clk.generator = generator
-    clk.paused=false
-    clk
-end
-function set!(clk::Clock, t::Real, dt::Real, tf::Real)
-    set!(clk, Generator(t, dt, tf))
-    clk.t = t 
-    clk.dt = dt 
-    clk.tf = tf
-    clk
-end
-function stop!(clk::Clock)
-    set!(clk, Channel{typeof(clk.t)}(0)) 
-    clk
-end
-
-##### Iterating clock.
[…]

### 2020-04-29 build/components/sources/generators.jl

@@ -1,209 +1,0 @@
-# This file contains the function generator tools to drive other tools of DsSimulator.
-
-
-import ..Components.Base: @generic_source_fields
-
-
-##### Generic Function Generator
-mutable struct FunctionGenerator{OF, OB, T, H} <: AbstractSource
-    @generic_source_fields
-    function FunctionGenerator(outputfunc)
-        out = outputfunc(0.)
-        output =  Bus{eltype(out)}(length(out))
-        trigger = Link()
-        handshake = Link{Bool}()
-        new{typeof(outputfunc), typeof(output), typeof(trigger), typeof(handshake)}(outputfunc, output, trigger, 
-        handshake, Callback[], uuid4())
-    end
-end
-
-##### Common generator types.
-mutable struct SinewaveGenerator{OF, OB, T, H} <: AbstractSource
-    @generic_source_fields
-    amplitude::Float64
-    frequency::Float64
-    phase::Float64
-    delay::Float64
-    offset::Float64
-    function SinewaveGenerator(;amplitude=1., frequency=1., phase=0., delay=0., offset=0.)
-        outputfunc(t) =  amplitude * sin(2 * pi * frequency * (t - delay)) + offset
-        output = Bus()
-        trigger = Link()
-        handshake = Link{Bool}()
-        new{typeof(outputfunc), typeof(output), typeof(trigger), typeof(handshake)}(outputfunc, output, trigger, 
-            handshake, Callback[], uuid4(), amplitude, frequency, phase, delay, offset)
-    end
-end
-
-
-mutable struct DampedSinewaveGenerator{OF, OB, T, H} <: AbstractSource
-    @generic_source_fields
-    amplitude::Float64
-    decay::Float64
-    frequency::Float64
-    phase::Float64
-    delay::Float64
-    offset::Float64
-    function DampedSinewaveGenerator(;amplitude=1., decay=-0.5, frequency=1., phase=0., delay=0., offset=0.)
-        outputfunc(t) = amplitude * exp(decay) * sin(2 * pi * frequency * (t - delay)) + offset
-        output = Bus()
-        trigger = Link()
-        handshake = Link{Bool}()
-        new{typeof(outputfunc), typeof(output), typeof(trigger), typeof(handshake)}(outputfunc, output, trigger, 
-            handshake, Callback[], uuid4(), amplitude, decay,frequency, phase, delay, offset)
-    end
-end
-
-
-
[…]

### 2020-04-29 build/components/systems/dynamic_systems/DynamicSystems.jl

@@ -1,32 +1,0 @@
-# This file contains the dynamic systems of Jusdl.
-
-@reexport module DynamicSystems
-
-using DifferentialEquations
-using Sundials
-using UUIDs
-using LinearAlgebra
-import ..Systems: infer_number_of_outputs, checkandshow
-import ......Jusdl.Utilities: Callback, Buffer
-import ......Jusdl.Connections: Link, Bus
-import Base.show
-
-include("utils.jl")
-include("discrete_systems.jl")
-include("ode_systems.jl")
-include("dae_systems.jl")
-include("rode_systems.jl")
-include("sde_systems.jl")
-include("dde_systems.jl")
-# include("system_inference.jl")
-
-export Solver, Noise, History, Diffusion
-export DiscreteSystem
-export ODESystem, LinearSystem, LorenzSystem, ChenSystem, ChuaSystem, RosslerSystem, VanderpolSystem 
-export DAESystem 
-export RODESystem 
-export SDESystem, NoisyLinearSystem, NoisyLorenzSystem, NoisyChuaSystem, NoisyRosslerSystem, NoisyVanderpolSystem, Noise
-export DDESystem
-# export DynamicSystem
-
-end  # module

### 2020-04-29 build/components/systems/dynamic_systems/dde_systems.jl

@@ -1,22 +1,0 @@
-# This file includes DDESystems
-
-import ....Components.Base: @generic_system_fields, @generic_dynamic_system_fields, AbstractDDESystem
-
-const DDESolver = Solver(MethodOfSteps(Tsit5()))
-
-mutable struct DDESystem{IB, OB, T, H, SF, OF, ST, IV, S, HST} <: AbstractDDESystem
-    @generic_dynamic_system_fields
-    history::HST
-    function DDESystem(input, output, statefunc, outputfunc, state, history, t; solver=DDESolver)
-        trigger = Link()
-        handshake = Link{Bool}()
-        inputval = typeof(input) <: Bus ? rand(eltype(state), length(input)) : nothing
-        new{typeof(input), typeof(output), typeof(trigger), typeof(handshake), typeof(statefunc), typeof(outputfunc), 
-            typeof(state), typeof(inputval), typeof(solver), typeof(history)}(input, output, trigger, Callback[], 
-            uuid4(), statefunc, outputfunc, state, inputval, t, solver, history)
-    end
-end
-
-show(io::IO, ds::DDESystem) = print(io, "DDESystem(state:$(ds.state), history:$(ds.history), t:$(ds.t), ", 
-    "input:$(checkandshow(ds.input)), output:$(checkandshow(ds.output)), noise:$(checkandshow(ds.noise)))")
-

### 2020-04-29 build/components/systems/dynamic_systems/discrete_systems.jl

@@ -1,21 +1,0 @@
-# This file includes the Discrete Systems
-
-import ....Components.Base: @generic_system_fields, @generic_dynamic_system_fields, AbstractDiscreteSystem
-
-const DiscreteSolver = Solver(FunctionMap())
-
-
-mutable struct DiscreteSystem{IB, OB, T, H, SF, OF, ST, IV, S} <: AbstractDiscreteSystem
-    @generic_dynamic_system_fields
-    function DiscreteSystem(input, output, statefunc, outputfunc, state, t;  solver=DiscreteSolver)
-        trigger = Link()
-        handshake = Link{Bool}()
-        inputval = typeof(input) <: Bus ? rand(eltype(state), length(input)) : nothing
-        new{typeof(input), typeof(output), typeof(trigger), typeof(handshake), typeof(statefunc), typeof(outputfunc), 
-            typeof(state),  typeof(inputval), typeof(solver)}(input, output, trigger, Callback[], uuid4(), statefunc, 
-            outputfunc, state, inputval, t, solver)
-    end
-end
-
-show(io::IO, ds::DiscreteSystem) = print(io, "DiscreteSystem(state:$(ds.state), t:$(ds.t), ",
-    "input:$(checkandshow(ds.input)), output:$(checkandshow(ds.output)))")

### 2020-04-29 build/components/systems/dynamic_systems/utils.jl

@@ -1,114 +1,0 @@
-# This file includes utilities for DynamicalSystems module
-
-import ..Systems: hasargs
-
-
-allstates(x, u, t) = x
-
-struct Solver{A, T}
-    alg::A 
-    params::Dict{Symbol, T}
-end
-Solver(alg) = Solver(alg, Dict{Symbol, Any}())
-
-
-mutable struct Noise{P, R}
-    process::P 
-    prototype::R
-    seed::UInt
-end
-Noise(process) = Noise(process, nothing, UInt(0))
-
-struct Diffusion{M} 
-    matrix::M
-end
-(dif::Diffusion)(dx, x, u, t) = (dx .= dif.matrix)
-
-struct History{F, C, D}
-    func::F 
-    conslags::C 
-    depslags::D
-    neutral::Bool
-end
-History(func) = History(func, [], [], false)
-(hist::History)(u, t) = hist.func(u, t)
-
-##### Pretty-printing
-show(io::IO, solver::Solver) = print(io, "Solver(alg:$(solver.alg), params:$(solver.params))")
-show(io::IO, noise::Noise) = print(io, 
-    "Noise(process:$(noise.process), prototype:$(checkandshow(noise.prototype)), seed:$(noise.seed))")
-show(io::IO, dif::Diffusion) = print(io, "Diffusion(matrix:$(dif.matrix))")
-show(io::IO, hist::History) = print(io, 
-    "History(func:$(hist.func), conslags:$(hist.conslags), seed:$(hist.depslags), neutral:$(hist.neutral)")
-
-
-struct SignatureError <: Exception
-    msg::String
-end
-Base.showerror(io::IO, ex::SignatureError) = print(io, "SignatureError: " * ex.msg)
-
-
-signatures(func) = [method.sig for method in methods(func)]
-
-function check_methods(model::Symbol, statefunc, outputfunc)
-    if statefunc === nothing
-        if !hasargs(outputfunc, 3)
-            msg = "Expected signature for $model is `outputfunc(x, u, t)`, got $(signatures(outputfunc))"
-            throw(SignatureError(msg))
-        end
-    end
-    if model in [:DiscreteSystem, :ODESystem]
-        if !hasargs(statefunc, 4)
-            msg = "Expected signature for $model is `statefunc(dx, x, u, t)`, got $(signatures(statefunc))"
-            throw(SignatureError(msg))
-        end
-    elseif model == :DAESystem
-        if !hasargs(statefunc, 5)
[…]

### 2020-04-29 build/components/systems/subsystems/SubSystems.jl

@@ -1,17 +1,0 @@
-@reexport module SubSystems
-
-using UUIDs
-using LightGraphs, LinearAlgebra, GraphPlot
-import ..Systems: checkandshow
-import ..Systems.StaticSystems: Memory, Coupler, StaticSystem
-import ....Components.Base: @generic_system_fields, AbstractSubSystem, AbstractDynamicSystem
-import ......Jusdl.Connections: Link, Bus, connect, disconnect, getmaster
-import ......Jusdl.Utilities: Callback
-
-include("subsystem.jl")
-include("network.jl")
-
-export SubSystem, Network, uniformconnectivity, cgsconnectivity, clusterconnectivity, coupling, gplot
-export deletelink, changeweight, maketimevarying, openinputbus
-
-end

### 2020-04-29 build/components/systems/subsystems/subsystem.jl

@@ -1,38 +1,0 @@
-# This file includes SubSystem for interconnected subsystems.
-
-
-mutable struct SubSystem{IB, OB, T, H, C} <: AbstractSubSystem
-    @generic_system_fields
-    components::C
-    function SubSystem(components, input::Union{Nothing, <:Bus, <:AbstractVector{<:Link}}, 
-        output::Union{Nothing, <:Bus, <:AbstractVector{<:Link}})
-        trigger = Link()
-        handshake = Link{Bool}()
-        if typeof(input) <: AbstractVector{<:Link}
-            inputbus = Bus(length(input))
-            for (i, link) in enumerate(input)
-                inputbus[i] = link
-            end
-            # inputbus .= input
-        else 
-            inputbus = input
-        end
-        
-        if typeof(output) <: AbstractVector{<:Link}
-            outputbus = Bus(length(output))
-            for (i, link) in enumerate(output)
-                outputbus[i] = link
-            end
-            # outputbus .= output
-        else
-            outputbus = output
-        end
-        # TODO: Check if there exists an unconnected interconnected buses between the components of the subsytem.
-        new{typeof(inputbus), typeof(outputbus), typeof(trigger), typeof(handshake), typeof(components)}(inputbus, 
-            outputbus, trigger, handshake, Callback[], uuid4(), components)
-    end
-end
-
-
-show(io::IO, sub::SubSystem) = print(io, "SubSystem(input:$(checkandshow(sub.input)), ",
-    "output:$(checkandshow(sub.output)), components:$(checkandshow(sub.components)))")

### 2020-04-29 build/connections/bus.jl

@@ -1,84 +1,0 @@
-# This file contains the Bus tool for connecting the tools of DsSimulator
-
-import Base: put!, wait, take!
-import Base: size, getindex, setindex!, length, iterate, firstindex, lastindex, close, eltype
-
-
-struct Bus{T}
-    links::Vector{Link{T}}
-    callbacks::Vector{Callback}
-    id::UUID
-    Bus{T}(nlinks::Int=1, ln::Int=64) where T = 
-        new{Union{Missing, T}}([Link{T}(ln) for i = 1 : nlinks], Callback[], uuid4())
-end
-Bus(nlinks::Int=1, ln::Int=64) = Bus{Float64}(nlinks, ln)
-
-show(io::IO, bus::Bus{Union{Missing, T}})  where T = print(io, "Bus(nlinks:$(length(bus)), eltype:$(T), ",
-    "isreadable:$(isreadable(bus)), iswritable:$(iswritable(bus)))")
-
-##### Make bus indexable.
-eltype(bus::Bus{T}) where {T} = T
-length(bus::Bus) = length(bus.links)
-size(bus::Bus) = size(bus.links)
-getindex(bus::Bus, I::Int) =  bus.links[I]
-getindex(bus::Bus, I::Vector{Int}) =  bus.links[I]
-getindex(bus::Bus, I::UnitRange{Int}) = bus.links[I]
-getindex(bus::Bus, ::Colon) = bus.links[:]
-setindex!(bus::Bus, val, I::Int) = bus.links[I] = val
-setindex!(bus::Bus, val::AbstractVector, I::Vector{Int}) = bus.links[I] = val
-setindex!(bus::Bus, val::AbstractVector, I::UnitRange{Int}) = bus.links[I] = val
-setindex!(bus::Bus, val::AbstractVector, ::Colon) = bus.links[:] = val
-firstindex(bus::Bus) = 1
-lastindex(bus::Bus) = length(bus)  # For indexing like bus[end]
-
-##### Reading from and writing into from buses
-function take!(bus::Bus) 
-    out = take!.(bus.links)
-    bus.callbacks(bus)
-    out
-end
-function put!(bus::Bus, vals)
-    put!.(bus.links, vals)
-    bus.callbacks(bus)
-    vals
-end
-
-##### Iterating bus
[…]

### 2020-04-29 build/connections/link.jl

@@ -1,159 +1,0 @@
-# This file contains the links to connect together the tools of DsSimulator.
-
-import Base: put!, take!, RefValue, close, isready, eltype, isopen, isreadable, iswritable
-
-struct Pin
-    id::UUID
-    Pin() = new(uuid4())
-end
-
-
-mutable struct Link{T}
-    buffer::Buffer{Cyclic, T}
-    channel::Channel{T}
-    leftpin::Pin
-    rightpin::Pin
-    callbacks::Vector{Callback}
-    id::UUID
-    master::RefValue{Link{T}}
-    slaves::Vector{RefValue{Link{T}}}
-    Link{T}(ln::Int=64) where {T} = new{Union{Missing, T}}(Buffer(T, ln), Channel{Union{Missing, T}}(0), Pin(), Pin(),
-        Callback[], uuid4(), RefValue{Link{Union{Missing,T}}}(), Vector{RefValue{Link{Union{Missing, T}}}}()) 
-end
-Link(ln::Int=64) = Link{Float64}(ln)
-
-eltype(link::Link{T}) where T = T
-
-show(io::IO, link::Link) = print(io, 
-    "Link(state:$(isopen(link) ? :open : :closed), eltype:$(eltype(link)), hasmaster:$(isassigned(link.master)), ", 
-    "numslaves:$(length(link.slaves)), isreadable:$(isreadable(link)), iswritable:$(iswritable(link)))")
-
-##### Link reading writing.
-function put!(link::Link, val) 
-    write!(link.buffer, val)
-    isempty(link.slaves) || foreach(junc -> put!(junc[], val), link.slaves)
-    put!(link.channel, val)
-    link.callbacks(link)
-    return val
-end
-
-function take!(link::Link)
-    val = take!(link.channel)
-    link.callbacks(link)
-    return val
-end
-
-function close(link::Link)
-    channel = link.channel
-    isempty(channel.cond_take.waitq) || put!(link, missing)   # Terminate taker task 
-    isempty(channel.cond_put.waitq) || collect(link.channel)   # Terminater putter task 
-    # isopen(link.channel) && close(link.channel)  # Close link channel if it is open.
-    return 
-end 
-
-##### Auxilary functions to launch links.
-function taker(link::Link)
-    while true
-        val = take!(link)
-        val isa Missing && break  # Poison-pill the tasks to terminate safely.
-        @info "Took " val
-    end
-end
-
-function putter(link::Link, vals)
[…]

### 2020-04-29 build/models/taskmanager.jl

@@ -1,47 +1,0 @@
-# This file is for TaskManager object.
-
-import Base: istaskdone
-
-struct ComponentTask{T, S}
-    triggertask::T 
-    outputtask::S 
-end
-ComponentTask(tasks::Tuple) = ComponentTask(tasks...)
-ComponentTask(tasks::AbstractArray{<:Tuple}) = [ComponentTask.(tasks...)...]
-
-mutable struct TaskManager{T, S}
-    pairs::Dict{T, S}
-    callbacks::Vector{Callback}
-    id::UUID
-    TaskManager(pairs::Dict{T, S}) where {T, S}  = new{T, S}(pairs, Callback[], uuid4())
-end
-TaskManager() = TaskManager(Dict{Any, Any}())
-
-show(io::IO, tm::TaskManager) = print(io, "TaskManager(pairs:$(tm.pairs))")
-
-function checktaskmanager(tm::TaskManager)
-    for (block, comptask) in tm.pairs
-        # istaskfailed(comptask) && error("$comptask failed for $block")
-        checkcomptask(comptask) || error("$comptask failed for $block")
-    end
-end
-function checkcomptask(comptask)
-    if typeof(comptask) <: ComponentTask
-        istaskfailed(comptask) ? false : true
-    elseif typeof(comptask) <: AbstractArray
-        return checkcomptask(comptask...)
-    end
-end
-checkcomptask(comptask...) = all(checkcomptask.(comptask))
-
-istaskfailed(task::Nothing) = false
-istaskfailed(task::Task) = task.state == :failed
-istaskfailed(comptask::ComponentTask) = istaskfailed(comptask.triggertask) || istaskfailed(comptask.outputtask)
-
-istaskrunning(task::Task) = task.state == :runnable
-istaskrunning(task::Nothing) = true
-istaskrunning(comptask::ComponentTask) = istaskrunning(comptask.triggertask) && istaskrunning(comptask.outputtask)
-
-istaskdone(task::Nothing) = true
-istaskdone(comptask::ComponentTask) = istaskdone(comptask.triggertask) && istaskdone(comptask.outputtask)
-

### 2020-04-29 build/plugins/Plugins.jl

@@ -1,69 +1,0 @@
-# This file includes the Plugins module
-
-@reexport module Plugins
-
-using LibGit2
-using Random
-import Base.show
-
-abstract type AbstractPlugin end
-
-# Define generic plugin functions.
-function process end
-function enable end
-function disable end
-function check end
-function add end
-function remove end
-
-function search(rootpath::AbstractString, filename::AbstractString)
-    paths = String[]
-    for (root, dirs, files) in walkdir(rootpath)
-        for file in files
-            if occursin(filename, file)
-                push!(paths, joinpath(root, file))
-            end
-        end
-    end
-    paths
-end
-
-const remote_repo_url = "https://imel.eee.deu.edu.tr/git/JusdlPlugins.jl.git"
-
-function add(name::AbstractString, url::AbstractString=remote_repo_url)
-    startswith(name, ".") && error("Name of plugin should not start with `.`")
-    startswith(name, "Plugins") && error("Name of plugin cannot be `Plugins`")
-    startswith(".jl", name) || (name *= ".jl")
-    
-    repopath = joinpath("/tmp", "JusdlPlugins", randstring())
-    ispath(repopath) || mkpath(repopath)
-    @info "Cloning avaliable plugins from $url"
-    LibGit2.clone(url, repopath)
-    @info "Done..."
-
-    @info "Searching for $name in plugins repo."
-    srcpath = search(joinpath(repopath, "src"), name)[1]
-    if isempty(srcpath)
-        error("$name could not be found in avaliable plugins")
-    else
-        dstdir = joinpath(@__DIR__, "additionals")
-        dstpath = joinpath(dstdir, name)
-        cp(srcpath, dstpath, force=true)
-        include(dstpath)
-        @info "$name is added to Jusdl.Plugins"
-    end
-end
-
-# Includes essential plugins from Jusdl
-foreach(include, search(joinpath(@__DIR__, "essentials"), ".jl"))
-
-# Includes additional plugins from Jusdl
-foreach(include, search(joinpath(@__DIR__, "additionals"), ".jl"))
-
-# Include plugins from user working directory.
-user_plugins_path = joinpath(pwd(), "plugins")
-ispath(user_plugins_path) && foreach(include, search(joinpath(user_plugins_path), ".jl"))
-
-export process, add, remove, enable, disable, check
-
-end  # module

### 2020-04-29 build/plugins/essentials/fft.jl

@@ -1,11 +1,0 @@
-# This file includes the plugin for calculation of fast fourier transform of data
-using FFTW
-
-struct Fft <: AbstractPlugin 
-    dims::Int
-end 
-Fft(;dims::Int=1) = Fft(dims)
-
-show(io::IO, plg::Fft) = print(io, "Fft(dims:$(plg.dims))")
-
-process(plg::Fft, x) = fft(x, plg.dims)

### 2020-04-29 build/utilities/callbacks.jl

@@ -1,24 +1,0 @@
-# This file constains the callbacks for event monitoring.
-
-mutable struct Callback{C, A}
-    condition::C       
-    action::A     
-    enabled::Bool
-    id::UUID
-    Callback(condition::C, action::A) where {C, A} = new{C, A}(condition, action, true, uuid4()) 
-end
-
-show(io::IO, clb::Callback) = print(io, "Callback(condition:$(clb.condition), action:$(clb.action))")
-
-##### Callback controls
-enable!(clb::Callback) = clb.enabled = true
-disable!(clb::Callback) = clb.enabled = false
-isenabled(clb::Callback) = clb.enabled
-
-##### Callback calls
-(clb::Callback)(obj) = clb.enabled && clb.condition(obj) ?  clb.action(obj) : nothing
-@inbounds (clbs::Vector{Callback})(obj) = foreach(clb -> clb(obj), clbs)
-
-##### Adding callbacks
-addcallback(obj, callback::Callback, priority::Int=1) = (insert!(obj.callbacks, priority, callback); obj)
-deletecallback(obj, idx::Int) = (delete!(obj.callbacks, idx); obj)

### 2020-04-29 build/utilities/double_buffer.jl

@@ -1,179 +1,0 @@
-# This file contains the DouBuffer type for data buffering.
-
-using UUIDs
-import Base: getindex, setindex!, size, eltype, similar
-import Base: read, isempty, convert
-
-
-mutable struct DoubleBuffer{T, N, B, CB} <: AbstractDoubleBuffer{T, N}
-    input_buffer::B
-    output_buffer::B
-    mode::Symbol
-    callbacks::CB
-    name::String
-    function DoubleBuffer(input_buffer::B, output_buffer::B, callbacks::CB,
-        name::String) where {B<:AbstractBuffer{T, N},
-        CB<:AbstractVector{<:AbstractCallback}} where {T, N}
-        input_buffer_mode = mode(input_buffer)
-        output_buffer_mode = mode(output_buffer)
-        if input_buffer_mode != output_buffer_mode
-            msg = "Expected same internal buffer modes, "
-            msg *= "got $input_buffer_mode and $output_buffer_mode instead."
-            error(msg)
-        end
-        # Construct the swap callback. This callback
-        condition(dbuf) = isfull(dbuf.input_buffer)
-        action(dbuf) = swap_buffers(dbuf)
-        clb = Callback(condition, action)
-        callbacks = [clb, callbacks...]
-        new{T, N, B, typeof(callbacks)}(input_buffer, output_buffer, input_buffer_mode,
-            callbacks, name)
-    end
-end
-DoubleBuffer(::Type{T}, shape::NTuple{N, Int}; mode=:cyclic, callbacks=Callback[],
-    name=randstring()) where {T, N} =
-    DoubleBuffer(Buffer(T, shape, mode=mode), Buffer(T, shape, mode=mode), callbacks, name)
-DoubleBuffer(::Type{T}, shape::Int...; kwargs...) where T = DoubleBuffer(T,shape;kwargs...)
-DoubleBuffer(shape::Int...; kwargs...) = DoubleBuffer(Float64, shape...; kwargs...)
-
-"""
-    DoubleBuffer(::Type{T}, shape::NTuple{N, Int}; mode::Symbol=:cyclic,
-        callbacks::C=()) where {T<:Real, N, C<:Tuple{Vararg{<:AbstractCallback}}}
-
-Constructs a `DoubleBuffer` consisting of two internal cyclic buffers of size `shape` i.e.
[…]

### 2020-04-29 docs/make.jl

@@ -59,14 +59,14 @@ makedocs(
                 "manual/models/model.md",
                 ],
             ],
-        "Tutorials" => [
-            "Simple Model Simulation" => "tutorials/simple_model.md",
-            "Breaking Algebraic Loops" => "tutorials/breaking_algebraic_loops.md",
-            "Constuction and Simulation of Subsystems" => "tutorials/construction_and_simulation_of_subsystems.md",
-            "Constuction and Simulation of Networks" => "tutorials/construction_and_simulation_of_networks.md",
-        ],
+        # "Tutorials" => [
+        #     "Simple Model Simulation" => "tutorials/simple_model.md",
+        #     "Breaking Algebraic Loops" => "tutorials/breaking_algebraic_loops.md",
+        #     "Constuction and Simulation of Subsystems" => "tutorials/construction_and_simulation_of_subsystems.md",
+        #     "Constuction and Simulation of Networks" => "tutorials/construction_and_simulation_of_networks.md",
+        # ],
     ],
     # format=DocumenterLaTeX.LaTeX()  # Uncomment this option to generate pdf output.
 )  # end makedocs
 
-deploydocs(repo = "github.com/zekeriyasari/Jusdl.jl.git")
+# deploydocs(repo = "github.com/zekeriyasari/Jusdl.jl.git")

### 2020-04-29 src/Jusdl.jl

@@ -29,7 +29,7 @@ include("utilities/callback.jl")
 export Callback, enable!, disable!, isenabled, applycallbacks
 
 include("utilities/buffer.jl")
-export Buffer, Normal, Cyclic, Fifo, Lifo, write!, isfull, ishit, content, mode, snapshot, datalength, inbuf, outbuf
+export BufferMode, LinearMode, CyclicMode, Buffer, Normal, Cyclic, Fifo, Lifo, write!, isfull, ishit, content, mode, snapshot, datalength, inbuf, outbuf
 
 include("connections/link.jl")
 export Link, launch

### 2020-04-29 src/components/sources/clock.jl

@@ -38,14 +38,14 @@ show(io::IO, clk::Clock) = print(io,
 Takes a values from `clk`.
 
 # Example 
-```jldocstest
-ulia> clk = Clock(0., 0.1, 0.5)
+```jldoctest
+julia> clk = Clock(0., 0.1, 0.5)
 Clock(t:0.0, dt:0.1, tf:0.5, paused:false, isrunning:false)
 
 julia> set!(clk)
 Clock(t:0.0, dt:0.1, tf:0.5, paused:false, isrunning:true)
 
-julia> for i = 0 : 5 
+julia> for i in 0 : 5
        @show take!(clk)
        end
 take!(clk) = 0.0
@@ -107,14 +107,9 @@ isoutoftime(clk::Clock) = clk.t >= clk.tf
 Sets `clk` for current clock time `t`, sampling time `dt` and final time `tf`. After the set,  it is possible to take clock tick from `clk`. See also [`take!(clk::Clock)`](@ref)
 
 # Example 
-```jldocstest
+```jldoctest
 julia> clk = Clock(0., 0.1, 0.5)
 Clock(t:0.0, dt:0.1, tf:0.5, paused:false, isrunning:false)
-
-julia> take!(clk)
-┌ Warning: Clock is not running.
-└ @ Jusdl.Components.Sources ~/.julia/dev/Jusdl/src/components/sources/clock.jl:47
-0.0
 
 julia> set!(clk)
 Clock(t:0.0, dt:0.1, tf:0.5, paused:false, isrunning:true)
@@ -152,24 +147,23 @@ end
 Pauses `clk`. When paused, the current time of `clk` does not advance.
 
 # Example
-```jldocstest
+```jldoctest
 julia> clk = Clock(0., 0.1, 0.5);
 
 julia> set!(clk);
 
 julia> for i = 1 : 5
-       i > 3 && pause!(clk)
-       @show take!(clk)
-       end
-
+              i > 3 && pause!(clk)
+              @show take!(clk)
+              end
 take!(clk) = 0.0
 take!(clk) = 0.1
 take!(clk) = 0.2
 ┌ Warning: Clock is paused.
-└ @ Jusdl.Components.Sources ~/.julia/dev/Jusdl/src/components/sources/clock.jl:58
+└ @ Jusdl ~/.julia/dev/Jusdl/src/components/sources/clock.jl:61
 take!(clk) = 0.2
 ┌ Warning: Clock is paused.
[…]

### 2020-04-29 src/components/systems/dynamicalsystems/daesystems.jl

@@ -33,19 +33,19 @@ end
 
 # Example 
 ```jldoctest 
-julia> function sfunc(out, dx, x, u, t)
+julia> function sfuncdae(out, dx, x, u, t)
            out[1] = x[1] + 1 - dx[1]
            out[2] = (x[1] + 1) * x[2] + 2
        end;
 
-julia> ofunc(x, u, t) = x;
+julia> ofuncdae(x, u, t) = x;
 
 julia> x0 = [1., -1];
 
 julia> dx0 = [2., 0.];
 
-julia> ds = DAESystem(nothing, Bus(1), sfunc, ofunc, x0, dx0, 0., modelkwargs=(differential_vars=[true, false],))
-DAESystem(state:[1.0, -1.0], t:0.0, input:nothing, output:Bus(nlinks:1, eltype:Link{Float64}, isreadable:false, iswritable:false))
+julia> DAESystem(sfuncdae, ofuncdae, x0, 0., nothing, Outport(1), modelkwargs=(differential_vars=[true, false],), stateder=dx0)
+DAESystem(state:[1.0, -1.0], t:0.0, input:nothing, output:Outport(numpins:1, eltype:Outpin{Float64}))
 ```
 
 !!! info 

### 2020-04-29 src/components/systems/dynamicalsystems/ddesystems.jl

@@ -35,19 +35,19 @@ julia> const out = zeros(1);
 
 julia> histfunc(out, u, t) = (out .= 1.);
 
-julia> function statefunc(dx, x, h, u, t)
+julia> function sfuncdde(dx, x, h, u, t)
            h(out, u, t - tau) # Update out vector
            dx[1] = out[1] + x[1]
        end;
 
-julia> outputfunc(x, u, t) = x;
+julia> ofuncdde(x, u, t) = x;
 
 julia> tau = 1;
 
 julia> conslags = [tau];
 
-julia> ds = DDESystem(nothing, Bus(), (statefunc, histfunc), outputfunc, [1.],  0.)
-DDESystem(state:[1.0], t:0.0, input:nothing, output:Bus(nlinks:1, eltype:Link{Float64}, isreadable:false, iswritable:false))
+julia> DDESystem((sfuncdde, histfunc), ofuncdde, [1.],  0., nothing, Outport())
+DDESystem(state:[1.0], t:0.0, input:nothing, output:Outport(numpins:1, eltype:Outpin{Float64}))
 ```
 
 !!! info 

### 2020-04-29 src/components/systems/dynamicalsystems/discretesystems.jl

@@ -32,14 +32,12 @@ end
 
 # Example 
 ```jldoctest 
-julia> sfunc(dx,x,u,t) = (dx .= 0.5x)
-sfunc (generic function with 1 method)
+julia> sfuncdiscrete(dx,x,u,t) = (dx .= 0.5x);
 
-julia> ofunc(x, u, t) = x
-ofunc (generic function with 1 method)
+julia> ofuncdiscrete(x, u, t) = x;
 
-julia> ds = DiscreteSystem(Bus(1), Bus(1), sfunc, ofunc, [1.], 0.)
-DiscreteSystem(state:[1.0], t:0.0, input:Bus(nlinks:1, eltype:Link{Float64}, isreadable:false, iswritable:false), output:Bus(nlinks:1, eltype:Link{Float64}, isreadable:false, iswritable:false))
+julia> DiscreteSystem(sfuncdiscrete, ofuncdiscrete, [1.], 0., nothing, Outport())
+DiscreteSystem(state:[1.0], t:0.0, input:nothing, output:Outport(numpins:1, eltype:Outpin{Float64}))
 ```
 
 !!! info 

### 2020-04-29 src/components/systems/dynamicalsystems/odesystems.jl

@@ -32,17 +32,15 @@ end
 
 # Example 
 ```jldoctest
-julia> sfunc(dx,x,u,t) = (dx .= 0.5x)
-sfunc (generic function with 1 method)
+julia> sfuncode(dx,x,u,t) = (dx[1] = 0.5x[1] + u[1](t));
 
-julia> ofunc(x, u, t) = x
-ofunc (generic function with 1 method)
+julia> ofuncode(x, u, t) = x;
 
-julia> ds = ODESystem(Bus(1), Bus(1), sfunc, ofunc, [1.], 0.)
-ODESystem(state:[1.0], t:0.0, input:Bus(nlinks:1, eltype:Link{Float64}, isreadable:false, iswritable:false), output:Bus(nlinks:1, eltype:Link{Float64}, isreadable:false, iswritable:false))
+julia> ds = ODESystem(sfuncode, ofuncode, [1.], 0., Inport(), Outport())
+ODESystem(state:[1.0], t:0.0, input:Inport(numpins:1, eltype:Inpin{Float64}), output:Outport(numpins:1, eltype:Outpin{Float64}))
 
-julia> ds = ODESystem(Bus(1), Bus(1), sfunc, ofunc, [1.], 0., solverkwargs=(dt=0.1, reltol=1e-6))
-ODESystem(state:[1.0], t:0.0, input:Bus(nlinks:1, eltype:Link{Float64}, isreadable:false, iswritable:false), output:Bus(nlinks:1, eltype:Link{Float64}, isreadable:false, iswritable:false))
+julia> ds = ODESystem(sfuncode, ofuncode, [1.], 0., Inport(), Outport(), solverkwargs=(dt=0.1, reltol=1e-6))
+ODESystem(state:[1.0], t:0.0, input:Inport(numpins:1, eltype:Inpin{Float64}), output:Outport(numpins:1, eltype:Outpin{Float64}))
 ```
 
 !!! info 

### 2020-04-29 src/components/systems/dynamicalsystems/rodesystems.jl

@@ -32,16 +32,16 @@ end
 ```
 
 # Example 
-```julia
-julia> function statefunc(dx, x, u, t, W)
+```jldoctest
+julia> function sfuncrode(dx, x, u, t, W)
          dx[1] = 2x[1]*sin(W[1] - W[2])
          dx[2] = -2x[2]*cos(W[1] + W[2])
        end;
 
-julia> outputfunc(x, u, t) = x;
+julia> ofuncrode(x, u, t) = x;
 
-julia> ds = RODESystem(nothing, Bus(2), statefunc, outputfunc, [1., 1.], 0., solverkwargs=(dt=0.01,))
-RODESystem(state:[1.0, 1.0], t:0.0, input:nothing, output:Bus(nlinks:2, eltype:Link{Float64}, isreadable:false, iswritable:false))
+julia> RODESystem(sfuncrode, ofuncrode, [1., 1.], 0., solverkwargs=(dt=0.01,), nothing, Outport(2))
+RODESystem(state:[1.0, 1.0], t:0.0, input:nothing, output:Outport(numpins:2, eltype:Outpin{Float64}))
 ```
 
 !!! info 

### 2020-04-29 src/components/systems/dynamicalsystems/sdesystems.jl

@@ -35,14 +35,14 @@ end
 
 # Example 
 ```jldoctest
-julia> f(dx, x, u, t) = (dx[1] = -x[1]);
+julia> sfuncdrift(dx, x, u, t) = (dx[1] = -x[1]);
 
-julia> h(dx, x, u, t) = (dx[1] = -x[1]);
+julia> sfuncdiffusion(dx, x, u, t) = (dx[1] = -x[1]);
 
-julia> g(x, u, t) = x;
+julia> ofuncsde(x, u, t) = x;
 
-julia> ds = SDESystem(nothing, Bus(), (f,h), g, [1.], 0.)
-SDESystem(state:[1.0], t:0.0, input:nothing, output:Bus(nlinks:1, eltype:Link{Float64}, isreadable:false, iswritable:false))
+julia> SDESystem((sfuncdrift,sfuncdiffusion), ofuncsde, [1.], 0., nothing, Outport())
+SDESystem(state:[1.0], t:0.0, input:nothing, output:Outport(numpins:1, eltype:Outpin{Float64}))
 ```
 
 !!! info 

### 2020-04-29 src/components/systems/staticsystems/staticsystems.jl

@@ -14,14 +14,14 @@ where `g` is `outputfunc`, `t` is the time, `u` is the input at time `t` and `y`
 julia> g(u, t) = [u[1] + u[2], sin(u[2]), cos([1])]  # The system has 2 inputs and 3 outputs.
 g (generic function with 1 method)
 
-julia> ss = StaticSystem(Bus(2), Bus(3), g)
-StaticSystem(outputfunc:g, input:Bus(nlinks:2, eltype:Link{Float64}, isreadable:false, iswritable:false), output:Bus(nlinks:3, eltype:Link{Float64}, isreadable:false, iswritable:false))
+julia> ss = StaticSystem(g, Inport(2), Outport(3))
+StaticSystem(outputfunc:g, input:Inport(numpins:2, eltype:Inpin{Float64}), output:Outport(numpins:3, eltype:Outpin{Float64}))
 
 julia> g2(u, t) = t  # The system does not have any input.
 g2 (generic function with 1 method)
 
-julia> ss2 = StaticSystem(nothing, Bus(), g2)
-StaticSystem(outputfunc:g2, input:nothing, output:Bus(nlinks:1, eltype:Link{Float64}, isreadable:false, iswritable:false))
+julia> ss2 = StaticSystem(g2, nothing, Outport())
+StaticSystem(outputfunc:g2, input:nothing, output:Outport(numpins:1, eltype:Outpin{Float64}))
 ```
 """
 struct StaticSystem{OF, IB, OB, TR, HS, CB} <: AbstractStaticSystem
@@ -46,7 +46,7 @@ where `n` is the length of the `input`, ``s_k`` is the `k`th element of `signs`,
 
 # Example 
 ```jldoctest
-julia> adder = Adder(Bus(3), (+, +, -));
+julia> adder = Adder((+, +, -));
 
 julia> adder.outputfunc([3, 4, 5], 0.) == 3 + 4 - 5
 true
@@ -79,7 +79,7 @@ where `n` is the length of the `input`, ``s_k`` is the `k`th element of `signs`,
 
 # Example 
 ```jldoctest
-julia> mlt = Multiplier(Bus(3), (*, *, /));
+julia> mlt = Multiplier((*, *, /));
 
 julia> mlt.outputfunc([3, 4, 5], 0.) == 3 * 4 / 5
 true
@@ -120,9 +120,9 @@ where ``K`` is `gain`, ``u`` is the value of `input` and `y` is the value of `ou
 ```jldoctest
 julia> K = [1. 2.; 3. 4.];
 
[…]

### 2020-04-29 src/components/systems/subsystems/subsystem.jl

@@ -3,9 +3,25 @@
 
 # TODO: Check if there exists an unconnected interconnected buses between the components of the subsytem.
 """
-    SubSystem(components, input, output)
+    SubSystem(components, input, output; callbacks=nothing, name=Symbol())
 
-Constructs a `SubSystem` consisting of `components`. `input` and `output` determines the inpyt and output of `SubSystem`. `input` and `output` may be of type `Nothing`, `Bus` of `Vector{<:Link}`.
+Constructs a `SubSystem` consisting of `components`. `input` and `output` determines the input and output of `SubSystem`. `input` and `output` may be nothing, a vector of pins or a port.
+
+# Example 
+```jldoctest 
+julia> adder = Adder((+,-));
+
+julia> gain = Gain(); 
+
+julia> gen = ConstantGenerator();
+
+julia> connect(gen.output, adder.input);
+
+julia> connect(adder.output, gain.input);
+
+julia> ss = SubSystem([gen, adder, gain], adder.input[1], gain.output)
+SubSystem(input:Inpin(eltype:Float64, isbound:true), output:Outport(numpins:1, eltype:Outpin{Float64}), components:AbstractComponent[ConstantGenerator(amp:1.0), Adder(signs:(+, -), input:Inport(numpins:2, eltype:Inpin{Float64}), output:Outport(numpins:1, eltype:Outpin{Float64})), Gain(gain:1.0, input:Inport(numpins:1, eltype:Inpin{Float64}), output:Outport(numpins:1, eltype:Outpin{Float64}))])
+```
 """
 mutable struct SubSystem{IB, OB, TR, HS, CB, CP, TP, HP} <: AbstractSubSystem
     @generic_system_fields

### 2020-04-29 src/connections/pin.jl

@@ -100,9 +100,13 @@ Connects each link in `outpin` to each link in `inpin` one by one.
 ```jldoctest 
 julia> op, ip = Outpin(), Inpin();
 
-julia> connect(op, ip)
+julia> l = connect(op, ip)
+Link(state:open, eltype:Float64, isreadable:false, iswritable:false)
 
-julia> l2.outpin[] == l1
+julia> l in op.links
+true
+
+julia> ip.link === l
 true
 ```
 """

### 2020-04-29 src/connections/port.jl

@@ -1,4 +1,4 @@
-# This file contains the Bus tool for connecting the tools of DsSimulator
+# This file contains the Port tool for connecting the tools of Jusdl
 
 
 abstract type AbstractPort{P} <: AbstractVector{P} end
@@ -13,7 +13,7 @@ Outport{T}(numpins::Int=1) where T = Outport([Outpin{T}() for i = 1 : numpins])
 Outport(numpins::Int=1) = Outport{Float64}(numpins)
 
 show(io::IO, outport::Outport) = print(io, "Outport(numpins:$(length(outport)), eltype:$(eltype(outport)))")
-display(outport::Outport) = println("Outport(numpins:$(length(outport)), eltype:$(eltype(outport)))")
+# display(outport::Outport) = println("Outport(numpins:$(length(outport)), eltype:$(eltype(outport)))")
 
 
 struct Inport{P} <: AbstractPort{P}
@@ -24,94 +24,106 @@ Inport{T}(numpins::Int=1) where T = Inport([Inpin{T}() for i = 1 : numpins])
 Inport(numpins::Int=1) = Inport{Float64}(numpins)
 
 show(io::IO, inport::Inport) = print(io, "Inport(numpins:$(length(inport)), eltype:$(eltype(inport)))")
-display(inport::Inport) = println("Inport(numpins:$(length(inport)), eltype:$(eltype(inport)))")
+# display(inport::Inport) = println("Inport(numpins:$(length(inport)), eltype:$(eltype(inport)))")
 
 
 """
-    datatype(bus::Bus)
+    datatype(port::AbstractPort)
 
-Returns the data type of `bus`.
+Returns the data type of `port`.
 """
-datatype(bus::AbstractPort{<:AbstractPin{T}}) where T = T
+datatype(port::AbstractPort{<:AbstractPin{T}}) where T = T
 
 ##### AbstractVector interface
 """
-    size(bus::Bus)
+    size(port::AbstractPort)
 
-Retruns size of `bus`.
+Retruns size of `port`.
 """
 size(port::AbstractPort) = size(port.pins)
 
 """
-    getindex(bus::Bus, idx::Vararg{Int, N}) where N 
+    getindex(port::AbstractPort, idx::Vararg{Int, N}) where N 
 
-Returns elements from `bus` at index `idx`. Same as `bus[idx]`.
+Returns elements from `port` at index `idx`. Same as `port[idx]`.
 
 # Example
 ```jldoctest
-julia> bus = Bus(3);
+julia> op = Outport(3)
[…]

### 2020-04-29 src/models/model.jl

@@ -70,7 +70,7 @@ Adds a node to `model`. Component is `component` and `label` is `label` the labe
 
 # Example 
 ```jldoctest 
-julia> model = Model() 
+julia> model = Model()
 Model(numnodes:0, numedges:0, timesettings=(0.0, 0.01, 1.0))
 
 julia> addnode(model, SinewaveGenerator(), label=:gen)
@@ -95,7 +95,7 @@ Returns node of `model` whose index is `idx`.
 
 Returns node of `model` whose label is `label`.
 
-Example
+# Example
 ```jldoctest
 julia> model = Model()
 Model(numnodes:0, numedges:0, timesettings=(0.0, 0.01, 1.0))

### 2020-04-29 src/models/taskmanager.jl

@@ -31,24 +31,7 @@ Constructs a `TaskManager` with `pairs`. `pairs` is a dictionary whose keys are 
 
     TaskManager()
 
-Constructs a `TaskManager` with empty `pairs.
-
-# Example 
-```julia
-julia> tm = TaskManager()  # A TaskManager with empty pairs
-TaskManager(pairs:Dict{Any,Any}())
-
-julia> gen = SinewaveGenerator()  # A component
-SinewaveGenerator(amp:1.0, freq:1.0, phase:0.0, offset:0.0, delay:0.0)
-
-julia> ct = ComponentTask(launch(gen))  # A component task corresponding to gen
-ComponentTask{Task,Task}(Task (runnable) @0x00007f4de1a0d390, Task (runnable) @0x00007f4de1a0d120)
-
-julia> tm.pairs[gen] = ct  # Write a component and compontent task pair into TaskManager
-ComponentTask{Task,Task}(Task (runnable) @0x00007f4de1a0d390, Task (runnable) @0x00007f4de1a0d120)
-
-julia> println(tm.pairs)
-Dict{Any,Any}(SinewaveGenerator(amp:1.0, freq:1.0, phase:0.0, offset:0.0, delay:0.0) => ComponentTask{Task,Task}(Task (runnable) @0x00007f4de1a0d390, Task (runnable) @0x00007f4de1a0d120))
+Constructs a `TaskManager` with empty `pairs`.
 ```
 """
 mutable struct TaskManager{T, S, IP, OP, CB}

### 2020-04-29 src/utilities/buffer.jl

@@ -1,4 +1,4 @@
-# This file constains the Buffer for internals buffering.
+# This file constains the Buffer for data buffering.
 
 
 ##### Buffer modes
@@ -26,14 +26,14 @@ abstract type LinearMode <: BufferMode end
 """
     Cyclic <: CyclicMode
 
-Cyclic buffer mode. The internals is written to buffer until the buffer is full. When the buffer is full, new internals is written by overwriting the internals available in the buffer starting from the beginning of the buffer. When the buffer is read, the element written last is returned and the returned element is not deleted from the buffer.
+Cyclic buffer mode. The data is written to buffer until the buffer is full. When the buffer is full, new data is written by overwriting the data available in the buffer starting from the beginning of the buffer. When the buffer is read, the element written last is returned and the returned element is not deleted from the buffer.
 """
 struct Cyclic <: CyclicMode end 
 
 """
     Normal <: LinearMode
 
-LinearMode buffer mode. The internals is written to buffer until the buffer is full. When it is full, no more internals is written to the buffer. When read, the internals written last is returned and the returned internals is not deleted from the internal container of the buffer. 
+LinearMode buffer mode. The data is written to buffer until the buffer is full. When it is full, no more data is written to the buffer. When read, the data written last is returned and the returned data is not deleted from the internal container of the buffer. 
 """
 struct Normal <: LinearMode end
 
@@ -47,7 +47,7 @@ struct Lifo <: LinearMode end
 """
     Fifo <: LinearMode
 
[…]

### 2020-05-02 doctemp/assets/AlgebraicLoop/brokenloop.tex
Revised docs.

--- 2020-01-11 docs/build/assets/AlgebraicLoop/brokenloop.tex
@@
 
+\tikzset{
+    clockborder/.style = { 
+        trapezium, trapezium angle=60, minimum width=1cm, draw, very thick
+    },
+    Clock/.pic = {
+        \node [clockborder, shape border rotate=-180](-clockedge){#1};
+        \draw[very thick] (-clockedge.east) -- ++(2cm, 0cm);
+        \def\sft{0.5}
+        \foreach \x in {0, 0.5, 1, 1.5}{
+            \draw[very thick] (\x + \sft, 0.1) -| ++(0.25cm, 0.25cm) -| ++ (0.25cm, -0.25cm);
+        }
+    },
+}
+
 \begin{document}
-    \begin{tikzpicture}[every node/.style={font=\Large}]
+    \begin{tikzpicture}[every node/.style={font=\normalsize}]
         % Place the blocks 
-        \draw pic (b1) {Component={Static\\System}{t}};
-        \draw(3, 0) pic (b2) {Component={Dynamical\\System I}{t}};
-        \draw(3, -2.5) pic (b3) {Component={Dynamical\\System II}{t}};
-        \draw(0, -2.5) pic (b4) {Component={Memory}{t}};
+        \draw(-3.5, 0) pic (gen) {Component={Sinewave\\Generator}{t}};
+        \draw pic (adder) {Component={Adder}{t}};
+        \draw(3.5, 0) pic (ds) {Component={ODESystem}{t}};
+        \draw(7, 1.5) pic (writer) {Component={Writer}{t}};
+        \draw(2, -2.25) pic (memory) {Component={Memory}{t}};
         % Glow the blocks
-        \drawshadowbis{b1-edge};
-        \drawshadowbis{b2-edge};
-        \drawshadowbis{b3-edge};
-        \drawshadowbis{b4-edge};
-        \begin{scope}[line width=1.5mm, >={Triangle[width=3mm,length=3mm]}]
-            \draw[->] ([yshift=2mm, xshift=-1cm] b1-edge.west) -- ([yshift=2mm] b1-edge.west);
-            \draw[->] (b1-edge.east) -- (b2-edge.west);
-            \draw (b2-edge.east) -- ++(0.5cm, 0cm) coordinate (a);
-            \draw[->] (a) -- ++(0.5cm, 0cm);
-            \draw[->] (a) |- (b3-edge.east);
-            \draw[<-] ([yshift=-2mm] b1-edge.west) -- ++(-0.5cm, 0cm) coordinate (b);
-            \draw[-] ([yshift=0.75mm] b) |- (b4-edge.west);
-            \draw[->] (b3-edge.west) |- (b4-edge.east);
+        \drawshadowbis{gen-edge};
+        \drawshadowbis{adder-edge};
+        \drawshadowbis{ds-edge};
+        \drawshadowbis{writer-edge};
+        \drawshadowbis{memory-edge};
+        \begin{scope}[line width=1.5mm, ->, >={Triangle[width=3mm,length=3mm]}]
+            \draw[-] ([yshift=2mm] gen-edge.east) -- ++(1cm, 0cm) node[midway, anchor=south]{$r(t)$} coordinate(d); 
+            \draw (d) -- ([yshift=2mm]  adder-edge.west);
+            \draw (adder-edge.east) -- node[midway, anchor=south]{$u(t)$} (ds-edge.west);
+            \draw[-] (ds-edge.east) -- ++(1cm, 0cm) node[midway, anchor=south]{$y(t)$} coordinate (a);
+            \draw (a) |- ([yshift=-3mm] writer-edge.west);
+            \draw (a) |- (memory-edge.east);
+            \draw[-] (memory-edge.west) -- ++(-2.5cm, 0cm) coordinate (c);
+            \draw ([yshift=-0.75mm] c) |- ([yshift=-2mm] adder-edge.west);
+            \draw (d) |- ([yshift=3mm] writer-edge.west);
         \end{scope}
+        \draw[very thick, dashed] (-5, 3) rectangle (8.5, -4);
+        \node at (7.5, -3.5) {Model};
+
+         % \Place clock 
+        \begin{scope}[shift={(-4.25cm, -3.25cm)}]
+            \draw pic(clk) {Clock={T}} ;
+        \end{scope}
+
     \end{tikzpicture}

### 2020-05-02 docs/make.jl

@@ -4,44 +4,49 @@ using Documenter, Jusdl
 DocMeta.setdocmeta!(Jusdl, :DocTestSetup, :(using Jusdl); recursive=true)
 
 makedocs(
-    modules = [Jusdl], 
-    sitename = "Jusdl",
-    pages = [
+    modules=[Jusdl], 
+    sitename="Jusdl",
+    pages=[
         "Home" => "index.md",
         "Modeling and Simulation in Jusdl" => [
             "modeling_and_simulation/modeling.md",
             "modeling_and_simulation/simulation.md",
-            ],
+        ],
+        "Tutorials" => [
+            "Simple Model Simulation" => "tutorials/simple_model.md",
+            "Breaking Algebraic Loops" => "tutorials/breaking_algebraic_loops.md",
+            "Constuction and Simulation of Subsystems" => "tutorials/construction_and_simulation_of_subsystems.md",
+        ],
         "Manual" => [
             "Utilities" => [
                 "manual/utilities/callback.md",
                 "manual/utilities/buffers.md"
-                ], 
+            ], 
             "Connections" => [
                 "manual/connections/link.md",
                 "manual/connections/pin.md",
                 "manual/connections/port.md",
-                ],
+            ],
             "Components" => [
                 "ComponentsBase" => [
                     "manual/components/componentsbase/evolution.md",
-                    ],
+                    "manual/components/componentsbase/interpolation.md",
+                ],
                 "Sources" => [
                     "manual/components/sources/clock.md",
                     "manual/components/sources/generators.md",
-                    ],
+                ],
                 "Sinks" => [
                     "manual/components/sinks/sinks.md",
                     "manual/components/sinks/writer.md",
                     "manual/components/sinks/printer.md",
                     "manual/components/sinks/scope.md",
-                    ],
+                ],
                 "Systems" => [
                     "StaticSystems" => [
                         "StaticSystems" => "manual/components/systems/staticsystems/staticsystems.md",
                         "Subsystem" => "manual/components/systems/staticsystems/subsystem.md",
-                        # "Network" => "manual/components/systems/staticsystems/network.md",
-                        ],
+                    ],
                     "DynamicSystems" => [
                         "DiscreteSystem" => "manual/components/systems/dynamicsystems/discretesystem.md",
                         "ODESystem" => "manual/components/systems/dynamicsystems/odesystem.md",
@@ -49,24 +54,83 @@ makedocs(
[…]

### 2020-05-02 src/Jusdl.jl

@@ -84,9 +84,9 @@ export DDESystem
 include("components/systems/subsystems/subsystem.jl")
 export SubSystem
 
-include("components/systems/subsystems/network.jl")
-export SubSystem, Network, cgsconnectivity, clusterconnectivity, coupling, signalflow, topology, nodes, numnodes, dimnodes, 
-    deletelink, changeweight, maketimevarying
+# include("components/systems/subsystems/network.jl")
+# export SubSystem, Network, cgsconnectivity, clusterconnectivity, coupling, signalflow, topology, nodes, numnodes, dimnodes, 
+#     deletelink, changeweight, maketimevarying
 
 include("components/sinks/manageplugins.jl")
 export fasten, unfasten

### 2020-05-02 src/components/sinks/printer.jl

@@ -4,7 +4,7 @@ import Base.print
 
 
 """
-   Printer(input::Bus{Union{Missing, T}}, buflen=64, plugin=nothing) where T
+  Printer(input=Inport(); buflen=64, plugin=nothing, callbacks=nothing, name=Symbol()) where T
 
 Constructs a `Printer` with input bus `input`. `buflen` is the length of its internal `buflen`. `plugin` is data proccessing tool.
 """

### 2020-05-02 src/components/sinks/scope.jl

@@ -2,7 +2,7 @@
 
 
 """
-    Scope(input::Bus, buflen::Int=64, plugin=nothing, args...; kwargs...)
+    Scope(input=Inport(), args...; buflen::Int=64, plugin=nothing, callbacks=nothing, name=Symbol(), kwargs...) 
 
 Constructs a `Scope` with input bus `input`. `buflen` is the length of the internal buffer of `Scope`. `plugin` is the additional data processing tool. `args`,`kwargs` are passed into `plots(args...; kwargs...))`. See (https://github.com/JuliaPlots/Plots.jl) for more information.
 

### 2020-05-02 src/components/systems/dynamicalsystems/daesystems.jl

@@ -32,7 +32,7 @@ end
 ```
 
 # Example 
-```jldoctest 
+```julia 
 julia> function sfuncdae(out, dx, x, u, t)
            out[1] = x[1] + 1 - dx[1]
            out[2] = (x[1] + 1) * x[2] + 2

### 2020-05-02 src/components/systems/dynamicalsystems/ddesystems.jl

@@ -30,7 +30,7 @@ function outputfunc(x, u, t)
 end
 ```
 # Example 
-```jldoctest
+```julia
 julia> const out = zeros(1);
 
 julia> histfunc(out, u, t) = (out .= 1.);

### 2020-05-02 src/components/systems/dynamicalsystems/discretesystems.jl

@@ -5,7 +5,7 @@
     DiscreteSystem(input, output, statefunc, outputfunc, state, t, modelargs=(), solverargs=(); 
         alg=DiscreteAlg, modelkwargs=NamedTuple(), solverkwargs=NamedTuple())
 
-Construct a `DiscreteSystem` with `input` and `output`. `statefunc` is the state function and `outputfunc` is the output function of `DiscreteSystem`. `state` is the initial state and `t` is the time. `modelargs` and `modelkwargs` are passed into `ODEProblem` and `solverargs` and `solverkwargs` are passed into `solve` method of `DifferentialEquations`. `alg` is the algorithm to solve the diffence equation of the system.
+Constructs a `DiscreteSystem` with `input` and `output`. `statefunc` is the state function and `outputfunc` is the output function of `DiscreteSystem`. `state` is the initial state and `t` is the time. `modelargs` and `modelkwargs` are passed into `ODEProblem` and `solverargs` and `solverkwargs` are passed into `solve` method of `DifferentialEquations`. `alg` is the algorithm to solve the diffence equation of the system.
 
 The system is represented by
 ```math
@@ -31,7 +31,7 @@ end
 ```
 
 # Example 
-```jldoctest 
+```julia 
 julia> sfuncdiscrete(dx,x,u,t) = (dx .= 0.5x);
 
 julia> ofuncdiscrete(x, u, t) = x;

### 2020-05-02 src/components/systems/dynamicalsystems/odesystems.jl

@@ -31,7 +31,7 @@ end
 ```
 
 # Example 
-```jldoctest
+```julia
 julia> sfuncode(dx,x,u,t) = (dx[1] = 0.5x[1] + u[1](t));
 
 julia> ofuncode(x, u, t) = x;

### 2020-05-02 src/components/systems/dynamicalsystems/rodesystems.jl

@@ -32,7 +32,7 @@ end
 ```
 
 # Example 
-```jldoctest
+```julia
 julia> function sfuncrode(dx, x, u, t, W)
          dx[1] = 2x[1]*sin(W[1] - W[2])
          dx[2] = -2x[2]*cos(W[1] + W[2])
@@ -40,7 +40,7 @@ julia> function sfuncrode(dx, x, u, t, W)
 
 julia> ofuncrode(x, u, t) = x;
 
-julia> RODESystem(sfuncrode, ofuncrode, [1., 1.], 0., solverkwargs=(dt=0.01,), nothing, Outport(2))
+julia> RODESystem(sfuncrode, ofuncrode, [1., 1.], 0., nothing, Outport(2), solverkwargs=(dt=0.01,))
 RODESystem(state:[1.0, 1.0], t:0.0, input:nothing, output:Outport(numpins:2, eltype:Outpin{Float64}))
 ```
 

### 2020-05-02 src/components/systems/dynamicalsystems/sdesystems.jl

@@ -34,7 +34,7 @@ end
 ```
 
 # Example 
-```jldoctest
+```julia
 julia> sfuncdrift(dx, x, u, t) = (dx[1] = -x[1]);
 
 julia> sfuncdiffusion(dx, x, u, t) = (dx[1] = -x[1]);
@@ -66,206 +66,3 @@ end
 show(io::IO, ds::SDESystem) = print(io, 
     "SDESystem(state:$(ds.state), t:$(ds.t), input:$(ds.input), output:$(ds.output))")
 
-##### Noisy Linear System
-
-# mutable struct NoisyLinearSystem{SF, OF, T<:AbstractFloat, IB, OB, SW, B, N, NP} <: AbstractSDESystem
-#     @generic_dynamic_system_fields
-#     noise::N
-#     noise_prototype::NP 
-#     seed::UInt
-#     A::Matrix{Float64}
-#     B::Matrix{Float64}
-#     C::Matrix{Float64}
-#     D::Matrix{Float64}
-#     function NoisyLinearSystem(A, B, C, D, diffusion, outputfunc, state, t, noise, noise_prototype, seed, 
-#         input, solver, solver_kwargs, callbacks, name)
-#         if input == nothing
-#             driftfunc = (dx, x, u, t) -> (dx .= A * x)
-#             outputfunc = (x, u, t) -> (C * x)
-#         else
-#             driftfunc = (dx, x, u, t) -> (dx .= A * x .+ B * u)
-#             if C == nothing || D == nothing
-#                 outputfunc = nothing
-#             else
-#                 outputfunc = (x, u, t) -> (C * x .+ D * u)
-#             end
-#         end
-#         statefunc = (driftfunc, diffusion)
-#         trigger = Link()
-#         output = Bus(infer_number_of_outputs(outputfunc, state, input, t))  
-#         buffer = length(state) == 1 ? Buffer(64) : Buffer(64, length(state))
-#         new{typeof(statefunc), typeof(outputfunc), typeof(t), typeof(input), typeof(output), typeof(solver), 
-#         typeof(buffer), typeof(noise), typeof(noise_prototype)}(statefunc, outputfunc, state, t, input, output, solver, solver_kwargs, buffer, trigger, callbacks, name, noise, noise_prototype, seed, A, B, C, D)
-#     end
-# end
[…]

### 2020-05-02 src/components/systems/staticsystems/staticsystems.jl

@@ -36,7 +36,7 @@ end
 
 
 @doc raw"""
-    Adder(input::Bus[, signs])
+    Adder(signs=(+,+))
 
 Construts an `Adder` with input bus `input` and signs `signs`. `signs` is a tuplle of `+` and/or `-`. The output function `g` of `Adder` is of the form,
 ```math 
@@ -69,7 +69,7 @@ end
 
 
 @doc raw"""
-    Multiplier(input::Bus[, ops])
+    Multiplier(ops=(*,*))
 
 Construts an `Multiplier` with input bus `input` and signs `signs`. `signs` is a tuplle of `*` and/or `/`. The output function `g` of `Multiplier` is of the form,
 ```math 
@@ -142,7 +142,7 @@ end
 
 
 @doc raw"""
-    Terminator(input::Bus)
+    Terminator(input::Inport)
 
 Constructs a `Terminator` with input bus `input`. The output function `g` is eqaul to `nothing`. A `Terminator` is used just to sink the incomming data flowing from its `input`.
 """

### 2020-05-02 src/components/systems/subsystems/subsystem.jl

@@ -11,7 +11,7 @@ Constructs a `SubSystem` consisting of `components`. `input` and `output` determ
 ```jldoctest 
 julia> adder = Adder((+,-));
 
-julia> gain = Gain(); 
+julia> gain = Gain();
 
 julia> gen = ConstantGenerator();
 
@@ -20,7 +20,7 @@ julia> connect(gen.output, adder.input);
 julia> connect(adder.output, gain.input);
 
 julia> ss = SubSystem([gen, adder, gain], adder.input[1], gain.output)
-SubSystem(input:Inpin(eltype:Float64, isbound:true), output:Outport(numpins:1, eltype:Outpin{Float64}), components:AbstractComponent[ConstantGenerator(amp:1.0), Adder(signs:(+, -), input:Inport(numpins:2, eltype:Inpin{Float64}), output:Outport(numpins:1, eltype:Outpin{Float64})), Gain(gain:1.0, input:Inport(numpins:1, eltype:Inpin{Float64}), output:Outport(numpins:1, eltype:Outpin{Float64}))])
+SubSystem(input:Inport(numpins:1, eltype:Inpin{Float64}), output:Outport(numpins:1, eltype:Outpin{Float64}), components:AbstractComponent[ConstantGenerator(amp:1.0), Adder(signs:(+, -), input:Inport(numpins:2, eltype:Inpin{Float64}), output:Outport(numpins:1, eltype:Outpin{Float64})), Gain(gain:1.0, input:Inport(numpins:1, eltype:Inpin{Float64}), output:Outport(numpins:1, eltype:Outpin{Float64}))])
 ```
 """
 mutable struct SubSystem{IB, OB, TR, HS, CB, CP, TP, HP} <: AbstractSubSystem
@@ -38,8 +38,8 @@ mutable struct SubSystem{IB, OB, TR, HS, CB, CP, TP, HP} <: AbstractSubSystem
             connect(triggerport[k], component.trigger)
             connect(component.handshake, handshakeport[k])
         end
-        inputport = typeof(input) <: AbstractVector{<:Inpin} ? Inport(input) : input  
-        outputport = typeof(output) <: AbstractVector{<:Outpin} ? Outport(output) : output
+        inputport = typeof(input) <: Union{<:Inpin, AbstractVector{<:Inpin}} ? Inport(input) : input  
+        outputport = typeof(output) <: Union{<:Outpin, AbstractVector{<:Outpin}} ? Outport(output) : output
[…]

### 2020-05-02 src/connections/port.jl

@@ -12,7 +12,7 @@ abstract type AbstractPort{P} <: AbstractVector{P} end
 """
     Outport{T}(numpins=1) 
 
-Constructs an `Outport` with `numpins` [`Outpins`](@ref).
+Constructs an `Outport` with `numpins` [`Outpin`](@ref).
 
 !!! warning
     Element type of an `Outport` must be `Outpin`. See also [`Outpin`](@ref)
@@ -34,6 +34,7 @@ struct Outport{P} <: AbstractPort{P}
     id::UUID
     Outport(pins::AbstractVector{P}) where {T, P<:Outpin{T}} = new{P}(pins, uuid4())
 end
+Outport(pin::Outpin) = Outport([pin])
 Outport{T}(numpins::Int=1) where T = Outport([Outpin{T}() for i = 1 : numpins]) 
 Outport(numpins::Int=1) = Outport{Float64}(numpins)
 
@@ -44,7 +45,7 @@ show(io::IO, outport::Outport) = print(io, "Outport(numpins:$(length(outport)), 
 """
     Inport{T}(numpins=1) 
 
-Constructs an `Inport` with `numpins` [`Inpins`](@ref).
+Constructs an `Inport` with `numpins` [`Inpin`](@ref).
 
 !!! warning
     Element type of an `Inport` must be `Inpin`. See also [`Inpin`](@ref)
@@ -65,6 +66,7 @@ struct Inport{P} <: AbstractPort{P}
     pins::Vector{P}
     Inport(pins::AbstractVector{P}) where {T, P<:Inpin{T}} = new{P}(pins)
 end
+Inport(pin::Inpin) = Inport([pin])
 Inport{T}(numpins::Int=1) where T = Inport([Inpin{T}() for i = 1 : numpins])
 Inport(numpins::Int=1) = Inport{Float64}(numpins)
 

### 2020-05-02 src/models/model.jl

@@ -357,7 +357,7 @@ end
 """
     initialize(model::Model)
 
-Initializes `model` by launching component task for each of the component of `model`. The pairs component and component tasks are recordedin the task manager of the `model`. See also: [`ComponentTask`](@ref), [`TaskManager`](@ref). The `model` clock is [`set!`](@ref) and the files of [`Writer`](@ref) are openned.
+Initializes `model` by launching component task for each of the component of `model`. The pairs component and component tasks are recordedin the task manager of the `model`. The `model` clock is [`set!`](@ref) and the files of [`Writer`](@ref) are openned.
 """
 function initialize(model::Model)
     pairs = model.taskmanager.pairs
@@ -388,7 +388,6 @@ Runs the `model` by triggering the components of the `model`. This triggering is
 
 !!! warning 
     The `model` must first be initialized to be `run`. See also: [`initialize`](@ref).
-```
 """
 function run(model::Model, withbar::Bool=true)
     taskmanager = model.taskmanager
@@ -409,7 +408,7 @@ end
 """
     terminate(model::Model)
 
-Terminates `model` by terminating all the components of the `model`, i.e., the components tasks in the task manager of the `model` is terminated. See also: [`ComponentTask`](@ref), [`TaskManager`](@ref).
+Terminates `model` by terminating all the components of the `model`, i.e., the components tasks in the task manager of the `model` is terminated.
 """
 function terminate(model::Model)
     taskmanager = model.taskmanager

### 2020-05-02 src/models/taskmanager.jl

@@ -1,28 +1,4 @@
-# # This file is for TaskManager object.
-
-# """
-#     ComponentTask(triggertask, outputtask)
-
-# Constructs a `ComponentTask` from `triggertask` and `outputtask`. `triggertask` is the task constructed for the evolution of components and `outputtask` task is contructed to make the output busses of the components writable. 
-
-# # Example
-# ```julia 
-# julia> gen = SinewaveGenerator()
-# SinewaveGenerator(amp:1.0, freq:1.0, phase:0.0, offset:0.0, delay:0.0)
-
-# julia> taskpair = launch(gen)
-# (Task (runnable) @0x00007f4de65544f0, Task (runnable) @0x00007f4de5e8fd00)
-
-# julia> comptask = ComponentTask(taskpair)
-# ComponentTask{Task,Task}(Task (runnable) @0x00007f4de65544f0, Task (runnable) @0x00007f4de5e8fd00)
-# ```
-# """
-# struct ComponentTask{T, S}
-#     triggertask::T 
-#     outputtask::S 
-# end
-# ComponentTask(tasks::Tuple) = ComponentTask(tasks...)
-# ComponentTask(tasks::AbstractVector{<:Tuple}) = [ComponentTask.(tasks...)...]
+# This file is for TaskManager object.
 
 """
     TaskManager(pairs)
@@ -78,7 +54,7 @@ Returns `false`.
 
     istaskfailed(comptask::ComponentTask)
 
-Returns `true` is `triggertask` or `outputtask` of `comptask` is failed. See also: [`ComponentTask`](@ref)
+Returns `true` is `triggertask` or `outputtask` of `comptask` is failed.
 """
 # function istaskfailed end
 # istaskfailed(task::Nothing) = false
@@ -95,7 +71,7 @@ Returns `true`
 
     istaskrunning(comptask::ComponentTask)
 
-Returns `true` if `triggertask` and `outputtask` of `comptask` is running. See also: [`ComponentTask`](@ref)
+Returns `true` if `triggertask` and `outputtask` of `comptask` is running. 
 """
 function istaskrunning end
 istaskrunning(task::Task) = task.state == :runnable
@@ -109,7 +85,7 @@ istaskrunning(task::Task) = task.state == :runnable
 
 #     istaskdone(comptask::ComponentTask)
 
-# Returns `true` if the state of `triggertask` and `outputtask` of `comptask` is `done`. See also: [`ComponentTask`](@ref)
[…]

### 2020-05-02 src/plugins/essentials/fft.jl

@@ -19,7 +19,7 @@ show(io::IO, plg::Fft) = print(io, "Fft(dims:$(plg.dims))")
 Performes an `fft` transformation for the input data `x`.
 
 # Example
-```jldoctest 
+```julia 
 julia> x = collect(reshape(1:16, 4,4))
 4×4 Array{Int64,2}:
  1  5   9  13

### 2020-05-02 src/plugins/essentials/lyapunov.jl

@@ -25,7 +25,7 @@ show(io::IO, plg::Lyapunov) = print(io,
 Computes the maximum Lyapunov exponent of the input data `x`. 
 
 # Example
-```jldoctest 
+```julia 
 julia> using Random 
 
 julia> rng = MersenneTwister(1234);

### 2020-05-02 src/plugins/essentials/mean.jl

@@ -19,7 +19,7 @@ show(io::IO, plg::Mean) = print(io, "Mean(dims:$(plg.dims))")
 Returns the means of `x` along the dimension `plg.dims`.
 
 # Example
-```jldoctest
+```julia
 julia> x = collect(reshape(1:16, 4,4))
 4×4 Array{Int64,2}:
  1  5   9  13

### 2020-05-02 src/plugins/essentials/std.jl

@@ -20,7 +20,7 @@ show(io::IO, plg::Std) = print(io, "Mean(dims:$(plg.dims))")
 Returns the standard deviation of `x` along the dimension `plg.dims`.
 
 # Example 
-```jldoctest 
+```julia 
 julia> x = collect(reshape(1:16, 4,4))
 4×4 Array{Int64,2}:
  1  5   9  13

### 2020-05-02 src/plugins/essentials/variance.jl

@@ -20,7 +20,7 @@ show(io::IO, plg::Variance) = print(io, "Mean(dims:$(plg.dims))")
 Returns the standard deviation of `x` along the dimension `plg.dims`.
 
 # Example 
-```jldoctest 
+```julia 
 julia> x = collect(reshape(1:16, 4,4))
 4×4 Array{Int64,2}:
  1  5   9  13

### 2020-05-02 src/utilities/constants.jl

@@ -1,23 +1,23 @@
 # This file includes the package-wide defaults.
 
-"""Number of taps of buffers used for interpolations"""
+# Number of taps of buffers used for interpolations
 const numtaps = 3
 
-"""DiscreteSystem default solver algorithm."""
+# DiscreteSystem default solver algorithm.
 const DiscreteAlg = FunctionMap()
 
-"""ODESystem default algorithm."""
+# ODESystem default algorithm.
 const ODEAlg = Tsit5()
 
-"""DDESystem default solver algorithm."""
+# DDESystem default solver algorithm.
 const DDEAlg = MethodOfSteps(Tsit5())
 
-"""DAESystem default solver algorithm"""
+# DAESystem default solver algorithm
 const DAEAlg = IDA()
 
-"""RODESystem default solver algorithm"""
+# RODESystem default solver algorithm
 const RODEAlg = RandomEM()
 
-"""SDESysttem default solver algorithm"""
+# SDESysttem default solver algorithm
 const SDEAlg = LambaEM{true}()
 

### 2020-05-02 docs/build/assets/SimpleModel/simplemodel.tex
Added tutorials to docs.

--- 2020-01-11 docs/src/assets/Model/model.tex
@@
 
-\def\mw{2cm}
-\def\mh{1.75cm}
-\def\trianglecoordinate{2mm}
-
-\newcommand\drawshadowbis[1]{
-    \begin{pgfonlayer}{shadow}
-        \fill[inner color=black,outer color=white] ($(#1.south west)$) circle (\shadowradius);
-        \fill[inner color=black ,outer color=white] ($(#1.north west)$) circle (\shadowradius);
-        \fill[inner color=black ,outer color=white] ($(#1.south east)$) circle (\shadowradius);
-        \fill[inner color=black,outer color=white] ($(#1.north east)$) circle (\shadowradius);
-        \fill[ top color=black, bottom color=white] ($(#1.south west)+((0,-\shadowradius)$) rectangle ($(#1.south east)$);
-        \fill[left color=black,right color=white] ($(#1.south east)$) rectangle ($(#1.north east)+((\shadowradius,0)$);
-        \fill[bottom color=black,top color=white] ($(#1.north west)$) rectangle ($(#1.north east)+((0,\shadowradius)$);
-        \fill[right color=black,left color=white] ($(#1.south west)$) rectangle ($(#1.north west)+(-\shadowradius,0)$);
-    \end{pgfonlayer}
-    }
+\def\mw{1.25cm}
+\def\mh{1cm}
 
@@
     border/.style = { 
-        draw, rectangle, minimum width=\mw, minimum height=\mh, thick, align=center
+        draw, rectangle, minimum width=\mw, minimum height=\mh, thick, align=center, ultra thick
     },
@@
         \node [border](-edge){#1}; 
-        \draw[thick] ([xshift=\trianglecoordinate] -edge.south) -- ([yshift=\trianglecoordinate] -edge.south);
-        \draw[thick] ([xshift=-\trianglecoordinate] -edge.south) -- ([yshift=\trianglecoordinate] -edge.south);
-        \draw[thick] (-edge.south) |- ++(-3mm, -4mm) node[xshift=-2mm, yshift=-1mm] {T}; 
     },
@@
 \begin{document}
-    \begin{tikzpicture}[every node/.style={font=\large}]
+    \begin{tikzpicture}
         % Place the blocks 
-        \matrix (m) [matrix of nodes, ampersand replacement=\&, column sep = 1.5cm, row sep = -1cm]{
-                                            \& \draw pic (b1) {Component={B1}}; \&                                  \\
-        \draw pic (b2) {Component={B2}};    \&                                  \& \draw pic (b3) {Component={B3}}; \\
-                                            \& \draw pic (b4) {Component={B4}}; \&                                  \\[1.25cm]
-                                            \& \draw pic (b5) {Component={B5}}; \&                                  \\
+        \matrix (m) [
+            matrix of nodes, 
+            ampersand replacement=\&, 
+            column sep = 1cm, 
+            row sep = 1cm, 
+            nodes={
+                text height=1.5ex,
+                text depth=.25ex,
+                anchor=center}
+                ]{
+                    \draw pic (gen) {Component={gen}}; \& \draw pic (adder) {Component={adder}}; \& \draw pic (gain) {Component={gain}}; \& \draw pic (writer) {Component={writer}}; \\
                 };
-        % Glow the blocks
-        \foreach \x in {1, 2, 3, 4, 5}{
-            \drawshadowbis{b\x-edge};
-        }
+
         % Draw connections 
-        \begin{scope}[line width=2mm, >={Triangle[width=4mm,length=4mm]}]
+        \begin{scope}[line width=1.5mm, >={Triangle[width=4mm,length=3mm]}]
             \def\shiftamount{0.5mm};
-            \draw[-] (b2-edge.east) -- ++(0.5cm, 0cm) coordinate(a);
-            \draw[-] (a) -- node[midway, anchor=west]{L1} ++(0, 0.5*\mh) coordinate(b);
-            \draw[-] (a) -- node[midway, anchor=west]{L2} ++(0cm, -0.5*\mh) coordinate(c);
-            \draw[->] (b) |- (b1-edge.west);
-            \draw[->] (c) |- ([yshift=0.25cm] b4-edge.west);
-            \draw[-] (b1-edge.east) -- ++(0.4*\mw, 0cm) coordinate(d);
-            \draw[-] (b4-edge.east) -- ++(0.4*\mw, 0cm) coordinate(e);
-            \draw[-] ([yshift=1mm] d) -- node[midway, anchor=east]{L3} ++(0cm, -0.7*\mh) coordinate(f);
-            \draw[-] ([yshift=-1mm] e) -- node[midway, anchor=east]{L4} ++(0cm, 0.7*\mh) coordinate(g);
-            \draw[->] ([yshift=\shiftamount] f) |- ([yshift=2mm] b3-edge.west);
-            \draw[->] ([yshift=-\shiftamount] g) |- ([yshift=-2mm] b3-edge.west);
-            \draw (b5-edge.west) -- ++(-1cm, 0cm) coordinate (h);
-            \draw[->] ([yshift=-1mm] h) |- node[midway, anchor=east, yshift=-1.25cm]{L6}  ([yshift=-0.25cm] b4-edge.west);
-            \draw[->] ([yshift=1mm] g) |- node[midway, anchor=east, yshift=1.25cm]{L5} (b5-edge.east);
+            \draw[->] (gen-edge.east) -- (adder-edge.west);
+            \draw[->] (adder-edge.east) -- (gain-edge.west);
+            \draw[->] (gain-edge.east) -- (writer-edge.west);
+            \draw[->] (gain-edge.east) -- (writer-edge.west);
+            \draw[-] (gain-edge.east) -| ++ (0.3cm, -1.5cm) coordinate (a);
+            \draw[->] ([yshift=0.75mm] a) -| (adder-edge.south);
         \end{scope}
@@
         % \Place clock 
-        \begin{scope}[shift={(-4.25cm, -4cm)}]
+        \begin{scope}[shift={(-4cm, -2cm)}]
             \draw pic(clk) {Clock={T}} ;
@@
         %  Draw rectangle 
-        \draw[dashed, thick] ([xshift=-0.25*\mw, yshift=-0.25*\mh] clk-clockedge.south west) rectangle ([xshift=2*\mw, yshift=0.25*\mh] b1-edge.north east);
-        \draw (b3-edge.south) node[yshift=-2.75*\mh, xshift=0.4*\mw]{Model};
+        \draw[dashed, thick] (-4.5, -3) rectangle (4.5, 1);
+        \draw (0,0) node[yshift=-2.5cm, xshift=3.5cm]{Model};
     \end{tikzpicture}

### 2020-05-02 docs/make.jl

@@ -13,6 +13,7 @@ makedocs(
             "modeling_and_simulation/simulation.md",
         ],
         "Tutorials" => [
+            "Models and Graphs" => "tutorials/models_and_graphs.md",
             "Simple Model Simulation" => "tutorials/simple_model.md",
             "Breaking Algebraic Loops" => "tutorials/breaking_algebraic_loops.md",
             "Constuction and Simulation of Subsystems" => "tutorials/construction_and_simulation_of_subsystems.md",

### 2020-05-02 src/Jusdl.jl

@@ -108,7 +108,7 @@ export Simulation, SimulationError, setlogger, closelogger, report
 
 include("models/model.jl")
 export Model, getloops, breakloop, inspect, initialize, run, terminate, simulate
-export Node, Branch, addnode, getnode, addbranch, getbranch, deletebranch
+export Node, Branch, addnode, getnode, addbranch, getbranch, deletebranch, signalflow
 
 include("plugins/loadplugins.jl")
 export AbstractPlugin, process, add, remove, enable, disable, check

### 2020-05-03 docs/make.jl
Revised docs.

@@ -13,10 +13,10 @@ makedocs(
             "modeling_and_simulation/simulation.md",
         ],
         "Tutorials" => [
-            "Models and Graphs" => "tutorials/models_and_graphs.md",
-            "Simple Model Simulation" => "tutorials/simple_model.md",
-            "Breaking Algebraic Loops" => "tutorials/breaking_algebraic_loops.md",
-            "Constuction and Simulation of Subsystems" => "tutorials/construction_and_simulation_of_subsystems.md",
+            "Model Constuction" => "tutorials/model_construction.md",
+            "Model Simulation" => "tutorials/model_simulation.md",
+            "Algebraic Loops" => "tutorials/algebraic_loops.md",
+            "Subsystems" => "tutorials/subsystems.md",
         ],
         "Manual" => [
             "Utilities" => [

### 2020-05-03 docs/build/assets/AlgebraicLoop/algebraicloop.tex
Revised docs.

--- 2020-05-02 docs/build/assets/SimpleModel/simplemodel.tex
@@
             column sep = 1cm, 
-            row sep = 1cm, 
+            row sep = 0.5cm, 
             nodes={
@@
                 ]{
-                    \draw pic (gen) {Component={gen}}; \& \draw pic (adder) {Component={adder}}; \& \draw pic (gain) {Component={gain}}; \& \draw pic (writer) {Component={writer}}; \\
+                     \& \draw pic (writerin) {Component={writerin}}; \& \&  \\
+                    \draw pic (gen) {Component={gen}}; \& \draw pic (adder) {Component={adder}}; \& \draw pic (gain) {Component={gain}}; \& \draw pic (writerout) {Component={writerout}}; \\
                 };
@@
             \def\shiftamount{0.5mm};
-            \draw[->] (gen-edge.east) -- (adder-edge.west);
-            \draw[->] (adder-edge.east) -- (gain-edge.west);
-            \draw[->] (gain-edge.east) -- (writer-edge.west);
-            \draw[->] (gain-edge.east) -- (writer-edge.west);
+            \draw[->] (gen-edge.east) -- node[midway, anchor=north]{$r(t)$} (adder-edge.west);
+            \draw[->] (adder-edge.east) -- node[midway, anchor=north]{$u(t)$} (gain-edge.west);
+            \draw[->] (gain-edge.east) -- (writerout-edge.west);
+            \draw[->] (gain-edge.east) -- (writerout-edge.west);
             \draw[-] (gain-edge.east) -| ++ (0.3cm, -1.5cm) coordinate (a);
-            \draw[->] ([yshift=0.75mm] a) -| (adder-edge.south);
+            \draw[->] ([yshift=0.75mm] a) -| node[midway, xshift=1.75cm, anchor=north]{$y(t)$} (adder-edge.south);
+            \draw[-] (gen-edge.east) -- ++(0.5cm, 0cm) coordinate(b);
+            \draw[->] (b) |- (writerin-edge.west);
         \end{scope}
@@
         % \Place clock 
-        \begin{scope}[shift={(-4cm, -2cm)}]
+        \begin{scope}[shift={(-4.5cm, -2.25cm)}]
             \draw pic(clk) {Clock={T}} ;
@@
         %  Draw rectangle 
-        \draw[dashed, thick] (-4.5, -3) rectangle (4.5, 1);
-        \draw (0,0) node[yshift=-2.5cm, xshift=3.5cm]{Model};
+        \draw[dashed, thick] (-5, -3) rectangle (5, 1.5);
+        \draw (0,0) node[yshift=-2.5cm, xshift=4cm]{Model};
     \end{tikzpicture}

### 2020-05-03 docs/src/assets/CoupledSystem/coupledsystem.tex
Revised docs.

--- 2020-05-02 docs/build/assets/SimpleModel/simplemodel.tex
@@
             ampersand replacement=\&, 
-            column sep = 1cm, 
-            row sep = 1cm, 
+            column sep = 1.5cm, 
+            row sep = 0cm, 
             nodes={
@@
                 ]{
-                    \draw pic (gen) {Component={gen}}; \& \draw pic (adder) {Component={adder}}; \& \draw pic (gain) {Component={gain}}; \& \draw pic (writer) {Component={writer}}; \\
+                   \& \draw pic (ds1) {Component={ds1}}; \&  \\
+                   \draw pic (writer) {Component={writer}}; \& \& \draw pic (coupler) {Component={coupler}}; \\
+                   \& \draw pic (ds2) {Component={ds2}}; \&  \\
                 };
@@
             \def\shiftamount{0.5mm};
-            \draw[->] (gen-edge.east) -- (adder-edge.west);
-            \draw[->] (adder-edge.east) -- (gain-edge.west);
-            \draw[->] (gain-edge.east) -- (writer-edge.west);
-            \draw[->] (gain-edge.east) -- (writer-edge.west);
-            \draw[-] (gain-edge.east) -| ++ (0.3cm, -1.5cm) coordinate (a);
-            \draw[->] ([yshift=0.75mm] a) -| (adder-edge.south);
+            \draw[-] (ds1-edge.east) -| ++ (0.5cm, -0.75cm) coordinate(a);
+            \draw[-] (ds2-edge.east) -| ++ (0.5cm, 0.75cm) coordinate(b);
+            \draw[->] ([yshift=0.75mm]a) |- ([yshift=0.25cm]coupler-edge.west);
+            \draw[->] ([yshift=-0.75mm]b) |- ([yshift=-0.25cm]coupler-edge.west);
+            \draw[-] ([yshift=0.25cm]coupler-edge.east) -| ++ (1cm, 2cm) coordinate(c);
+            \draw[-] ([yshift=-0.25cm]coupler-edge.east) -| ++ (1cm, -2cm) coordinate(d);
+            \draw[-] ([yshift=-0.75mm]c) -- ++(-6cm, 0cm) coordinate(e);
+            \draw[-] ([yshift=0.75mm]d) -- ++(-6cm, 0cm) coordinate(f);
+            \draw[->] ([yshift=0.75mm] e) |- (ds1-edge.west);
+            \draw[->] ([yshift=-0.75mm] f) |- (ds2-edge.west);
+            \draw[->] (a) |- ([yshift=2.5mm]writer-edge.east);
+            \draw[->] (b) |- ([yshift=-2.5mm]writer-edge.east);
         \end{scope}
@@
         % \Place clock 
-        \begin{scope}[shift={(-4cm, -2cm)}]
+        \begin{scope}[shift={(-4.25cm, -2cm)}]
             \draw pic(clk) {Clock={T}} ;
@@
         %  Draw rectangle 
-        \draw[dashed, thick] (-4.5, -3) rectangle (4.5, 1);
-        \draw (0,0) node[yshift=-2.5cm, xshift=3.5cm]{Model};
+        \draw[dashed, thick] (-5, -3) rectangle (5, 2.5);
+        \draw (0,0) node[yshift=-2.75cm, xshift=4cm]{Model};
     \end{tikzpicture}

### 2020-05-03 docs/src/assets/GeneratorWriter/generatorwriter.tex
Revised docs.

--- 2020-05-02 docs/build/assets/SimpleModel/simplemodel.tex
@@
                 ]{
-                    \draw pic (gen) {Component={gen}}; \& \draw pic (adder) {Component={adder}}; \& \draw pic (gain) {Component={gain}}; \& \draw pic (writer) {Component={writer}}; \\
+                    \draw pic (gen) {Component={gen}}; \& \draw pic (writer) {Component={writer}}; \\
                 };
@@
             \def\shiftamount{0.5mm};
-            \draw[->] (gen-edge.east) -- (adder-edge.west);
-            \draw[->] (adder-edge.east) -- (gain-edge.west);
-            \draw[->] (gain-edge.east) -- (writer-edge.west);
-            \draw[->] (gain-edge.east) -- (writer-edge.west);
-            \draw[-] (gain-edge.east) -| ++ (0.3cm, -1.5cm) coordinate (a);
-            \draw[->] ([yshift=0.75mm] a) -| (adder-edge.south);
+            \draw[->] (gen-edge.east) -- (writer-edge.west);
         \end{scope}
@@
         % \Place clock 
-        \begin{scope}[shift={(-4cm, -2cm)}]
+        \begin{scope}[shift={(-2cm, -1.5cm)}]
             \draw pic(clk) {Clock={T}} ;
@@
         %  Draw rectangle 
-        \draw[dashed, thick] (-4.5, -3) rectangle (4.5, 1);
-        \draw (0,0) node[yshift=-2.5cm, xshift=3.5cm]{Model};
+        \draw[dashed, thick] (-2.5, -2.25) rectangle (2.5, 1);
+        \draw (0,0) node[yshift=-2cm, xshift=1.75cm]{Model};
     \end{tikzpicture}

### 2020-05-03 docs/make.jl

@@ -13,10 +13,11 @@ makedocs(
             "modeling_and_simulation/simulation.md",
         ],
         "Tutorials" => [
-            "Model Constuction" => "tutorials/model_construction.md",
+            "Model Construction" => "tutorials/model_construction.md",
             "Model Simulation" => "tutorials/model_simulation.md",
             "Algebraic Loops" => "tutorials/algebraic_loops.md",
             "Subsystems" => "tutorials/subsystems.md",
+            "Coupled Systems" => "tutorials/coupled_systems.md",
         ],
         "Manual" => [
             "Utilities" => [

### 2020-05-03 example/breaking_loop_of_complex_model.jl

@@ -4,27 +4,24 @@ using Jusdl
 using Plots; pyplot() 
 
 model = Model() 
-addnode(model, SinewaveGenerator(frequency=2), label=:gen)
-addnode(model, SinewaveGenerator(frequency=3), label=:gen2)
-addnode(model, Adder((+, +)), label=:adder2)
+addnode(model, SinewaveGenerator(frequency=2), label=:gen1)
 addnode(model, Gain(gain=1), label=:gain1)
-addnode(model, Adder((+,-, +)), label=:adder)
+addnode(model, Adder((+,+)), label=:adder1)
+addnode(model, SinewaveGenerator(frequency=3), label=:gen2)
+addnode(model, Adder((+, +, -)), label=:adder2)
 addnode(model, Gain(gain=1), label=:gain2)
+addnode(model, Writer(), label=:writer)
 addnode(model, Gain(gain=1), label=:gain3)
-addnode(model, Writer(Inport(2)), label=:writer)
-addbranch(model, :gen => :gain1, 1 => 1)
-addbranch(model, :gain1 => :adder, 1 => 1)
-addbranch(model, :gen2 => :adder2, 1 => 1)
-addbranch(model, :gen => :adder2, 1 => 2)
-addbranch(model, :adder => :gain2, 1 => 1)
+addbranch(model, :gen1 => :gain1, 1 => 1)
+addbranch(model, :gain1 => :adder1, 1 => 1)
+addbranch(model, :adder1 => :adder2, 1 => 1)
+addbranch(model, :gen2 => :adder1, 1 => 2)
+addbranch(model, :gen2 => :adder2, 1 => 2)
+addbranch(model, :adder2 => :gain2, 1 => 1)
+addbranch(model, :gain2 => :writer, 1 => 1)
 addbranch(model, :gain2 => :gain3, 1 => 1)
-addbranch(model, :gain3 => :adder, 1 => 2)
-addbranch(model, :adder2 => :adder, 1 => 3)
-addbranch(model, :gen => :writer, 1 => 1)
-addbranch(model, :gain2 => :writer, 1 => 2)
+addbranch(model, :gain3 => :adder2, 1 => 3)
 
-display(signalflow(model, linetype="curve"))
 simulate(model)
 t, x = read(getnode(model, :writer).component)
-plot(t, x[:, 1], label=:gen)
-plot!(t, x[:, 2], label=:gain)
+plot(t, x)

### 2020-05-03 src/models/model.jl

@@ -182,6 +182,10 @@ function inspect(model, breakpoints::Vector{Int}=Int[])
         @info msg
         while !isempty(loops)
             loop = popfirst!(loops)
+            if hasmemory(model, loop)
+                @info "\tLoop $loop has a Memory component.  The loops is broken"
+                continue
+            end
             breakpoint = isempty(breakpoints) ? length(loop) : popfirst!(breakpoints)
             breakloop(model, loop, breakpoint)
             @info "\tLoop $loop is broken"
@@ -190,6 +194,7 @@ function inspect(model, breakpoints::Vector{Int}=Int[])
     end
 end
 
+hasmemory(model, loop) = any([getnode(model, idx).component isa Memory for idx in loop])
 
 """
     getloops(model)

### 2020-05-03 docs/build/assets/ModelGraph/modelgraph.tex

--- 2020-05-03 docs/src/assets/GeneratorWriter/generatorwriter.tex
@@
 
-\def\mw{1.25cm}
-\def\mh{1cm}
+\def\mw{1.5cm}
+\def\mh{1.25cm}
 
@@
             ampersand replacement=\&, 
-            column sep = 1cm, 
+            column sep = 0.75cm, 
             row sep = 1cm, 
@@
                 ]{
-                    \draw pic (gen) {Component={gen}}; \& \draw pic (writer) {Component={writer}}; \\
+                    \draw pic (gen1) {Component={gen1}}; \& \draw pic (gain1) {Component={gain1}}; \& \draw pic (adder1) {Component={adder1}}; \& 
+                                         \&                                  \&                                  \\
+                    \draw pic (gen2) {Component={gen2}}; \&                                  \&                                  \& 
+                    \draw pic (adder2) {Component={adder2}}; \& \draw pic (gain2) {Component={gain2}}; \& \draw pic (writer) {Component={writer}}; \\
+                                         \&                                  \&                                  \& 
+                                         \& \draw[xshift=-1cm] pic (gain3) {Component={gain3}}; \&                                  \\
                 };
@@
         % Draw connections 
-        \begin{scope}[line width=1.5mm, >={Triangle[width=4mm,length=3mm]}]
+        \begin{scope}[line width=2mm, >={Triangle[width=4mm,length=3mm]}]
             \def\shiftamount{0.5mm};
-            \draw[->] (gen-edge.east) -- (writer-edge.west);
+            \draw[->] (gen1-edge.east) -- (gain1-edge.west);
+            \draw[->] (gain1-edge.east) -- (adder1-edge.west);
+            \draw[->] (adder1-edge.east) -| (adder2-edge.north);
+            \draw[-] (gen2-edge.east) -- ++ (4cm, 0.02cm) coordinate(a);
+            \draw[->] (a) -| (adder1-edge.south);
+            \draw[->] (a) -- (adder2-edge.west);
+            \draw[->] (adder2-edge.east) -- (gain2-edge.west);
+            \draw[-] (gain2-edge.east) -- ++ (0.25cm, 0.0cm) coordinate(b);
+            \draw[->] (b) |- (gain3-edge.east);
+            \draw[->] (b) |- (writer-edge.west);
+            \draw[->] (gain3-edge.west) -| (adder2-edge.south);
         \end{scope}
@@
         % \Place clock 
-        \begin{scope}[shift={(-2cm, -1.5cm)}]
+        \begin{scope}[shift={(-6.5cm, -2cm)}]
             \draw pic(clk) {Clock={T}} ;
@@
         %  Draw rectangle 
-        \draw[dashed, thick] (-2.5, -2.25) rectangle (2.5, 1);
-        \draw (0,0) node[yshift=-2cm, xshift=1.75cm]{Model};
+        \draw[dashed, thick] (-7.5, -3.5) rectangle (7.5, 3.5);
+        \draw (0,0) node[yshift=-3cm, xshift=6.5cm]{Model};
     \end{tikzpicture}

### 2020-05-03 src/components/sources/clock.jl
Update README

@@ -147,7 +147,7 @@ end
 Pauses `clk`. When paused, the current time of `clk` does not advance.
 
 # Example
-```jldoctest
+```julia
 julia> clk = Clock(0., 0.1, 0.5);
 
 julia> set!(clk);

### 2020-05-04 v0.1.2/assets/AlgebraicLoopWithMemory/algebraicloopwithmemory.tex
build based on e8a0348

--- 2020-05-03 docs/build/assets/AlgebraicLoop/algebraicloop.tex
@@
                 ]{
-                     \& \draw pic (writerin) {Component={writerin}}; \& \&  \\
-                    \draw pic (gen) {Component={gen}}; \& \draw pic (adder) {Component={adder}}; \& \draw pic (gain) {Component={gain}}; \& \draw pic (writerout) {Component={writerout}}; \\
+                     \& \draw pic (writerin) {Component={writerin}}; \& \& \&  \\
+                     \draw pic (gen) {Component={gen}}; \& \draw pic (adder) {Component={adder}}; \& \& \draw pic (gain) {Component={gain}}; \& \draw pic (writerout) {Component={writerout}}; \\
+                     \& \& \draw pic (memory) {Component={Memory}}; \& \&  \\
                 };
@@
             \draw[-] (gain-edge.east) -| ++ (0.3cm, -1.5cm) coordinate (a);
-            \draw[->] ([yshift=0.75mm] a) -| node[midway, xshift=1.75cm, anchor=north]{$y(t)$} (adder-edge.south);
+            \draw[->] ([yshift=0.75mm] a) |- node[midway, xshift=-1cm, anchor=north]{$y(t)$} (memory-edge.east);
+            \draw[->] (memory-edge.west) -| node[midway, xshift=1cm, anchor=north]{$\hat{y}(t)$} (adder-edge.south);
             \draw[-] (gen-edge.east) -- ++(0.5cm, 0cm) coordinate(b);
@@
         % \Place clock 
-        \begin{scope}[shift={(-4.5cm, -2.25cm)}]
+        \begin{scope}[shift={(-5cm, -3cm)}]
             \draw pic(clk) {Clock={T}} ;
@@
         %  Draw rectangle 
-        \draw[dashed, thick] (-5, -3) rectangle (5, 1.5);
-        \draw (0,0) node[yshift=-2.5cm, xshift=4cm]{Model};
+        \draw[dashed, thick] (-6, -4) rectangle (6, 2.5);
+        \draw (0,0) node[xshift=4.75cm, yshift=-3cm]{Model};
     \end{tikzpicture}

### 2020-05-04 v0.1.2/assets/SubsystemConnected/subsystemconnected.tex
build based on e8a0348

--- 2020-05-03 docs/src/assets/GeneratorWriter/generatorwriter.tex
@@
                 ]{
-                    \draw pic (gen) {Component={gen}}; \& \draw pic (writer) {Component={writer}}; \\
+                    \draw pic (gen) {Component={gen}}; \& \draw pic (sub) {Component={sub}}; \& \draw pic (writer) {Component={writer}}; \\
                 };
@@
             \def\shiftamount{0.5mm};
-            \draw[->] (gen-edge.east) -- (writer-edge.west);
+            \draw[->] (gen-edge.east) -- (sub-edge.west);
+            \draw[->] (sub-edge.east) -- (writer-edge.west);
         \end{scope}
@@
         % \Place clock 
-        \begin{scope}[shift={(-2cm, -1.5cm)}]
+        \begin{scope}[shift={(-2.5cm, -1.5cm)}]
             \draw pic(clk) {Clock={T}} ;
@@
         %  Draw rectangle 
-        \draw[dashed, thick] (-2.5, -2.25) rectangle (2.5, 1);
-        \draw (0,0) node[yshift=-2cm, xshift=1.75cm]{Model};
+        \draw[dashed, thick] (-3.35, -2.25) rectangle (3.25, 1);
+        \draw (0,0) node[yshift=-1.75cm, xshift=2.5cm]{Model};
     \end{tikzpicture}

### 2020-05-04 versions.js

@@ -1,2 +1,5 @@
 var DOC_VERSIONS = [
+  "stable",
+  "v0.1",
+  "v0.1.2",
 ];

### 2020-05-04 example/closed_loop_system.jl
Revised docs and README.md

@@ -2,28 +2,27 @@
 
 using Jusdl 
 
+# Construct the model 
 model = Model(clock=Clock(0, 0.01, 10.))
-addcomponent(model, FunctionGenerator(sin, name=:gen))
-addcomponent(model, Adder(Inport(2), (+,-), name=:adder))
-addcomponent(model, ODESystem((dx,x,u,t)->(dx[1]=-x[1]+u[1](t)), (x,u,t) -> x, [1.], 0., Inport(), Outport(), name=:ds))
-addcomponent(model, Memory(Inport(), 1, name=:mem))
-addcomponent(model, Writer(Inport(2), name=:writer))
-addconnection(model, :gen, :adder, 1, 1)
-addconnection(model, :adder, :ds)
-addconnection(model, :ds, :mem)
-addconnection(model, :mem, :adder, 1, 2)
-addconnection(model, :gen, :writer, 1, 1)
-addconnection(model, :ds, :writer, 1, 2)
+addnode(model, FunctionGenerator(sin), label=:gen)
+addnode(model, Adder((+,-)), label=:adder)
+addnode(model, ODESystem((dx,x,u,t)->(dx[1]=-x[1]+u[1](t)), (x,u,t) -> x, [1.], 0., Inport(), Outport()), label=:ds)
+addnode(model, Writer(Inport(2)), label=:writer)
+addbranch(model, :gen => :adder, 1 => 1)
+addbranch(model, :adder => :ds, 1 => 1)
+addbranch(model, :ds => :adder, 1 => 2)
+addbranch(model, :gen => :writer, 1 => 1)
+addbranch(model, :ds => :writer, 1 => 2)
 
 # Simualate the model 
 sim = simulate(model)
 
 # Read and plot data 
-t, x = read(getcomponent(model, :writer), flatten=true)
-using Plots 
-plot(t, x[:, 1], label="r(t)", xlabel="t")
-plot!(t, x[:, 2], label="y(t)", xlabel="t")
-plot!(t, 6 / 5 * exp.(-2t) + 1 / 5 * (2 * sin.(t) - cos.(t)), label="Analytical Solution")
+t, x = read(getnode(model, :writer).component)
+using Plots; pyplot()
+plot(t, x[:, 1], label="r(t)", xlabel="t", lw=3)
+plot!(t, x[:, 2], label="y(t)", xlabel="t", lw=3)
[…]

### 2020-05-04 dev/assets/ReadMeModel/brokenloop.tex
build based on c05b8d3

--- 2020-05-02 doctemp/assets/AlgebraicLoop/brokenloop.tex
@@
     border/.style = { 
-        draw, rectangle, minimum width=2cm, minimum height=1.5cm, thick
+        draw, rectangle, minimum width=1.5cm, minimum height=1cm, ultra thick
     },
@@
         % Place the blocks 
-        \draw(-3.5, 0) pic (gen) {Component={Sinewave\\Generator}{t}};
-        \draw pic (adder) {Component={Adder}{t}};
-        \draw(3.5, 0) pic (ds) {Component={ODESystem}{t}};
-        \draw(7, 1.5) pic (writer) {Component={Writer}{t}};
-        \draw(2, -2.25) pic (memory) {Component={Memory}{t}};
-        % Glow the blocks
-        \drawshadowbis{gen-edge};
-        \drawshadowbis{adder-edge};
-        \drawshadowbis{ds-edge};
-        \drawshadowbis{writer-edge};
-        \drawshadowbis{memory-edge};
+        \draw(-3.5, 0) pic (gen) {Component={gen}{t}};
+        \draw pic (adder) {Component={adder}{t}};
+        \draw(3.5, 0) pic (ds) {Component={ds}{t}};
+        \draw(7, 1.5) pic (writer) {Component={writer}{t}};
         \begin{scope}[line width=1.5mm, ->, >={Triangle[width=3mm,length=3mm]}]
@@
             \draw (a) |- ([yshift=-3mm] writer-edge.west);
-            \draw (a) |- (memory-edge.east);
-            \draw[-] (memory-edge.west) -- ++(-2.5cm, 0cm) coordinate (c);
-            \draw ([yshift=-0.75mm] c) |- ([yshift=-2mm] adder-edge.west);
+            \draw[-] (a) |- ++(-7cm, -2cm) coordinate (c);
+            \draw ([yshift=-0.75mm]c) |- ([yshift=-2mm] adder-edge.west);
+            \draw[-] ([yshift=2mm] gen-edge.east) -- ++ (1cm, 0cm) coordinate(d);
             \draw (d) |- ([yshift=3mm] writer-edge.west);
         \end{scope}
-        \draw[very thick, dashed] (-5, 3) rectangle (8.5, -4);
-        \node at (7.5, -3.5) {Model};
+        \draw[very thick, dashed] (-4.5, 2.5) rectangle (8, -4);
+        \node at (7, -3.25) {Model};
 
          % \Place clock 
-        \begin{scope}[shift={(-4.25cm, -3.25cm)}]
+        \begin{scope}[shift={(-4cm, -3cm)}]
             \draw pic(clk) {Clock={T}} ;

### 2020-05-13 v0.1.4/assets/TaskForComponents/components.tex
build based on 76fe946

--- 2020-01-11 docs/build/assets/AlgebraicLoop/brokenloop.tex
@@
     border/.style = { 
-        draw, rectangle, minimum width=2cm, minimum height=1.5cm, thick
+        draw, rectangle, minimum width=2cm, minimum height=1.5cm, ultra thick
     },
@@
 \begin{document}
-    \begin{tikzpicture}[every node/.style={font=\Large}]
+    \begin{tikzpicture}
         % Place the blocks 
-        \draw pic (b1) {Component={Static\\System}{t}};
-        \draw(3, 0) pic (b2) {Component={Dynamical\\System I}{t}};
-        \draw(3, -2.5) pic (b3) {Component={Dynamical\\System II}{t}};
-        \draw(0, -2.5) pic (b4) {Component={Memory}{t}};
-        % Glow the blocks
-        \drawshadowbis{b1-edge};
-        \drawshadowbis{b2-edge};
-        \drawshadowbis{b3-edge};
-        \drawshadowbis{b4-edge};
+        \draw pic (b1) {Component={B1}{t}};
+        \draw(3.5, 0) pic (b2) {Component={B2}{t}};
+        % % Glow the blocks
+        % \drawshadowbis{b1-edge};
+        % \drawshadowbis{b2-edge};
         \begin{scope}[line width=1.5mm, >={Triangle[width=3mm,length=3mm]}]
-            \draw[->] ([yshift=2mm, xshift=-1cm] b1-edge.west) -- ([yshift=2mm] b1-edge.west);
-            \draw[->] (b1-edge.east) -- (b2-edge.west);
-            \draw (b2-edge.east) -- ++(0.5cm, 0cm) coordinate (a);
-            \draw[->] (a) -- ++(0.5cm, 0cm);
-            \draw[->] (a) |- (b3-edge.east);
-            \draw[<-] ([yshift=-2mm] b1-edge.west) -- ++(-0.5cm, 0cm) coordinate (b);
-            \draw[-] ([yshift=0.75mm] b) |- (b4-edge.west);
-            \draw[->] (b3-edge.west) |- (b4-edge.east);
+            \draw[->] ([xshift=-1cm] b1-edge.west) -- node[midway, anchor=south]{L1} (b1-edge.west);
+            \draw[->] (b1-edge.east) -- node[midway, anchor=south]{L2} (b2-edge.west);
+            \draw[->] (b2-edge.east) -- node[midway, anchor=south]{L3} ([xshift=1cm] b2-edge.east);
         \end{scope}

### 2020-05-13 v0.1.4/assets/Tasks/reader_writer_task.tex
build based on 76fe946

--- 2020-04-29 docs/build/assets/TaskForComponents/tasks.tex
@@
     border/.style = { 
-        draw, circle, minimum width=2cm, ultra thick
+        draw, circle, minimum width=1cm, thick
     },
@@
 \begin{document}
-    \begin{tikzpicture}[every node/.style={font=\Large}]
-        \draw (0, 0) pic (t1) {Task={B1}};
-        \draw (2.5, 0) pic (t2) {Task={B1}};
-        \draw (6.5, 0) pic (t3) {Task={B2}};
-        \draw (9,0) pic (t4) {Task={B2}};
-        \begin{scope}[line width = \lw, >={Triangle[width=4mm,length=4mm]}, ->]
-            \draw ([xshift=-1.25cm] t1-edge.west) -- node[midway, anchor=south]{L1} (t1-edge.west);
-            \draw (t2-edge.east) -- node[midway, anchor=south]{L2}  (t3-edge.west);
-            \draw[line width = \lw, ->] (t4-edge.east) -- node[midway, anchor=south]{L3} ([xshift=1cm] t4-edge.east);
-        \end{scope}
+    \begin{tikzpicture}
+        \draw pic (t1) {Task={Writer\\Task}};
+        \draw (3,0) pic (t2) {Task={Reader\\Task}};
+        \draw[line width = \lw, >={Triangle[width=4mm,length=4mm]}, ->] (t1-edge.east) -- (t2-edge.west);
     \end{tikzpicture}

### 2020-05-13 versions.js

@@ -1,5 +1,6 @@
 var DOC_VERSIONS = [
   "stable",
   "v0.1",
+  "v0.1.4",
   "v0.1.2",
 ];

### 2020-06-18 v0.1.5/assets/FlowChart/flowchart.tex
build based on b33f934

--- 2020-05-13 v0.1.4/assets/Tasks/reader_writer_task.tex
@@
 
-\def\lw{2mm}        % Arrow line width
+\def\lw{1mm}        % Arrow line width
 \def\mw{2cm}        % Minimum width of component
-\def\mh{1.75cm}     % Minimum height of component
+\def\mh{1cm}     % Minimum height of component
 \def\trianglecoordinate{2mm}    % Starting coordinate clock input triangle of components
@@
     border/.style = { 
-        draw, circle, minimum width=1cm, thick
+        draw, rectangle, minimum width=0.75\mw, minimum height=\mh, very thick
     },
-    pics/Task/.style={
+    pics/Component/.style ={
         code = {
@@
 
+\tikzset{
+    decisionborder/.style = { 
+        draw, diamond,, minimum width=1*\mw, minimum height=\mh, very thick
+    },
+    pics/Decision/.style ={
+        code = {
+            \node [decisionborder, align=center](-decisionedge){#1};
+    }}
+    }
+
 \begin{document}
     \begin{tikzpicture}
-        \draw pic (t1) {Task={Writer\\Task}};
-        \draw (3,0) pic (t2) {Task={Reader\\Task}};
-        \draw[line width = \lw, >={Triangle[width=4mm,length=4mm]}, ->] (t1-edge.east) -- (t2-edge.west);
+        % Place the blocks 
+        \matrix (m) [matrix of nodes, ampersand replacement=\&, column sep = 0.75cm, row sep = 1cm, 
+            nodes={anchor=center}]{
+        \draw pic (b1) {Component={Start}}; \&
+        \draw pic (b2) {Decision={Inspect}}; \&
+        \draw pic (b3) {Component={Initialize}}; \&
+        \draw pic (b4) {Component={Run}}; \&
+        \draw pic (b5) {Component={Terminate}}; \\
+        };
+        \begin{scope}[very thick, >={Triangle[width=2mm,length=2mm]}]
+            \draw[->] (b1-edge.east) -- (b2-decisionedge.west);
+            \draw[->] (b2-decisionedge.east) -- node[midway, anchor=west, align=center, rotate=90]{Suitable\\For Simulation} (b3-edge.west);
+            \draw[->] (b3-edge.east) -- (b4-edge.west);
+            \draw[->] (b4-edge.east) -- (b5-edge.west);
+            \draw[-] (b2-decisionedge.south) -- node[midway, anchor=east, align=center]{Unsuitable\\For Simulation} ++(0cm, -1cm) coordinate(a);
+            \draw[->] (a) -| (b5-edge.south);
+        \end{scope}
     \end{tikzpicture}

### 2020-06-18 versions.js

@@ -1,6 +1,7 @@
 var DOC_VERSIONS = [
   "stable",
   "v0.1",
+  "v0.1.5",
   "v0.1.4",
   "v0.1.2",
 ];

### 2020-08-20 v0.2.0/assets/Components/components.tex
build based on d445921

--- 2020-01-11 docs/build/assets/Components/components.tex
@@
 
-\def\lw{1mm}        % Arrow line width
+\def\lw{2mm}        % Arrow line width
 \def\mw{2cm}        % Minimum width of component
@@
     border/.style = { 
-        draw, rectangle, minimum width=2.5cm, minimum height=2cm, thick
+        draw, rectangle, minimum width=2.5cm, minimum height=2cm, ultra thick
     },
@@
         \&
-        \draw pic (b8) {Component={DDESystem}{t}{$\dot{x}=f(x,x_\tau,u,t)$\\$y=f(x,u,t)$}}; 
+        \draw pic (b8) {Component={DDESystem}{t}{$\dot{x}=f(x,x_\tau,u,t)$\\$y=g(x,u,t)$}}; 
         \\
         };
-        % Glow the blocks
-        \foreach \x in {1, 2, ..., 9}{
-            \drawshadowbis{b\x-edge};
-        }
-        \begin{scope}[line width=\lw, >={Triangle[width=2mm,length=2mm]}]
+        % % Glow the blocks
+        % \foreach \x in {1, 2, ..., 9}{
+        %     \drawshadowbis{b\x-edge};
+        % }
+        \begin{scope}[line width=\lw, >={Triangle[width=4mm,length=4mm]}]
             \foreach \x in {1, 2, 4, 5, 6, 7, 8, 9}{
-                \draw[line width = \lw, ->] (b\x-edge.east) -- ++(0.5cm, 0cm) node[anchor=west]{$y$};
+                \draw[line width = \lw, ->] (b\x-edge.east) -- ++(1cm, 0cm) node[anchor=west]{$y$};
             }
             \foreach \x in {2, 3, 4, 5, 6, 7, 8, 9}{
-                \draw[line width = \lw, ->] ([xshift=-0.5cm] b\x-edge.west) node[anchor=east]{$u$} -- (b\x-edge.west);
+                \draw[line width = \lw, ->] ([xshift=-1cm] b\x-edge.west) node[anchor=east]{$u$} -- (b\x-edge.west);
             }

### 2020-08-20 versions.js

@@ -1,6 +1,8 @@
 var DOC_VERSIONS = [
   "stable",
+  "v0.2",
   "v0.1",
+  "v0.2.0",
   "v0.1.5",
   "v0.1.4",
   "v0.1.2",

### 2020-08-20 src/components/systems/dynamicalsystems/ddesystems.jl
Wrong doc Fixes #33

@@ -8,7 +8,7 @@ import UUIDs: uuid4
 
 where `ex` is the expression to define to define a new AbstractDDESystem component type. The usage is as follows:
 ```julia
-@def_dde_system struct MyDDESystem{T1,T2,T3,...,TN,OP,RH,RO,ST,IP,OP} <: AbstractDDESystem
+@def_dde_system mutable struct MyDDESystem{T1,T2,T3,...,TN,OP,RH,RO,ST,IP,OP} <: AbstractDDESystem
     param1::T1 = param1_default                 # optional field 
     param2::T2 = param2_default                 # optional field 
     param3::T3 = param3_default                 # optional field
@@ -16,9 +16,9 @@ where `ex` is the expression to define to define a new AbstractDDESystem compone
     paramN::TN = paramN_default                 # optional field 
     constlags::CL = constlags_default           # mandatory field
     depslags::DL = depslags_default             # mandatory field
-    righthandside::RH = righthandside_default   # mandatory field
-    history::HST = history_default              # mandatory field
-    readout::RO = readout_default               # mandatory field
+    righthandside::RH = righthandside_function  # mandatory field
+    history::HST = history_function             # mandatory field
+    readout::RO = readout_function              # mandatory field
     state::ST = state_default                   # mandatory field
     input::IP = input_defauult                  # mandatory field
     output::OP = output_default                 # mandatory field

### 2020-08-20 src/components/systems/dynamicalsystems/rodesystems.jl

@@ -9,14 +9,14 @@ import UUIDs: uuid4
 
 where `ex` is the expression to define to define a new AbstractRODESystem component type. The usage is as follows:
 ```julia
-@def_rode_system struct MyRODESystem{T1,T2,T3,...,TN,OP,RH,RO,ST,IP,OP} <: AbstractRODESystem
+@def_rode_system mutable struct MyRODESystem{T1,T2,T3,...,TN,OP,RH,RO,ST,IP,OP} <: AbstractRODESystem
     param1::T1 = param1_default                 # optional field 
     param2::T2 = param2_default                 # optional field 
     param3::T3 = param3_default                 # optional field
         ⋮
     paramN::TN = paramN_default                 # optional field 
-    righthandside::RH = righthandside_default   # mandatory field
-    readout::RO = readout_default               # mandatory field
+    righthandside::RH = righthandside_function  # mandatory field
+    readout::RO = readout_function              # mandatory field
     state::ST = state_default                   # mandatory field
     input::IP = input_default                   # mandatory field
     output::OP = output_default                 # mandatory field
@@ -44,7 +44,7 @@ Here, `MyRODESystem` has `N` parameters. `MyRODESystem` is represented by the `r
 
 # Example 
 ```jldoctest 
-julia> @def_rode_system struct MySystem{RH, RO, IP, OP} <: AbstractRODESystem
+julia> @def_rode_system mutable struct MySystem{RH, RO, IP, OP} <: AbstractRODESystem
            A::Matrix{Float64} = [2. 0.; 0 -2]
            righthandside::RH = (dx, x, u, t, W) -> (dx .= A * x * W)
            readout::RO = (x, u, t) -> x 

### 2020-08-20 docs/build/assets/SignalFlow/signalflow.tex

--- 2020-05-02 docs/build/assets/SimpleModel/simplemodel.tex
@@
 
-\def\mw{1.25cm}
-\def\mh{1cm}
+\def\mw{0.01cm}
+\def\mh{0.01cm}
 
@@
     border/.style = { 
-        draw, rectangle, minimum width=\mw, minimum height=\mh, thick, align=center, ultra thick
+        draw, circle, inner sep=0pt, align=center, thick
     },
     Component/.pic = {
-        \node [border](-edge){#1}; 
+        \node [border, label={[shift={(0.1pt,0.3pt)}]#1}](-edge){}; 
     },
@@
         % Draw connections 
-        \begin{scope}[line width=1.5mm, >={Triangle[width=4mm,length=3mm]}]
+        \begin{scope}[line width=0.25mm, >={Triangle[width=1.25mm,length=1.25mm]}]
             \def\shiftamount{0.5mm};
@@
             \draw[->] (gain-edge.east) -- (writer-edge.west);
-            \draw[-] (gain-edge.east) -| ++ (0.3cm, -1.5cm) coordinate (a);
-            \draw[->] ([yshift=0.75mm] a) -| (adder-edge.south);
+            \draw[->] (gain-edge.south) to [out=225,in=315] (adder-edge.south);
         \end{scope}
 
-        % \Place clock 
-        \begin{scope}[shift={(-4cm, -2cm)}]
-            \draw pic(clk) {Clock={T}} ;
-        \end{scope}
-
-        %  Draw rectangle 
-        \draw[dashed, thick] (-4.5, -3) rectangle (4.5, 1);
-        \draw (0,0) node[yshift=-2.5cm, xshift=3.5cm]{Model};
     \end{tikzpicture}

### 2020-08-21 v0.2.1/assets/NetworkModel/network.tex
build based on 41ea9c6

--- 2020-01-11 docs/build/assets/SubsystemModel/subsystem.tex
@@
 \begin{document}
-    \begin{tikzpicture}[every node/.style={font=\large}]
+    \begin{tikzpicture}[every node/.style={font=\Large}]
         % Place the blocks 
-        \matrix (m) [matrix of nodes, ampersand replacement=\&, column sep = 1.5cm, row sep = 0.25cm, nodes={anchor=center}]{
-             \& \draw pic (kaynak2) {Component={Source II}}; \& \&   \\[-1cm]
-            \draw pic (kaynak1) {Component={Source I}};    \& \& \draw pic (statiksistem1) {Component={StaticSystem I}}; \& \draw pic (statiksistem2) {Component={StaticSystem II}}; \\
-            \draw pic (kutuk1) {Component={Sink I}}; \& \& \& \draw pic (kutuk2) {Component={Sink II}}; \\
+        \matrix (m) [matrix of nodes, ampersand replacement=\&, column sep = 2cm, row sep = -0.75cm, nodes={anchor=center}]{
+            \draw pic (ds1) {Component={ODESystem $1$}}; \& \& \draw pic (ss1) {Component={StaticSystem $1$}}; \\
+            \draw node[]{\huge $\vdots$}; \& \draw pic (ss0) {Component={StaticSystem $0$}}; \& \draw[ultra thick] node[]{\huge $\vdots$}; \\
+            \draw pic (dsn) {Component={ODESystem $n$}}; \& \& \draw pic (ssn) {Component={Static\\System $n$}}; \\[1.5cm]
+             \& \draw pic (kutuk) {Component={Sink}}; \& \\
         };
         % Glow the blocks
-        \foreach \x in {kaynak1, kaynak2, kutuk1, kutuk2, statiksistem1, statiksistem2}{
+        \foreach \x in {ds1, dsn, ss0, ss1, ssn, kutuk}{
             \drawshadowbis{\x-edge};
@@
         \begin{scope}[line width=2mm, >={Triangle[width=4mm,length=4mm]}]
-            \draw[-] (kaynak1-edge.east) -- ++(0.75cm, 0cm) coordinate(a);
-            \draw[->] ([yshift=1mm] a) |- (kutuk1-edge.east);
-            \draw[->] (a) |- ([yshift=-0.25cm] statiksistem1-edge.west);
-            \draw[-] (kaynak2-edge.east) -- ++(0.5cm, 0cm) coordinate(b);
-            \draw[->] ([yshift=1mm] b) |- ([yshift=0.25cm] statiksistem1-edge.west);
-            \draw[->] (statiksistem1-edge.east) |- (statiksistem2-edge.west);
-            \draw[-] (statiksistem2-edge.east) -- ++(0.5cm, 0cm) coordinate(c);
-            \draw[->] ([yshift=1mm] c) |- (kutuk2-edge.east);
+            \draw[-] (ds1-edge.east) -- ++(1cm, 0cm) coordinate(a);
+            \draw[-] (dsn-edge.east) -- ++(1cm, 0cm) coordinate(b);
+            \draw[->] ([yshift=1mm] a) |- ([yshift=0.5cm] ss0-edge.west);
+            \draw[->] ([yshift=-1mm] b) |- ([yshift=-0.5cm] ss0-edge.west);
+            \draw (ss0-edge.west) node [xshift=-0.75cm]{\huge $\vdots$};
+            \draw (ss0-edge.east) node [xshift=0.75cm]{\huge $\vdots$};
+            \draw[-] ([yshift=0.5cm] ss0-edge.east) -- ++(0.5cm, 0cm) coordinate(c);
+            \draw[-] ([yshift=-0.5cm] ss0-edge.east) -- ++(0.5cm, 0cm) coordinate(d);
+            \draw[->] ([yshift=-1mm] c) |- (ss1-edge.west);
+            \draw[->] ([yshift=1mm] d) |- (ssn-edge.west);
+            \draw[-] (ds1-edge.east) -- ++(0.75cm, 0cm) coordinate(e);
+            \draw[-] (dsn-edge.east) -- ++(0.25cm, 0cm) coordinate(f);
+            \draw[->] (e) |- ([yshift=0.5cm] kutuk-edge.west);
+            \draw[->] (f) |- ([yshift=-0.5cm] kutuk-edge.west);
+            \draw (kutuk-edge.west) node [xshift=-0.75cm]{\huge $\vdots$};
+            \draw[->] ([xshift=-1cm] ds1-edge.west) node[anchor=east]{$u_1$} -- (ds1-edge.west);
+            \draw[->] ([xshift=-1cm] dsn-edge.west) node[anchor=east]{$u_n$} -- (dsn-edge.west);
+            \draw[->] (ss1-edge.east) -- ([xshift=1cm] ss1-edge.east) node[anchor=west]{$u_1$};
+            \draw[->] (ssn-edge.east) -- ([xshift=1cm] ssn-edge.east) node[anchor=west]{$u_n$};
         \end{scope}
 
-        % Draw rectangle for subsystem 
-        \draw[thick, dashed] ([xshift=-0.25cm, yshift=0.25cm] kaynak2-edge.north west) rectangle ([xshift=0.25cm, yshift=-0.75cm] statiksistem2-edge.south east);
-        \draw (statiksistem2-edge.north west) node[yshift=1.75cm, xshift=1cm]{SubSystem};
+        % Draw rectangle for network
+        \draw[thick, dashed] ([xshift=-1.75cm, yshift=0.25cm] ds1-edge.north west) rectangle ([xshift=1.75cm, yshift=-1.25cm] ssn-edge.south east);
+        \draw (ssn-edge.south) node[yshift=-1cm, xshift=1.7cm]{SubSystem};
 
         % \Place clock 
-        \begin{scope}[shift={(-5.75cm, -4.5cm)}]
+        \begin{scope}[shift={(-5.75cm, -5cm)}]
             \draw pic(clk) {Clock={T}} ;
@@
         %  Draw rectangle 
-        \draw[dashed, thick] ([xshift=-0.75*\mw, yshift=-0.25*\mh] clk-clockedge.south west) rectangle ([xshift=0.5*\mw, yshift=1.5*\mh] statiksistem2-edge.north east);
-        \draw (clk-clockedge.east) node[yshift=0*\mh, xshift=6*\mw]{Model};
+        \draw[dashed, thick] ([xshift=-0.5*\mw, yshift=-0.25*\mh] clk-clockedge.south west) rectangle ([xshift=1*\mw, yshift=0.5*\mh] ss1-edge.north east);
+        \draw (clk-clockedge.east) node[yshift=0*\mh, xshift=5.75*\mw]{Model};
     \end{tikzpicture}

### 2020-08-21 v0.2.1/assets/Subsystem/subsystem.tex
build based on 41ea9c6

--- 2020-05-02 docs/build/assets/SimpleModel/simplemodel.tex
@@
                 ]{
-                    \draw pic (gen) {Component={gen}}; \& \draw pic (adder) {Component={adder}}; \& \draw pic (gain) {Component={gain}}; \& \draw pic (writer) {Component={writer}}; \\
+                    \& \draw pic (adder) {Component={adder}}; \& \draw pic (gain) {Component={gain}}; \\
+                    \draw pic (gen) {Component={gen}}; \&  \&  \\
                 };
@@
             \def\shiftamount{0.5mm};
-            \draw[->] (gen-edge.east) -- (adder-edge.west);
+            \draw[->] (gen-edge.east) -| (adder-edge.south);
             \draw[->] (adder-edge.east) -- (gain-edge.west);
-            \draw[->] (gain-edge.east) -- (writer-edge.west);
-            \draw[->] (gain-edge.east) -- (writer-edge.west);
-            \draw[-] (gain-edge.east) -| ++ (0.3cm, -1.5cm) coordinate (a);
-            \draw[->] ([yshift=0.75mm] a) -| (adder-edge.south);
-        \end{scope}
-
-        % \Place clock 
-        \begin{scope}[shift={(-4cm, -2cm)}]
-            \draw pic(clk) {Clock={T}} ;
+            \draw[->] ([xshift=-3.5cm] adder-edge.west) -- (adder-edge.west);
+            \draw[->] (gain-edge.east) -- ++(2cm, 0cm);
         \end{scope}
@@
         %  Draw rectangle 
-        \draw[dashed, thick] (-4.5, -3) rectangle (4.5, 1);
-        \draw (0,0) node[yshift=-2.5cm, xshift=3.5cm]{Model};
+        \draw[dashed, thick] (-3.5, -2) rectangle (4, 1.5);
+        \draw (0,0) node[yshift=-1.5cm, xshift=3.5cm]{sub};
     \end{tikzpicture}

### 2020-08-21 versions.js

@@ -2,6 +2,7 @@ var DOC_VERSIONS = [
   "stable",
   "v0.2",
   "v0.1",
+  "v0.2.1",
   "v0.2.0",
   "v0.1.5",
   "v0.1.4",

### 2020-08-27 versions.js
build based on 15202f3

@@ -1,7 +1,9 @@
 var DOC_VERSIONS = [
   "stable",
+  "v0.3",
   "v0.2",
   "v0.1",
+  "v0.3.0",
   "v0.2.1",
   "v0.2.0",
   "v0.1.5",

### 2020-09-08 proceedings/tex/figures/ComponentsCompressed/components_compresses.tex
Added proceedings files [skip ci]

--- 2020-08-20 v0.2.0/assets/Components/components.tex
@@
-\documentclass[convert={density=900,size=1080x800,outext=.png}]{standalone}
+\documentclass[margin=5mm]{standalone}
 \usepackage{tikz}
@@
     border/.style = { 
-        draw, rectangle, minimum width=2.5cm, minimum height=2cm, ultra thick
+        draw, rectangle, minimum width=2.5cm, minimum height=2cm, line width=1.25mm
     },
@@
         code = {
-            \node [border, align=center](-edge){#1};
+            \node [border, align=center](-edge){\huge #1};
             \draw[thick] ([xshift=\trianglecoordinate] -edge.south) -- ([yshift=\trianglecoordinate] -edge.south);
             \draw[thick] ([xshift=-\trianglecoordinate] -edge.south) -- ([yshift=\trianglecoordinate] -edge.south);
-            \draw[thick] (-edge.south) |- ++(-3mm, -4mm) node[xshift=-2mm, yshift=-1mm] {#2}; 
-            \draw (-edge.south) node [yshift=-0.75*\mh, align=left, font=\large] {#3};
+            \draw[thick] (-edge.south) |- ++(-3mm, -4mm) node[xshift=-2mm, yshift=-1mm] {\huge #2}; 
+            \draw (-edge.south) node [yshift=-\mh, align=left, font=\huge] {#3};
     }}
@@
 \begin{document}
-    \begin{tikzpicture}[every node/.style={font={\large}}]
+    \begin{tikzpicture}[every node/.style={font={\Large}}]
         % Place the blocks 
-        \matrix (m) [matrix of nodes, ampersand replacement=\&, column sep = 2cm, row sep = 0.5cm, 
+        \matrix (m) [matrix of nodes, ampersand replacement=\&, column sep = 1cm, row sep = 0.5cm, 
             nodes={anchor=center}]{
-        \draw pic (b1) {Component={Source}{t}{$y=g(t)$}};    
+        \draw pic (b1) {Component={Source}{t}{$y=g(t)$\\}};    
         \& 
@@
             \foreach \x in {1, 2, 4, 5, 6, 7, 8, 9}{
-                \draw[line width = \lw, ->] (b\x-edge.east) -- ++(1cm, 0cm) node[anchor=west]{$y$};
+                \draw[line width = \lw, ->] (b\x-edge.east) -- ++(1cm, 0cm) node[anchor=west]{\huge $y$};
             }
             \foreach \x in {2, 3, 4, 5, 6, 7, 8, 9}{
-                \draw[line width = \lw, ->] ([xshift=-1cm] b\x-edge.west) node[anchor=east]{$u$} -- (b\x-edge.west);
+                \draw[line width = \lw, ->] ([xshift=-1cm] b\x-edge.west) node[anchor=east]{\huge $u$} -- (b\x-edge.west);
             }

### 2020-09-08 proceedings/tex/figures/CoupledChuaCircuit/coupled_chua.tex
Added proceedings files [skip ci]

\documentclass[]{standalone}  
\usepackage[utf8]{inputenc}
\usepackage[american]{circuitikz}
\usepackage{graphicx}

\renewcommand{\=}{=}

\begin{document}  
    \begin{tikzpicture}[scale=0.6, every node/.style={scale=0.6, font=\Large}]
        \begin{scope}
            \draw (0, 0) node[ground]{} coordinate (o1) to[resistor, l_=$N_R$, i_<=$i \= g(\upsilon)$] ++(0, 3) coordinate(b1);
            \draw (-0.25, 0.25) to[open,v^<=$\upsilon$] (-0.25, 2.75);
            \draw (b1) to[short] ++(3, 0) coordinate(c1);
            \draw (c1) to[resistor, l=$R_1$] ++(6, 0) coordinate(d1);
            \draw (d1) to[short] ++(3, 0) coordinate(e1);
            \draw (c1) to[capacitor, l=$C_1$, v=$\upsilon_{1,1}$, *-*] ++(0, -3);
            \draw (d1) to[capacitor, l=$C_2$, v=$\upsilon_{1,2}$, *-*] ++(0, -3);
            \draw (e1) to[cute inductor, l=$L$, i<=$i_{1,1}$] ++(0, -3) coordinate(f1);
            \draw (o1) -- (f1);
            \draw ([yshift=0.7cm, xshift=-0.25cm] o1) rectangle ([yshift=-0.7cm, xshift=0.25cm] b1);
            \fill ([yshift=0.7cm, xshift=-0.25cm] o1) rectangle ([yshift=-2cm, xshift=0.25cm] b1);
            \draw[dashed] ([yshift=-0.75cm, xshift=-1.25cm] o1) rectangle ([yshift=1cm, xshift=1cm] e1) coordinate (g1);
            \node at ([xshift=-2cm, yshift=-0.45cm] g1){Chua Circuit I};
        \end{scope}

        \begin{scope}[shift={(0cm, -5.5cm)}]
            \node at (3, 1.5)[op amp](op1){};
            \node at (9, 2)[op amp](op2){};
            \draw (op1.-) to[short] ++(0, 1) to[short] ++(2.5, 0) to[short, -*] ++(0, -1.5);
            \draw (op1.out) to[resistor, l=$R_2$] (op2.+);
            \draw (op2.-) to[short] ++(-0.5, 0) to[short] ++(0, 1) coordinate (a2);
            \draw (a2) to[resistor, l=$R_2$] ++(3,0) to[short, -*] ++(0,-1.5) coordinate(b2) to (op2.out);
            \draw (b2) to[short] ++(0, -2) to[resistor, l_=$R_2$] ++(-3, 0) coordinate(c2) to[short, -*]++(0, 1.5);
            \draw[dashed] (-1.25, -0.75) rectangle (13, 4.5) coordinate (g2);
            \node at ([xshift=-10.5cm, yshift=-0.4cm] g2){Voltage-to-Current Converter};
            \draw (a2) to[resistor, l_=$R_2$] ++(-2cm, 0cm) node[ground, rotate=-90]{};
        \end{scope}

        \begin{scope}[shift={(0cm, -11cm)}]
            \draw (0, 0) node[ground]{} coordinate (o3) to[resistor, l_=$N_R$, i_<=$i \= g(\upsilon)$, -*] ++(0, 3) coordinate(b3);
            \draw (-0.25, 0.25) to[open,v^<=$\upsilon$,] (-0.25, 2.75);
            \draw (b3) to[short] ++(3, 0) coordinate(c3);
            \draw (c3) to[resistor, l=$R_1$] ++(3, 0) to[voltage source, l=$\upsilon_\eta \= V_{rms} \xi_t$] ++(3,0) coordinate(d3);
            \draw (d3) to[short] ++(3, 0) coordinate(e3);
            \draw (c3) to[capacitor, l=$C_1$, v=$\upsilon_{2,1}$, *-*] ++(0, -3);
            \draw (d3) to[capacitor, l=$C_2$, v=$\upsilon_{2,2}$, *-*] ++(0, -3);
            \draw (e3) to[cute inductor, l=$L$, i<=$i_{2,1}$] ++(0, -3) coordinate(f3);
            \draw (o3) -- (f3);
            \draw ([yshift=0.7cm, xshift=-0.25cm] o3) rectangle ([yshift=-0.7cm, xshift=0.25cm] b3);
            \fill ([yshift=0.7cm, xshift=-0.25cm] o3) rectangle ([yshift=-2cm, xshift=0.25cm] b3);
            \draw[dashed] ([yshift=-0.75cm, xshift=-1.25cm] o3) rectangle ([yshift=1.5cm, xshift=1cm] e3) coordinate (g3);
            \node at ([xshift=-2cm, yshift=-0.4cm] g3){Chua Circuit II};
        \end{scope}
        \draw (c2) to[short, i=$i_o$] ++(-3, 0) -| (b3);
        \draw (b1) to[short, *-] ++(-1, 0) |- (op1.+);

        \draw ([xshift=-2cm] op1.+) to[open, *-*, v=$\upsilon_o$] ++(0, 1cm) node[ground, rotate=180]{};
    \end{tikzpicture}
\end{document}

### 2020-09-08 proceedings/tex/figures/FlowChart/flowchart.tex
Added proceedings files [skip ci]

--- 2020-06-18 v0.1.5/assets/FlowChart/flowchart.tex
@@
-\documentclass[convert={density=900,size=1080x800,outext=.png}]{standalone}
+\documentclass[convert={density=900,size=1080x800,outext=.png}, margin=5mm]{standalone}
 \usepackage[utf8]{inputenc}
@@
 \def\mw{2cm}        % Minimum width of component
-\def\mh{1cm}     % Minimum height of component
+\def\mh{0.75cm}     % Minimum height of component
 \def\trianglecoordinate{2mm}    % Starting coordinate clock input triangle of components
@@
     decisionborder/.style = { 
-        draw, diamond,, minimum width=1*\mw, minimum height=\mh, very thick
+        draw, diamond,, minimum width=\mw, minimum height=0.7*\mh, very thick
     },
@@
         \draw pic (b1) {Component={Start}}; \&
-        \draw pic (b2) {Decision={Inspect}}; \&
-        \draw pic (b3) {Component={Initialize}}; \&
+        \draw pic (b2) {Decision={Inspection}}; \&
+        \draw pic (b3) {Component={Initialization}}; \&
         \draw pic (b4) {Component={Run}}; \&
-        \draw pic (b5) {Component={Terminate}}; \\
+        \draw pic (b5) {Component={Termination}}; \\
         };
@@
             \draw[->] (b1-edge.east) -- (b2-decisionedge.west);
-            \draw[->] (b2-decisionedge.east) -- node[midway, anchor=west, align=center, rotate=90]{Suitable\\For Simulation} (b3-edge.west);
+            \draw[->] (b2-decisionedge.east) -- node[midway, anchor=west, align=center, rotate=90]{Suitable For\\Simulation} (b3-edge.west);
             \draw[->] (b3-edge.east) -- (b4-edge.west);
             \draw[->] (b4-edge.east) -- (b5-edge.west);
-            \draw[-] (b2-decisionedge.south) -- node[midway, anchor=east, align=center]{Unsuitable\\For Simulation} ++(0cm, -1cm) coordinate(a);
+            \draw[-] (b2-decisionedge.south) -- node[midway, anchor=east, align=center]{Unsuitable For\\Simulation} ++(0cm, -1cm) coordinate(a);
             \draw[->] (a) -| (b5-edge.south);

### 2020-09-08 proceedings/tex/figures/Model/model.tex
Added proceedings files [skip ci]

--- 2020-01-11 docs/src/assets/Model/model.tex
@@
 
-\def\mw{2cm}
-\def\mh{1.75cm}
+\def\mw{1.5cm}
+\def\mh{1cm}
 \def\trianglecoordinate{2mm}
@@
 \begin{document}
-    \begin{tikzpicture}[every node/.style={font=\large}]
+    \begin{tikzpicture}[every node/.style={font=\normalsize}]
         % Place the blocks 
-        \matrix (m) [matrix of nodes, ampersand replacement=\&, column sep = 1.5cm, row sep = -1cm]{
+        \matrix (m) [matrix of nodes, ampersand replacement=\&, column sep = 1.5cm, row sep = -0.75cm]{
                                             \& \draw pic (b1) {Component={B1}}; \&                                  \\
         \draw pic (b2) {Component={B2}};    \&                                  \& \draw pic (b3) {Component={B3}}; \\
-                                            \& \draw pic (b4) {Component={B4}}; \&                                  \\[1.25cm]
+                                            \& \draw pic (b4) {Component={B4}}; \&                                  \\[0.9cm]
                                             \& \draw pic (b5) {Component={B5}}; \&                                  \\
         };
-        % Glow the blocks
-        \foreach \x in {1, 2, 3, 4, 5}{
-            \drawshadowbis{b\x-edge};
-        }
+        % % Glow the blocks
+        % \foreach \x in {1, 2, 3, 4, 5}{
+        %     \drawshadowbis{b\x-edge};
+        % }
         % Draw connections 
-        \begin{scope}[line width=2mm, >={Triangle[width=4mm,length=4mm]}]
+        \begin{scope}[line width=1.5mm, >={Triangle[width=3mm,length=2mm]}]
             \def\shiftamount{0.5mm};
             \draw[-] (b2-edge.east) -- ++(0.5cm, 0cm) coordinate(a);
-            \draw[-] (a) -- node[midway, anchor=west]{L1} ++(0, 0.5*\mh) coordinate(b);
-            \draw[-] (a) -- node[midway, anchor=west]{L2} ++(0cm, -0.5*\mh) coordinate(c);
+            \draw[-] (a) -- node[midway, anchor=west, yshift=0.25cm]{L1} ++(0, 0.5*\mh) coordinate(b);
+            \draw[-] (a) -- node[midway, anchor=west, yshift=-0.1cm]{L2} ++(0cm, -0.5*\mh) coordinate(c);
             \draw[->] (b) |- (b1-edge.west);
@@
             \draw[-] (b4-edge.east) -- ++(0.4*\mw, 0cm) coordinate(e);
-            \draw[-] ([yshift=1mm] d) -- node[midway, anchor=east]{L3} ++(0cm, -0.7*\mh) coordinate(f);
-            \draw[-] ([yshift=-1mm] e) -- node[midway, anchor=east]{L4} ++(0cm, 0.7*\mh) coordinate(g);
+            \draw[-] ([yshift=0.75mm] d) -- node[midway, anchor=east, xshift=0.75cm]{L3} ++(0cm, -0.7*\mh) coordinate(f);
+            \draw[-] ([yshift=-0.75mm] e) -- node[midway, anchor=east, xshift=0.75cm]{L4} ++(0cm, 0.7*\mh) coordinate(g);
             \draw[->] ([yshift=\shiftamount] f) |- ([yshift=2mm] b3-edge.west);
@@
             \draw (b5-edge.west) -- ++(-1cm, 0cm) coordinate (h);
-            \draw[->] ([yshift=-1mm] h) |- node[midway, anchor=east, yshift=-1.25cm]{L6}  ([yshift=-0.25cm] b4-edge.west);
-            \draw[->] ([yshift=1mm] g) |- node[midway, anchor=east, yshift=1.25cm]{L5} (b5-edge.east);
+            \draw[->] ([yshift=-0.75mm] h) |- node[midway, anchor=east, yshift=-0.75cm]{L6}  ([yshift=-0.25cm] b4-edge.west);
+            \draw[->] ([yshift=0.75mm] g) |- node[midway, anchor=east, xshift=0.75cm, yshift=0.75cm]{L5} (b5-edge.east);
         \end{scope}
@@
         % \Place clock 
-        \begin{scope}[shift={(-4.25cm, -4cm)}]
+        \begin{scope}[shift={(-4.25cm, -2.25cm)}]
             \draw pic(clk) {Clock={T}} ;
@@
         %  Draw rectangle 
-        \draw[dashed, thick] ([xshift=-0.25*\mw, yshift=-0.25*\mh] clk-clockedge.south west) rectangle ([xshift=2*\mw, yshift=0.25*\mh] b1-edge.north east);
-        \draw (b3-edge.south) node[yshift=-2.75*\mh, xshift=0.4*\mw]{Model};
+        \draw[dashed, thick] ([xshift=-0.25*\mw, yshift=-0.25*\mh] clk-clockedge.south west) rectangle ([xshift=2.25*\mw, yshift=0.25*\mh] b1-edge.north east);
+        \draw (b3-edge.south) node[yshift=-2.75*\mh, xshift=0.3*\mw]{model};
     \end{tikzpicture}

### 2020-09-08 proceedings/tex/figures/TaskForComponents/components.tex
Added proceedings files [skip ci]

--- 2020-05-13 v0.1.4/assets/TaskForComponents/components.tex
@@
-\documentclass[convert={density=900,size=1080x800,outext=.png}]{standalone}
+\documentclass[]{standalone}
 \usepackage{tikz}
@@
     border/.style = { 
-        draw, rectangle, minimum width=2cm, minimum height=1.5cm, ultra thick
+        draw, rectangle, minimum width=1.25cm, minimum height=0.75cm, ultra thick
     },
@@
         \draw pic (b1) {Component={B1}{t}};
-        \draw(3.5, 0) pic (b2) {Component={B2}{t}};
+        \draw(2.5, 0) pic (b2) {Component={B2}{t}};
         % % Glow the blocks

### 2020-09-08 proceedings/tex/figures/TaskForComponents/tasks.tex
Added proceedings files [skip ci]

--- 2020-04-29 docs/build/assets/TaskForComponents/tasks.tex
@@
     border/.style = { 
-        draw, circle, minimum width=2cm, ultra thick
+        draw, circle, minimum width=1cm, ultra thick
     },
@@
 \begin{document}
-    \begin{tikzpicture}[every node/.style={font=\Large}]
+    \begin{tikzpicture}
         \draw (0, 0) pic (t1) {Task={B1}};
-        \draw (2.5, 0) pic (t2) {Task={B1}};
-        \draw (6.5, 0) pic (t3) {Task={B2}};
-        \draw (9,0) pic (t4) {Task={B2}};
-        \begin{scope}[line width = \lw, >={Triangle[width=4mm,length=4mm]}, ->]
+        \draw (1.5, 0) pic (t2) {Task={B1}};
+        \draw (4, 0) pic (t3) {Task={B2}};
+        \draw (5.5,0) pic (t4) {Task={B2}};
+        \begin{scope}[line width = 1.5mm, >={Triangle[width=3mm,length=3mm]}, ->]
             \draw ([xshift=-1.25cm] t1-edge.west) -- node[midway, anchor=south]{L1} (t1-edge.west);
             \draw (t2-edge.east) -- node[midway, anchor=south]{L2}  (t3-edge.west);
-            \draw[line width = \lw, ->] (t4-edge.east) -- node[midway, anchor=south]{L3} ([xshift=1cm] t4-edge.east);
+            \draw[->] (t4-edge.east) -- node[midway, anchor=south]{L3} ([xshift=1.25cm] t4-edge.east);
         \end{scope}

### 2020-09-08 proceedings/tex/sections/abstract.tex
Added proceedings files [skip ci]

\begin{abstract}
   This paper introduces a modeling and simulation framework, Causal.jl,  that enables fast and effective system simulations and online and offline data analyzes. Causal.jl adopts a causal modeling approach in which a model consists of components that process data and the connections that transfer the data flowing between these components. The framework developed makes it possible to simulate discrete time or continuous time, static or dynamical systems. In particular, it is possible to simulate dynamical systems modeled by various types of equations such as the ordinary, random ordinary, stochastic, delayed differential, differential-algebraic equations, and discrete-time difference equations. During the simulation, the data flowing through the connections can be processed online and offline, and specialized analyzes can be performed. These analyzes can also be enriched with plugins that can be easily defined using the standard Julia library or various Julia packages. The simulation is performed by evolving the model components between sampling time intervals individually and in parallel. The independent evolution of the components allows the simulation of the models consisting of the components represented by different mathematical equations, while the parallel evolution of components increases the simulation performance.
\end{abstract}

### 2020-09-08 proceedings/tex/sections/appendix.tex
Added proceedings files [skip ci]

\appendix

\begin{lstlisting}[caption={Program using Causal.jl for the simulation of the system in Figure \ref{fig: coupled model}. Plots.jl is used to plot the simulation data while FFTW.jl is used to compute the FFT of the simulation data \cite{plots, fftw}.}, label={lst: coupled codes}, language=Julia]
using Causal, Plots, FFTW

# Define ODE system type under AbstractODESystem
@def_ode_system mutable struct ODESys{RH, RO, IP, OP} <: AbstractODESystem
    righthandside::RH = function fode(dx, x, u, t, a=35., b=3., c=28.)
        dx[1] = a * (x[2] - x[1])
        dx[2] = (c - a) * x[1] + c * x[2] - x[1] * x[3]
        dx[3] = x[1] * x[2] - b * x[3]
    end
    readout::RO = (x, u, t) -> x 
    state::Vector{Float64} = rand(3)
    input::IP = nothing
    output::OP = Outport(3)
end

# Define SDE system type under AbstractSDESystem
@def_sde_system mutable struct SDESys{DR, DF, RO, IP, OP} <: AbstractSDESystem
    drift::DR = function fsde(dx, x, u, t, a=35., b=3., c=28.)
        dx[1] = a * (x[2] - x[1]) + u[1](t)
        dx[2] = (c - a) * x[1] + c * x[2] - x[1] * x[3] + u[2](t)
        dx[3] = x[1] * x[2] - b * x[3] + u[3](t)
    end
    diffusion::DF = (dx, x, u, t, η=10.) -> (dx .= η) 
    readout::RO = (x, u, t) -> x
    state::Vector{Float64} = rand(3)
    input::IP = Inport(3)
    output::OP = Outport(3)
end

# Define Gain system type under AbstractStaticSystem
@def_static_system struct GainSys{RO,IP,OP} <: AbstractStaticSystem 
    readout::RO = (u,t, ϵ=0.1) -> ϵ * u 
    input::IP = Inport(3)
    output::OP = Outport(3)
end

# Define plugin type under AbstractPlugin
@def_plugin struct FFTPlug{PR} <: AbstractPlugin 
    process::PR = x -> fft(x, 2)    # Computes FFT of the data `x`
end

# Construct model
@defmodel model begin 
    @nodes begin 
        odeds = ODESys()    # Add odeds component  
        gain = GainSys()    # Add gain  component   
        sdeds = SDESys()    # Add sde components
        writer1 = Writer(input=Inport(3))                   # Add writer without plugin
        writer2 = Writer(input=Inport(3))                   # Add writer without plugin
        writer3 = Writer(input=Inport(3), plugin=FFTPlug()) # Add writer with `FFTPlug` plugin
    end
    @branches begin 
        odeds => gain       # Add connection from `odeds` to `gain`.
        gain => sdeds       # Add connection from `gain` to `sdeds`.
        odeds => writer1    # Add connection from `odeds` to `writer1`.
        sdeds => writer2    # Add connection from `sdeds` to `writer2`.
        odeds => writer3    # Add connection from `odeds` to `writer3`.
    end 
end

# Simulate model 
sim = simulate!(model, 0, 0.001, 100) # Simulate from 0 to 100 seconds with a step size of 0.001 seconds

# Plot simulation data 
t, x1 = read(getnode(model, :writer1).component)
t, x2 = read(getnode(model, :writer2).component)
x3 = read(getnode(model, :writer3).component, flatten=false)
plot(x1[:, 1], x1[:, 2], subplot=1, label="")
plot(x2[:, 1], x2[:, 2], subplot=2, label="")   
println(x3)  
\end{lstlisting}

\begin{lstlisting}[caption={Program using Causal.jl for the simulation of the system in Figure \ref{fig: network graph}. Plots.jl is used to plot the simulation data while LightGraphs.jl is used to construct the connectiviy matrix of the network topology \cite{plots, lightgraphs}}, label={lst: network codes}, language=Julia]
using Causal, Plots
using LightGraphs: watts_strogatz, laplacian_matrix

# Define DynamicSystem type under AbstractODESystem
@def_ode_system mutable struct DynamicSystem{RH, RO, IP, OP} <: AbstractODESystem
    righthandside::RH = function f(dx, x, u, t, σ=10., β=8/3, ρ=28)
        dx[1] = σ * (x[2] - x[1]) + u[1](t)
        dx[2] = x[1] * (ρ - x[3]) - x[2] + u[2](t)
        dx[3] = x[1] * x[2] - β * x[3] + u[3](t)
    end
    readout::RO = (x, u, t) -> x
    state::Vector{Float64} = rand(3)
    input::IP = Inport(3)
    output::OP = Outport(3) 
end

# Define Coupler type under AbstractStaticSystem
@def_static_system struct CouplerSystem{ET, CT, IP, OP, RO} <: AbstractStaticSystem
    E::ET
    P::CT
    input::IP = Inport(size(E, 1) * size(P, 1))
    output::OP = Outport(size(E, 1) * size(P, 1))
    readout::RO =  (u, t, E=E, P=P) ->  kron(E, P) * u
end

# Construct network parameters 
n = 50      # Number of nodes 
d = 3       # Dimension of each node
ϵ = 20.     # Coupling strength 
components = [DynamicSystem() for i in 1 : n]
E = ϵ * collect(-laplacian_matrix(watts_strogatz(n, 10, 0.5)))  # Connectivity matrix of network topology
P = [1 0 0; 0 0 0; 0 0 0]   # Systems are coupled by their first state variable.

# Construct model 
model = Model()

# Add components
for (i, component) in enumerate(components)
    addnode!(model, component, label=Symbol("node$i"))
end
addnode!(model, CouplerSystem(E=E, P=P), label=Symbol("coupler"))
addnode!(model, Writer(input=Inport(n * d)), label=Symbol("writer"))

# Add connections
m = n + 1
for (j, k) in zip(1:n, map(i -> i : i + d - 1, 1 : d : n * d))
    addbranch!(model, j => m, 1 : d => k)
    addbranch!(model, m => j, k => 1 : d)
end
p = n + 2
for (j, k) in zip(1:n, map(i -> i : i + d - 1, 1 : d : n * d))
    addbranch!(model, j => p, 1 : d => k)
end

# Simulate model 
sim = simulate!(model, 0, 0.001, 100.)

# Read and plot the simulation data 
t, x = read(getnode(model, :writer).component)

# Compute mean square error
mse = sqrt.(sum(diff(x[:, 1 : d : end],dims=2).^2/n, dims=2))

# Plot results
k = 3000 
plot(t, x[:, 1] , label="")
plot(x[:, 1], x[:,2], label="")
plot(t[1:k], mse[1:k], label="")
\end{lstlisting}

### 2020-09-08 proceedings/tex/sections/conlusion.tex
Added proceedings files [skip ci]

\section{Conclusion}
In this paper, we introduced Causal.jl. In Causal.jl, the simulation is performed by evolving the components according to their mathematical equations between the sampling intervals in parallel and independently. The components can be static or dynamical or represented by mathematical equations having continuous or discrete-time variables. The simulation of the models consisting of components defined by ordinary, random ordinary, stochastic, delay differential, differential-algebraic, or difference equations is possible. It is not an obligation to describe all the model components with the same type of mathematical equation.

The data flowing through the connections can be directly recorded or visualized during the simulation. In addition to the offline analyzes, with user-defined plugins, it is also possible to carry out online data analysis such as extracting statistical or spectral properties, applying different signal processing techniques, etc.

The model components evolve in parallel and simultaneously. The tasks of the Julia programming language is used for this parallel evolution. The tasks allow switching between the evolution of the components during the simulation. Using the Julia programming language's distributed computing tools, it is possible to distribute computation workload on multiple processors.

Especially when considering extensive system networks consisting of thousands of system nodes, it is an important advantage that the system models can be created easily and quickly, that such models can be simulated in multiple microprocessor cores with distributed programming tools and that the proposed tool can provide this with an easy syntax.

### 2020-09-08 proceedings/tex/sections/illustrative_examples.tex
Added proceedings files [skip ci]

\section{Illustrative Examples}

\subsection{Simulation of Models Having Different Component Types}
\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{figures/CoupledChuaModel/coupled_chua_model.pdf}
    \caption{A model consisting of components represented by different equation types.}
    \label{fig: coupled model}
\end{figure}

In Causal.jl, it is possible to simulate models that include components represented by different types of equations. In Figure \ref{fig: coupled model} is given such an example model.`odeds` is a dynamical system represented by the ordinary differential equation in (\ref{eq: coupled ode}) where where $x_1, y_1, z_1$ are the state variables and $a=35, b=3, c = 28$ are system parameters.
\begin{equation}
    \begin{split}
        \dot{x}_1 &= a (y_1 - x_1) \\
        \dot{y}_1 &= (c - 1) x_1 + c y_1 - x_1 z_1 \\
        \dot{z}_1 &= x_1 y_1 - b z_1
    \end{split}
    \label{eq: coupled ode}
\end{equation}
`sdsds` is dynamical system that is represented by the stochastic differential equation in (\ref{eq: coupled sde}) where $x_2, y_2, z_2$ are the state variables, $u=[u_1,u_2, u_3]$ is the input, $\eta$ is noise strength, $W_t$ is the Wiener process corresponding to the noise and $a, b, c$ are the same as those in (\ref{eq: coupled ode}).
\begin{equation}
    \begin{split}
        dx_2 &= (a (y_1 - x_1) + u_1) dt + \eta dW_t \\
        dy_2 &= ((c - 1) x_1 + c y_1 - x_1 z_1)dt + \eta dW_t \\
        dz_2 &= (x_1 y_1 - b z_1 + u_3) dt + \eta dW_t 
    \end{split}
    \label{eq: coupled sde}
\end{equation}
`gain` is a static system whose input output relation is given in (\ref{eq: gain}) where $u, y, \epsilon$ are the input, output and gain coefficient of the system. 
\begin{equation}
    y = \epsilon u
    \label{eq: gain}
\end{equation}
`writer1` and `writer2` are used to record the outputs of `odeds` and `sdeds`, respectively, while `writer3` is used to record the fast Fourier transform(FFT) of the data flowing out of `odeds`\cite{proakis2004digital}.

Being a domain-specific-language, Causal.jl provides a syntax for handy model construction. The program written using Causal.jl to construct and simulate the model in Figure \ref{fig: coupled model} is given in Listing \ref{lst: coupled codes}. The program first starts with the type definitions of the components `odeds`, `sdeds`, and `gain`, together with their fields' default values. Note that the types of components are defined as subtypes of the corresponding abstract component types, which shows how the user-defined component types can enrich the standard library of Causal.jl. `writer1` and `writer2` are used directly to record the data without further processing, so they do not need additional data processing plugins.
On the other hand, rather than directly recording the data, `writer3` is used to process the data online, so it needs an additional plugin. `FFTPlug` is defined for this purpose, and `writer3` is equipped with an instance. For the sake of this example, we used the `fft` function \cite{fftw}. The model is constructed and simulated for $100$ seconds with a step size of $0.001$ seconds. After the simulation, the data in `write1` and `writer2` are read back and plotted in Figure \ref{fig: coupled simulation results}. From Figure \ref{subfig: coupled simulation sde}, the presence of the noise is apparent in the trajectory of `sdeds`.

The individual evolution of components makes it possible to simulate such models that include components represented by different equations.

Causal.jl adopts a causal modeling approach in which the data flow through the connections is unidirectional. Components that write data to a connection drives other components that read data from the same connection. Thus, the topological structure of a model can be extracted by following the components that read data from the connections bound to the output ports of model components.

The order in which the connections are specified is arbitrary. One does not need to follow the true data flow directions through the connections. Therefore, complex topologies with many components can be defined concisely.

\begin{figure}
    \centering
    \subfloat[]{
        \begin{tikzpicture}
            \node[](plt){\includegraphics[scale=0.25]{figures/ChenSystemSimulations/odeds.pdf}};
            \node[] at (plt.south) {$x_1$};
            \node[] at (plt.west) {$y_1$};
        \end{tikzpicture}
        \label{subfig: coupled simulation ode}
        }\\
    \subfloat[]{
        \begin{tikzpicture}
            \node[](plt){\includegraphics[scale=0.25]{figures/ChenSystemSimulations/sdeds.pdf}};
            \node[] at (plt.south) {$x_2$};
            \node[] at (plt.west) {$y_2$};
            \end{tikzpicture}
        \label{subfig: coupled simulation sde}
    }
    \caption{\protect\subref{subfig: coupled simulation ode} $x_1 - y_1$ trajectory of `odeds`. \protect\subref{subfig: coupled simulation sde} $x_2 - y_2$ trajectory of `sdeds`.}
    \label{fig: coupled simulation results}
\end{figure}

\subsection{Simulation of Models Consisting of a Large Number of Nodes}
In Causal.jl, its is possible to simulate large scale complex models consisting of a large number of dynamical system nodes. As an example, a network of continuous time identical dynamical systems is given Figure \ref{fig: network graph}. The nodes of the network evolve by 
\begin{equation}
    \dot{\bm{x}}_i = f(\bm{x}_i) + \bm{u}_i, \quad i = 1, \ldots, n
    \label{eq: network equation}
\end{equation}
where 
\begin{equation}
    \bm{u}_i = \sum_{i = 1}^n \epsilon_{ij} \bm{P} \bm{x}_j, \quad i = 1, \ldots, n,
    \label{eq: network node inputs}
\end{equation}
$n$ is the number of nodes, $\bm{x}_i \in \mathbb{R}^d$ is the state vector of node $i$, $f: \mathbb{R} \mapsto \mathbb{R}^d$ is the function corresponding to the individual node dynamics, $\epsilon_{ij} \geq 0 $ is the coupling strength between the nodes $i$ and $j$. The diagonal matrix $\bm{P} = diag(p_1, \ldots, p_d)$ determines by which state variables the nodes are connected to each other. The matrix $\bm{E} = [\epsilon_{ij}] \in \mathbb{R}^{n, n}, \; \epsilon_{ij} = \epsilon_{ji} \geq 0, \; \sum_{j = 1}^n \epsilon_{ij} = 0, i = 1, \ldots, n$ determines the network topology: if $\epsilon_{ij} > 0$, there is a connection between the nodes $i$ and $j$, if $\epsilon_{ij} = 0$, there is no connection between the nodes $i$ and $j$.

In the network given in Figure \ref{fig: network graph}, $n=50$,  $f$ is the Lorenz dynamics given by,
\begin{equation}
    \begin{split}
        \dot{x}_{i,1} &= \sigma (x_{i, 2} - x_{i, 1}) \\
        \dot{x}_{i,2} &= x_{i, 1} (\rho -  x_{i, 3}) - x_{i, 2} \\
        \dot{x}_{i,3} &= x_{i, 1} x_{i, 2} - \beta x_{i, 3}
    \end{split}
\end{equation}
where $\sigma=10, \beta=8/3, \rho=28$ are system parameters, $\bm{P} = diag(1, 0, 0)$. The network has Wattz-Strogatz topology that has a vertex degree of $10$ and that is randomized with a probability of $0.5$\cite{watts1998collective}.

\begin{figure}
    \centering
    \includegraphics[width=0.5\linewidth]{figures/Networks/wattz_strogatz.pdf}    
    \caption{A network consisting of identical dynamical system nodes The spheres and the line segments represent the dynamical system nodes and the connection between them, respectively. s}
    \label{fig: network graph}
\end{figure}

The model in Figure \ref{fig: network graph} is given in Figure \ref{fig: network model}. `node $k$` for $k =1, \ldots, n$ correspond to the dynamical system nodes of the network.  From (\ref{eq: network equation}) and (\ref{eq: network node inputs}), we see that the states of the nodes are taken as their outputs, weighted by the coupling strengths and fed back to their inputs. Hence, `coupler` is used to construct the weighted outputs. `writer` records the nodes' outputs. The model has algebraic loops $L_k$ for $k = 1, \ldots, n$, where the algebraic loop $L_k$ consists of `node $k$` and `coupler`.

\begin{figure}
    \centering
    \includegraphics[width=0.8\linewidth]{figures/NetworkModel-WattzStrogatz/network_wattz_strogratz.pdf}
    \caption{Block diagram model of the network in Figure \ref{fig: network graph}.}
    \label{fig: network model}
\end{figure}

The program written using Causal.jl to construct and simulate the model in Figure \ref{fig: network model} is given in Listing \ref{lst: network codes}. Having defined the types of dynamical system nodes and the coupler, the model is constructed and simulated for $100$ seconds with a sampling period of $0.005$ seconds. After the simulation, the simulation data is read back from the writer and the mean square error (MSE) 
\begin{equation}
    MSE(t) = \dfrac{1}{n} \sum_{i = 2}^n \Vert \bm{x}_{1,1}(t) - \bm{x}_{i,1}(t) \Vert
\end{equation}
is computed and plotted. It is seen from Figure \ref{subfig: network error} that the all the nodes in the network synchronize with each other as the MSE goes to zero as time evolves.

Note from the program in Listing \ref{lst: network codes} that memory components are not used to break algebraic loops of the model. Causal.jl is capable of detecting and breaking these algebraic loops automatically without requiring any user intervention.

% TODO: Include package limits 1. Distributed simulation, breaking nested loops, subsystem construction.

\begin{figure}
    \centering
    \subfloat[]{
        \begin{tikzpicture}
            \node[](plt){\includegraphics[scale=0.25]{figures/NetworkSimulation-WattzStrogatz/waveform.pdf}};
            \node[] at (plt.south) {$t$ [seconds]};
            \node[] at (plt.west) {$x_{1,1}$};
        \end{tikzpicture}
        \label{subfig: network timewaveform}
        }\\[-0.1cm]
    \subfloat[]{
        \begin{tikzpicture}
            \node[](plt){\includegraphics[scale=0.25]{figures/NetworkSimulation-WattzStrogatz/trajectory.pdf}};
            \node[] at (plt.south) {$x_{1,1}$};
            \node[] at (plt.west) {$x_{1, 2}$};
            \end{tikzpicture}
        \label{subfig: network trajectory}
    } \\[-0.1cm]
    \subfloat[]{
        \begin{tikzpicture}
            \node[](plt){\includegraphics[scale=0.25]{figures/NetworkSimulation-WattzStrogatz/error.pdf}};
            \node[] at (plt.south) {$t$ [seconds]};
            \node[xshift=-0.25cm] at (plt.west) {MSE};
            \end{tikzpicture}
        \label{subfig: network error}
    }
    \caption{Simulation results the model given in Figure \ref{fig: network model}. \protect\subref{subfig: network timewaveform} Time waveform of $x_{1,1}$. \protect\subref{subfig: network trajectory} $x_{1,1} - x_{1,2}$ trajectory. \protect\subref{subfig: network trajectory} MSE.}
    \label{fig: network simulation results}
\end{figure}

% \subsection{Breaking Algebraic Loops}
% Consider the model given in Figure \ref{fig: small network}. The model includes dynamical systems `ds1` and `ds2` whose dynamics evolve by
% \begin{equation}
%     \begin{split}
%         \dot{x}_{i,1} &= \sigma (x_{i,2} - x_{i,1}) + u_i \\
%         \dot{x}_{i,2} &= x_{i,1} (\rho - x_{i,3}) - x_{i,2} \\
%         \dot{x}_{i,3} &= x_{i,1} x_{i,2} - \beta x_{i,3}
%     \end{split}
%     \qquad i = 1, 2.
%     \label{eq: small network noncompact}
% \end{equation}
% where $\sigma=10, \beta=8/3, \rho=28$ are the system parameters, $u_1 = \epsilon(x_{2,1} - x_{1,1})$, $u_2 = \epsilon(x_{1,1} - x_{2,1})$ and $\epsilon > 0$. (\ref{eq: small network noncompact}) can be written more compactly as
% \begin{equation}
%     \dot{\bm{x}} = \bm{f}(\bm{x}) + \epsilon(\bm{E}\otimes \bm{P})
% \end{equation}
% where $\bm{x} = [\bar{\bm{x}}_1, \bar{\bm{x}}_2], \; \bar{\bm{x}}_i = [x_{i, 1}, x_{i, 2}, x_{i, 3}], \; i = 1, 2$,
% \begin{equation}
%     \bm{E} = \begin{bmatrix*}[r]
%         -1 & 1 \\
%         1 & -1
%     \end{bmatrix*} \quad \bm{P} = \begin{bmatrix*}[r]
%         1 & 0 & 0 \\
%         0 & 0 & 0 \\
%         0 & 0 & 0 
%     \end{bmatrix*}, 
% \end{equation}
% and $\otimes$ is the Kronecker product.

% \begin{figure}
%     \centering
%     \includegraphics[width=\linewidth]{figures/SmallNetwork/small_network.pdf}
%     \caption{A model consisting algebraic loops.}
%     \label{fig: small network}
% \end{figure}

% Note from the block diagram of the model in Figure \ref{fig: small network} that there are feedback loops from the outputs of the dynamical systems to their inputs. This means there are algebraic loops in the model. The model includes two algebraic loops: the first loop is between `odeds1` and `coupler` and the second one is between `ds2` and `coupler`. It is possible to break these loops by inserting memory components in the loops. However, Causal.jl is capable of detecting and breaking algebraic loops automatically without requiring any user intervention. The program written using Causal.jl to construct and simulate the model in Figure \ref{fig: small network} is given in Listing \ref{lst: small network codes}. Having defined the component types, the model is constructed and simulated. After the simulation the data recorded into the writer component is read back and plotted in Figure \ref{fig: small network simulation results}. From the time waveform in Figure \ref{subfig: small network error}, as time evolves the absolute error between the $x_{1,1}$ state variable of `ds1` and $x_{2,1}$ goes to zero as time evolves, which implies two dynamical systems synchronize to each other.

% \begin{figure}
%     \centering
%     \subfloat[]{
%         \begin{tikzpicture}
%             \node[](plt){\includegraphics[scale=0.25]{figures/SmallNetworkSimulation/timewaveform.pdf}};
%             \node[] at (plt.south) {$t$ [seconds]};
%             \node[] at (plt.west) {$x_{1,1}$};
%         \end{tikzpicture}
%         \label{subfig: small network ds1}
%         }\\
%     \subfloat[]{
%         \begin{tikzpicture}
%             \node[](plt){\includegraphics[scale=0.25]{figures/SmallNetworkSimulation/trajectory.pdf}};
%             \node[] at (plt.south) {$x_{1,1}$};
%             \node[] at (plt.west) {$x_{1,2}$};
%             \end{tikzpicture}
%         \label{subfig: small network ds2}
%     }\\
%     \subfloat[]{
%         \begin{tikzpicture}
%             \node[](plt){\includegraphics[scale=0.25]{figures/SmallNetworkSimulation/error.pdf}};
%             \node[] at (plt.south) {$t$ [seconds]};
%             \node[rotate=90] at (plt.west) {$|x_{1,1} - x_{2,1}|$};
%             \end{tikzpicture}
%         \label{subfig: small network error}
%     }
%     \caption{\protect\subref{subfig: small network ds1} Time waveform of $x_{1,1}$. \protect\subref{subfig: small network ds2} $x_{1,1} - x_{1,2}$ trajectory. \protect\subref{subfig: small network error}. The absolute error between $x_{1,1}$ and $x_{2,1}$}
%     \label{fig: small network simulation results}
% \end{figure}

### 2020-09-08 proceedings/tex/sections/introduction.tex
Added proceedings files [skip ci]

\section{Introduction}
Numerical simulations can be expressed as solving the mathematical equations derived from modeling physical systems. Based on the system's properties at hand and abstraction level in the modeling, mathematical equations may be ordinary, stochastic, delay differential, or difference equations. High-speed performance and the ability to offer useful analysis tools are other typical features expected from an effective simulation environment.

% TODO: Revise articles here. Try to update them.

Many simulation environments are available for numerical analysis of systems\cite{elmqvist1978structured,nytsch2006advanced,zimmer2008introducing,mosterman2002hybrsim,van2001variables,giorgidze2009higher,pfeiffer2012pysimulator,simulink}. They are capable of allowing simulations that are represented by ordinary differential equations and differential algebraic equations, mostly. This is restrictive given the variety of mathematical equations that can be derived from the modeling\cite{rackauckas2017differentialequations}. Besides, many of the existing simulation environments lack modern computational methods such as parallel computing.

In this study, Causal.jl, a modeling and simulation framework for causal models, is introduced \cite{causal}. The aim is to model large scale complex system networks easily and to provide fast and effective simulations. For this purpose, Julia, an open-source, high level, general purpose dynamical programming language designed for high-performance numerical analysis and computational science, has been used. Although Julia is a dynamical language, owing to its Just-in-Time(JIT) compiler developed on Low Level Virtual Machine(LLVM), it can reach the high-speed performance of static languages such as C\cite{bezanson2017julia,julialang}. It supports various parallel computing techniques at thread and process levels. In addition to Julia's standard library, numerous specialized packages developed for different fields such as data science, scientific computing, are also available. Julia's high-speed performance and parallel computing support are essential in meeting the need to design a  fast and effective simulation environment. Julia's syntax can be enlarged purposefully using its metaprogramming support. The analyzes scope of the simulation framework can be extended with new plugins that can be easily defined. It is possible to analyze discrete or continuous-time, static, or dynamical systems. In particular, it is possible to simulate dynamical systems modeled by ordinary, random ordinary, stochastic, delay differential, differential-algebraic, and/or discrete difference equations simultaneously. Unlike its counterparts, the models do not evolve at once for the whole simulation duration. Instead, the model components evolve between sampling time intervals individually. While individual evolution of the components enables the simulation of systems consisting of components represented by different mathematical models, parallel evolution of components increases the simulation performance.

### 2020-09-08 proceedings/tex/sections/modelling_and_simulation.tex
Added proceedings files [skip ci]

\section{Modeling and Simulation}

\subsection{Modeling}

Causal.jl adopts causal modeling\footnote{Causal modeling is also known as signal flow modeling or block diagram modeling} approach in modeling systems. In causal modeling approach, a model consists of components and connections (Figure \ref{fig: simple model})\cite{matei2012modeling}. The simulation of the model is performed in a clocked environment. That is, the model is not simulated in one shot by solving a single mathematical equation system that represents the whole model, but instead, it is simulated by evolving the components between sampling intervals in parallel, individually.

The components interact with each other through the connections that are bound to their input/output ports. The components are data processing agents, and their behavior determines how the data is processed. Depending upon the nature of the system and the modeling, these equations may differ, i.e., they may or may not contain derivative terms, or they may contain the continuous or discrete-time variable, etc. The dataflow through the connections is unidirectional, i.e., a component is driven by other components that write data to its input port.

The model simulation is performed by evolving the components individually. A reference clock is used to make the components have a common time base. The clock generates pulses at simulation sampling intervals. These pulses are used to trigger the components during the run stage of the simulation. Each triggered component reads its input data from its input port, calculates its output according to its mathematical model, and writes the result to its output port.

\begin{figure}
    \centering
    \includegraphics[width=0.75\linewidth]{figures/Model/model.pdf}
    \caption{A model consisting of the components B1, $\ldots$, B5 and the connections L1, $\ldots$, L6. T is the common time reference of the model.}
    \label{fig: simple model}
\end{figure}

\subsection{Components}
The component types in Causal.jl are shown in Figure \ref{fig: component types}. The components can be classified as sources, sinks, and systems.

The sources are the components that generate outputs as functions of time only. When triggered, a source computes its output according to its readout function and writes the result to its output port. The sources do not have input ports.

The sinks are data processing units. Their primary goal is to process the data flowing through the connections online. When triggered, a sink reads its input data from its input port and processes it. The data can be visualized by being plotted on a graphical user interface, can be observed by being printed on a console, or can be recorded in data files. The sinks' data processing scope can be enriched by integrating new plugins that can be developed using the standard Julia library or various available Julia packages. Invariants, spectral properties, or statistical information can be extracted from the data. Parameter estimation can be performed, or various signal processing techniques can be applied. Causal.jl has been designed to be flexible enough to allow the users to extend its data analyzes scope by integrating newly-defined plugins.

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{figures/ComponentsCompressed/components_compresses.pdf}
    \caption{Component types in Causal.jl. $u, x, y$ signify the input, state, output of a system, respectively. $t$ and $k$ are continuous and discrete time variable, respectively. $W$ is the stochastic process corresponding to the noise and $x_\tau$ is the state $x$ delayed by $\tau$ seconds in time. $f$(and $h$) is the right-hand-side function of the differential equation representing the system and $g$ is the readout function.}
    \label{fig: component types}
\end{figure}

A static system is described by a readout equation solely. When triggered, a static system reads its input data from its input port, calculates its output according to its readout function, and writes the result to its output port. In dynamic systems, however, the system behavior is characterized by the states. The output of a dynamical system depends on its input, previous state(s), and time. Therefore, a dynamical system is described by a differential equation and a readout equation, classically. When triggered, a dynamical system reads its input from its input port, updates its state according to the differential equation, calculates its output according to its readout function, and writes the result to its output port. Being developed on top of DifferentialEquations.jl, Causal.jl is capable of simulating the dynamical systems represented by differential equations in the form of the ordinary differential equations(ODE), differential-algebraic equations(DAE), random ordinary differential equations(RODE), stochastic differential equations(SDE), delay differential equations(DDE) or discrete difference equations \cite{rackauckas2017differentialequations}. Most of the available simulation environments allow the systems represented by ordinary differential equations or differential-algebraic equations\cite{elmqvist1978structured,nytsch2006advanced,zimmer2008introducing,mosterman2002hybrsim,van2001variables,giorgidze2009higher,pfeiffer2012pysimulator,simulink}. Therefore, analyzes such as noise or delay analysis or unexpected change of system parameters cannot be performed in these simulation environments, easily. On the contrary, Causal.jl makes it possible for all these analyses to be performed owing to its ability to solve such a wide range of differential equations.

\subsection{Ports and Connections}
A port is a bunch of pins to which the connections are bound. There are two types of pins: an output pin that transfers data from the inside of the component to its outside, and an input pin that transfers data from the outside of the component to its inside. There are two types of ports: an output port that consists of output pins and an input port that consists of input pins.

\begin{figure}
    \centering
    \subfloat[]{\includegraphics[width=0.225\linewidth]{figures/Tasks/reader_task.pdf} \label{subfig: reader task}} \hfil 
    \subfloat[]{\includegraphics[width=0.225\linewidth]{figures/Tasks/writer_task.pdf} \label{subfig: writer task}} \hfil 
    \subfloat[]{\includegraphics[width=0.4\linewidth]{figures/Tasks/reader_writer_task.pdf} \label{subfig: reader writer task}} 
    \caption{\protect\subref{subfig: reader task} A readable connection, \protect\subref{subfig: writer task} A writable connection, \protect\subref{subfig: reader writer task} A readable and writable connection}
    \label{fig: tasks}
\end{figure}

The data transferred to a port are transferred to its connections. The data transfer through the connections is performed over the links of the connections. The links are built on top Julia channels. The data written to(read from) a link is written to(read from) its channel. Running Julia tasks bound to the channels must exist for the data to flow through these channels. Julia tasks are the control flow features that allow calculations to be flexibly suspended and maintained without directly communicating the task scheduler of the operating system\cite{julialang}. The communication and the data exchange between the tasks are carried out through Julia's channels to which they are bound.

Figure \ref{fig: tasks} depicts the tasks that must be bound to a connection to make it readable, writable, and both readable and writable, symbolically. The writer(the reader) task is the task that writes(reads) data to(from) the connection. A running writer task must be bound to the connection on the opposite side to read data from one side of a connection. This connection is called a readable connection. Similarly, to write data to one side of a connection, a running reader task must be bound to the connection at the other side. This connection is called a writable connection. If both running writer and reader tasks are bound to both sides of a connection, then the data can both be read from and written to the connection. Such a connection is called a readable and writable connection. The dataflow through a connection is only allowed if the connection is both readable and writable connection. The data read from a readable connection is the data written to the connection by the writer task of the connection. If the data have not been written to the connection by its writer task during a reading process yet, then reading does not occur, and the writer task is waited to put data to the connection. Similarly, if the data on a connection has not been read from the connection by its reader task during a writing process yet, then the reader task is waited to take data from the connection.

In the modeling approach adopted, the components reading data from a connection are driven by other components writing data to the connection. Therefore, all of the model's connections must be readable and writable so that data can flow through the connections. This necessitates that all the connections of the model must be connected to a component from both ends. Otherwise, the simulation gets stuck and does not terminate.

\subsection{Simulation}
A model to be simulated consists of components connected to each other and a time reference. The time reference is used to sample the continuous-time signals flowing through the model's connections and trigger the components. The simulation is performed by triggering the components with pulses generated by the time reference of the model at sampling time instants. When triggered, the components evolve to compute their outputs.

The simulation stages are shown in Figure \ref{fig: flowchart} basically. Performing, inspecting, and reporting all the simulation stages is carried out automatically without requiring any user intervention.

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{figures/FlowChart/flowchart.pdf}
    \caption{Flowchart of the simulation stages.}
    \label{fig: flowchart}
\end{figure}

\begin{figure}
    \centering
    \subfloat[]{\includegraphics[width=0.49\linewidth]{figures/AlgebraicLoop/unbrokenloop.pdf} \label{subfig: unbroken algebraic loop}}
    \subfloat[]{\includegraphics[width=0.49\linewidth]{figures/AlgebraicLoop/brokenloop.pdf} \label{subfig: broken algebraic loop}}
    \caption{\protect\subref{subfig: unbroken algebraic loop} An algebraic loop consisting of the components Static System, Dynamical System I and Dynamical System II. \protect\subref{subfig: broken algebraic loop} Breaking of the loop with a Memory component. }
    \label{fig: algebraic loop}
\end{figure}

In the \textit{inspection} stage, the model is inspected to see whether the model is suitable for simulation. If connections having any unconnected terminals are detected, the simulation is terminated at this stage. The model is not suitable for simulation when algebraic loops exist\cite{lamego2001adaptive}. An algebraic loop is a closed-loop consisting of one or more components whose outputs are directly dependent on their inputs. Almost every system that includes feedbacks has algebraic loops. The simulation does not proceed because none of the components in the loop can generate output to break the loop. Such a problem can be solved by redesigning the model so that the model has no algebraic loops, solving the feed-forward algebraic equation of the loop, or inserting a memory component with a particular initial condition anywhere in the loop. Causal.jl provides all these loop-breaking solutions. During the \textit{inspection}, when algebraic loops are detected, all the loops are broken, if possible, automatically. Otherwise, a report is printed to notify the user to insert memory components to break the loops.

\begin{figure}
    \centering
    \subfloat[]{\includegraphics[width=0.5\linewidth]{figures/TaskForComponents/components.pdf} \label{subfig: components}} \\
    \subfloat[]{\includegraphics[width=.75\linewidth]{figures/TaskForComponents/tasks.pdf} \label{subfig: tasks}}
    \caption{Launching tasks for the connections. \protect\subref{subfig: components} An example model part consisting of the components B1 and B2 and the connections L1, L2 and L3. \protect\subref{subfig: tasks} Tasks launched corresponding to the connections.}
    \label{fig: tasks for components}
\end{figure}

If the model passes the \textit{inspection}, the writer and reader tasks are launched in the \textit{initialization} stage to ensure the data flow through the model connections. At this point, a writer and a reader task are bound to each connection. In Figure \ref{subfig: components} model part consisting of components B1, B2, and the connections L1, L2, L3 are shown. When triggered, the B1 reads data from L1, calculates its output, and writes to L2. Similarly, when triggered, B2 reads data from the L2, calculates its output, and writes to the L3. The tasks bounded to L1, L2, and L3 corresponding to B1 and B2 are shown in Figure \ref{subfig: tasks}. Since B1 reads the data from L1 and writes data to L2, a reader task is bounded to L1, and a writer task is bounded L2. Similarly, since B2 reads the data from L2 and writes data to L3, a reader task is bounded to L2, and a writer task is bounded L3. Since both a writer and a reader task are bound to the L2, data can flow from B1 to B2 through L2. A task manager is constructed to check whether the tasks launched during the \textit{initialization} are running correctly throughout the simulation.

The \textit{initialization} is followed by the \textit{run} stage. The tasks that are launched corresponding to the components during the \textit{initialization} expect the components to be triggered through their trigger pins. These triggers are generated in the sampling instants by the model clock during the \textit{run} stage. It is possible to sample the signals flowing through the connections at equal or independent time intervals. The generated triggers are put into the trigger pins of the components.

When the \textit{run} stage is completed, the tasks launched at the \textit{initialization} stage are closed in the \textit{termination} stage and the simulation ends.

The sampled values are interpolated for a duration of one sampling period so that the components can evolve independently. The sampling period is an essential factor that affects the accuracy of the simulation results directly.

### 2020-09-08 proceedings/tex/main.tex
Renamed file name [skip ci]

\documentclass{juliacon}
\setcounter{page}{1}
\usepackage{subfig}
\usepackage{amsmath}
\usepackage{tikz}
\usepackage{mathtools}
\usepackage{cite}

\title{Causal.jl:\\A Modeling and Simulation Framework for Causal Models}

\author[1]{Zekeriya Sarı}
\author[1]{Serkan Günel}
\affil[1]{Department of Electrical and Electronics Engineering, Dokuz Eylül University, İzmir, Turkey}

\keywords{System Modeling, Causal Modeling, System Simulation, Dynamical Systems, Julia Programming Language}

\hypersetup{
pdftitle = {Causal.jl: A Modeling and Simulation Framework for Causal Models},
pdfsubject = {JuliaCon 2020 Proceedings},
pdfauthor = {1st author, 2nd author, 3rd author},
pdfkeywords = {System Simulation, System Modeling, Dynamical Systems, Julia Programming Language},
}

\hypersetup{
  colorlinks   = true,  % Colours links instead of ugly boxes
  urlcolor     = black,  % Colour for external hyperlinks
  linkcolor    = black,   % Colour of internal links
  citecolor   = black     % Colour of citations
}

\begin{document}
    \maketitle
    \input{sections/abstract.tex}
    \input{sections/introduction.tex}
    \input{sections/modelling_and_simulation.tex}
    \input{sections/illustrative_examples.tex}
    \input{sections/conlusion.tex}
    \input{sections/acknowledgements.tex}
    \bibliographystyle{juliacon}
    % \nocite{*}
    \bibliography{Refs}
    \onecolumn
    \input{sections/appendix.tex}
\end{document}

### 2020-09-08 proceedings/tex/prep.rb

@@ -3,7 +3,7 @@
 
 require 'yaml'
 
-metadata = YAML.load_file('paper.yml')
+metadata = YAML.load_file('main.yml')
 
 for k in ["title", "authors", "affiliations", "keywords", "bibliography"]
 	raise "Key #{k} not present in metadata" unless metadata.keys().include?(k)

### 2020-10-21 proceedings/tex/prep.rb
Deleted proceedings folder.

@@ -1,57 +1,0 @@
-# metadata generator for JuliaCon
-# DO NOT EDIT
-
-require 'yaml'
-
-metadata = YAML.load_file('main.yml')
-
-for k in ["title", "authors", "affiliations", "keywords", "bibliography"]
-	raise "Key #{k} not present in metadata" unless metadata.keys().include?(k)
-end
-
-# ENV variables or default for issue/volume/year
-issue = ENV["JLCON_ISSUE"] === nil ? 1 : ENV["JLCON_ISSUE"]
-volume = ENV["JLCON_VOLUME"] === nil ? 1 : ENV["JLCON_VOLUME"]
-year = ENV["JLCON_YEAR"] === nil ? 2019 : ENV["JLCON_YEAR"]
-journal_name = "Proceedings of JuliaCon" # hard-coded for now
-
-open('header.tex', 'w') do |f|
-  f << "% **************GENERATED FILE, DO NOT EDIT**************\n\n"
-  f << "\\title{#{metadata["title"]}}\n\n"
-  for auth in metadata["authors"]
-    f << "\\author[#{auth["affiliation"]}]{#{auth["name"]}}\n"
-  end
-  for aff in metadata["affiliations"]
-    f << "\\affil[#{aff["index"]}]{#{aff["name"]}}\n"
-  end
-  f << "\n\\keywords{"
-  for i in 0...metadata["keywords"].length-1
-    f << "#{metadata["keywords"][i]}, "
-  end
-  f << metadata["keywords"].last
-  f << "}\n\n"
-
-	# hypersetup
-	f << "\\hypersetup{\n"
-	f << "pdftitle = {#{metadata["title"]}},\n"
-	f << "pdfsubject = {JuliaCon 2019 Proceedings},\n"
-	author_list = metadata['authors'].map { |a| a['name'] }.join(', ')
-	f << "pdfauthor = {#{author_list}},\n"
-	keyword_list = metadata['keywords'].join(', ')
-	f << "pdfkeywords = {#{keyword_list}},\n"
-	f << "}\n\n"
-end
-
-open('journal_dat.tex', 'w') do |f|
-  f << "% **************GENERATED FILE, DO NOT EDIT**************\n\n"
-  f << "\\def\\@journalName{#{journal_name}}\n"
-  f << "\\def\\@volume{#{volume}}\n"
-  f << "\\def\\@issue{#{issue}}\n"
-  f << "\\def\\@year{#{year}}\n"
[…]

### 2020-10-21 paper/figures/Components/components.tex
Added revised paper folder.

\documentclass[margin=5mm]{standalone}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{tikz}
% \usepackage{mathpazo}
\usepackage[scaled=0.92]{helvet}

\usetikzlibrary{positioning, calc}
\usetikzlibrary{shadows.blur}
\usetikzlibrary{shapes, positioning, calc, decorations.markings, arrows.meta}

\tikzstyle{arrow}=[line width=1mm,draw=black, -{Triangle[length=3mm]}, postaction={draw, line width=2mm, shorten >=1mm, -}]
\tikzstyle{line}=[line width=2mm,draw=black]
\tikzstyle{component}=[rectangle, draw, fill=white, ultra thick, minimum height=1.5cm, minimum width = 2cm, align=center]
% \tikzstyle{component}=[rectangle, draw, fill=white, thick, minimum height=1.5cm, minimum width = 2cm, blur shadow={shadow blur steps=5}, align=center]

\begin{document}
    \begin{tikzpicture}[node distance = 2.5cm, very thick]
        % Draw the blocks
        \node[component](source){Source};
        % \node[xshift=-1cm] (in source) at (source.west) {$u$};
        \node[xshift=1cm] (out source) at (source.east) {$y$};
        % \draw[arrow] (in source) -- (source.west);
        \draw[arrow] (source.east) -- (out source);
        \node[below = 0.75cm of source]{\large
            $\begin{aligned}
                y &= g(t)
             \end{aligned}$
        };

        \node[component, below = of source](sink){Sink};
        \node[xshift=-1cm] (in sink) at (sink.west) {$u$};
        % \node[xshift=1cm] (out sink) at (sink.east) {$y$};
        \draw[arrow] (in sink) -- (sink.west);
        % \draw[arrow] (sink.east) -- (out sink);
        % \node[below = 0.1cm of sink]{
        %     $\begin{aligned}
        %         y &= g(t) \\
        %         y &= g(t)
        %      \end{aligned}$
        % };

        \node[component, below = of sink](static system){Static \\ System};
        \node[xshift=-1cm] (in static system) at (static system.west) {$u$};
        \node[xshift=1cm] (out static system) at (static system.east) {$y$};
        \draw[arrow] (in static system) -- (static system.west);
        \draw[arrow] (static system.east) -- (out static system);
        \node[below = 0.75cm of static system]{\large
            $\begin{aligned}
                y &= g(u, t)
             \end{aligned}$
        };

        \node[component, below = of static system](ode system){ODE \\ Dinamik \\ System};
        \node[xshift=-1cm] (in ode system) at (ode system.west) {$u$};
        \node[xshift=1cm] (out ode system) at (ode system.east) {$y$};
        \draw[arrow] (in ode system) -- (ode system.west);
        \draw[arrow] (ode system.east) -- (out ode system);
        \node[below = 0.75cm of ode system]{ \large
            $\begin{aligned}
                \dot{x} &= f(x, u, t) \\
                y &= g(x, u, t)
             \end{aligned}$
        };

        \node[component, right = of source, xshift=2cm](dae system){DAE \\ Dynamic \\ System};
        \node[xshift=-1cm] (in dae system) at (dae system.west) {$u$};
        \node[xshift=1cm] (out dae system) at (dae system.east) {$y$};
        \draw[arrow] (in dae system) -- (dae system.west);
        \draw[arrow] (dae system.east) -- (out dae system);
        \node[below = 0.75cm of dae system]{\large
            $\begin{aligned}
                0 &= f(dx, x, u, t) \\
                y &= g(x, u, t)
             \end{aligned}$
        };

        \node[component, below = of dae system](rode system){RODE \\ Dynamic \\ System};
        \node[xshift=-1cm] (in rode system) at (rode system.west) {$u$};
        \node[xshift=1cm] (out rode system) at (rode system.east) {$y$};
        \draw[arrow] (in rode system) -- (rode system.west);
        \draw[arrow] (rode system.east) -- (out rode system);
        \node[below = 0.75cm of rode system]{ \large
            $\begin{aligned}
                dx &= f(x, u, t, W)dt \\
                y &= g(x, u, t)
             \end{aligned}$
        };

        \node[component, below = of rode system](sde system){SDE \\ Dynamic \\ System};
        \node[xshift=-1cm] (in sde system) at (sde system.west) {$u$};
        \node[xshift=1cm] (out sde system) at (sde system.east) {$y$};
        \draw[arrow] (in sde system) -- (sde system.west);
        \draw[arrow] (sde system.east) -- (out sde system);
        \node[below = 0.75cm of sde system]{\large
            $\begin{aligned}
                dx &= f(x, u, t)dt + g(x, u, t)dW \\
                y &= g(x, u, t)
             \end{aligned}$
        };

        \node[component, below = of sde system](dde system){DDE \\ Dynamic \\ System};
        \node[xshift=-1cm] (in dde system) at (dde system.west) {$u$};
        \node[xshift=1cm] (out dde system) at (dde system.east) {$y$};
        \draw[arrow] (in dde system) -- (dde system.west);
        \draw[arrow] (dde system.east) -- (out dde system);
        \node[below = 0.75cm of dde system]{\large
            $\begin{aligned}
                \dot{x} &= f(x, x_\tau, u, t)\\
                y &= g(x, u, t)
             \end{aligned}$
        };

        \node[component, below = of dde system](discrete system){Discrete \\ Dynamic \\ System};
        \node[xshift=-1cm] (in discrete system) at (discrete system.west) {$u$};
        \node[xshift=1cm] (out discrete system) at (discrete system.east) {$y$};
        \draw[arrow] (in discrete system) -- (discrete system.west);
        \draw[arrow] (discrete system.east) -- (out discrete system);
        \node[below = 0.75cm of discrete system]{\large
            $\begin{aligned}
                x_{k + 1} &= f(x_k, u_k, k)\\
                y_k &= g(x_k, u_k, k)
             \end{aligned}$
        };

        \def\points{source, sink, static system, ode system, dae system, rode system, sde system, dde system}
        \foreach \p in \points {
            \draw (\p.south) |- ++(-0.5, -0.5) node[anchor=east]{t};
        }
        \draw (discrete system.south) |- ++(-0.5, -0.5) node[anchor=east]{k};

    \end{tikzpicture}
\end{document}

### 2020-10-21 paper/figures/CoupledChuaModel/coupled_chua_model.tex
Added revised paper folder.

--- 2020-01-11 docs/src/assets/Model/model.tex
@@
-\documentclass[convert={density=900,size=1080x800,outext=.png}]{standalone}
+\documentclass[margin=5mm]{standalone}
+\usepackage[utf8]{inputenc}
 \usepackage{tikz}
@@
 
-\def\mw{2cm}
-\def\mh{1.75cm}
+\def\mw{1.5cm}
+\def\mh{1cm}
 \def\trianglecoordinate{2mm}
-
-\newcommand\drawshadowbis[1]{
-    \begin{pgfonlayer}{shadow}
-        \fill[inner color=black,outer color=white] ($(#1.south west)$) circle (\shadowradius);
-        \fill[inner color=black ,outer color=white] ($(#1.north west)$) circle (\shadowradius);
-        \fill[inner color=black ,outer color=white] ($(#1.south east)$) circle (\shadowradius);
-        \fill[inner color=black,outer color=white] ($(#1.north east)$) circle (\shadowradius);
-        \fill[ top color=black, bottom color=white] ($(#1.south west)+((0,-\shadowradius)$) rectangle ($(#1.south east)$);
-        \fill[left color=black,right color=white] ($(#1.south east)$) rectangle ($(#1.north east)+((\shadowradius,0)$);
-        \fill[bottom color=black,top color=white] ($(#1.north west)$) rectangle ($(#1.north east)+((0,\shadowradius)$);
-        \fill[right color=black,left color=white] ($(#1.south west)$) rectangle ($(#1.north west)+(-\shadowradius,0)$);
-    \end{pgfonlayer}
-    }
 
@@
     border/.style = { 
-        draw, rectangle, minimum width=\mw, minimum height=\mh, thick, align=center
+        draw, rectangle, minimum width=\mw, minimum height=\mh, ultra thick, align=center
     },
@@
     clockborder/.style = { 
-        trapezium, trapezium angle=60, minimum width=1cm, draw, very thick
+        trapezium, trapezium angle=60, minimum width=1cm, draw, ultra thick
     },
@@
         % Place the blocks 
-        \matrix (m) [matrix of nodes, ampersand replacement=\&, column sep = 1.5cm, row sep = -1cm]{
-                                            \& \draw pic (b1) {Component={B1}}; \&                                  \\
-        \draw pic (b2) {Component={B2}};    \&                                  \& \draw pic (b3) {Component={B3}}; \\
-                                            \& \draw pic (b4) {Component={B4}}; \&                                  \\[1.25cm]
-                                            \& \draw pic (b5) {Component={B5}}; \&                                  \\
+        \matrix (m) [matrix of nodes, ampersand replacement=\&, column sep = 1.25cm, row sep = 0.1cm, nodes={anchor=center}]{
+                                            \& \draw pic (b1) {Component={writer1}}; \& \draw pic (b2) {Component={writer2}}; \\
+        \draw pic (b3) {Component={odeds}};    \& \draw pic (b4) {Component={gain}}; \& \draw pic (b5) {Component={sdeds}}; \\
+                                            \& \draw pic (b6) {Component={writer3}}; \&                                  \\
         };
-        % Glow the blocks
-        \foreach \x in {1, 2, 3, 4, 5}{
-            \drawshadowbis{b\x-edge};
-        }
         % Draw connections 
@@
             \def\shiftamount{0.5mm};
-            \draw[-] (b2-edge.east) -- ++(0.5cm, 0cm) coordinate(a);
-            \draw[-] (a) -- node[midway, anchor=west]{L1} ++(0, 0.5*\mh) coordinate(b);
-            \draw[-] (a) -- node[midway, anchor=west]{L2} ++(0cm, -0.5*\mh) coordinate(c);
-            \draw[->] (b) |- (b1-edge.west);
-            \draw[->] (c) |- ([yshift=0.25cm] b4-edge.west);
-            \draw[-] (b1-edge.east) -- ++(0.4*\mw, 0cm) coordinate(d);
-            \draw[-] (b4-edge.east) -- ++(0.4*\mw, 0cm) coordinate(e);
-            \draw[-] ([yshift=1mm] d) -- node[midway, anchor=east]{L3} ++(0cm, -0.7*\mh) coordinate(f);
-            \draw[-] ([yshift=-1mm] e) -- node[midway, anchor=east]{L4} ++(0cm, 0.7*\mh) coordinate(g);
-            \draw[->] ([yshift=\shiftamount] f) |- ([yshift=2mm] b3-edge.west);
-            \draw[->] ([yshift=-\shiftamount] g) |- ([yshift=-2mm] b3-edge.west);
-            \draw (b5-edge.west) -- ++(-1cm, 0cm) coordinate (h);
-            \draw[->] ([yshift=-1mm] h) |- node[midway, anchor=east, yshift=-1.25cm]{L6}  ([yshift=-0.25cm] b4-edge.west);
-            \draw[->] ([yshift=1mm] g) |- node[midway, anchor=east, yshift=1.25cm]{L5} (b5-edge.east);
+            \draw[-] (b3-edge.east) -- ++(0.5cm, 0cm) coordinate(a);
+            \draw[->] (a) |- (b1-edge.west);
+            \draw[->] (a) |- (b4-edge.west);
+            \draw[->] (a) |- (b6-edge.west);
+            \draw[->] (b4-edge.east) -- (b5-edge.west);
+            \draw[-] (b5-edge.east) -- ++(1cm, 0cm) coordinate(b);
+            \draw[->] ([yshift=-1mm] b) |- (b2-edge.east);
         \end{scope}
@@
         % \Place clock 
-        \begin{scope}[shift={(-4.25cm, -4cm)}]
+        \begin{scope}[shift={(-4.25cm, -2.5cm)}]
             \draw pic(clk) {Clock={T}} ;
@@
         %  Draw rectangle 
-        \draw[dashed, thick] ([xshift=-0.25*\mw, yshift=-0.25*\mh] clk-clockedge.south west) rectangle ([xshift=2*\mw, yshift=0.25*\mh] b1-edge.north east);
-        \draw (b3-edge.south) node[yshift=-2.75*\mh, xshift=0.4*\mw]{Model};
+        \draw[dashed, thick] ([xshift=-0.25*\mw, yshift=-0.25*\mh] clk-clockedge.south west) rectangle ([xshift=3*\mw, yshift=0.25*\mh] b1-edge.north east);
+        \draw (clk-clockedge.east) node[yshift=0*\mh, xshift=5*\mw]{model};
     \end{tikzpicture}

### 2020-10-21 paper/figures/NetworkModel-WattzStrogatz/network_wattz_strogratz.tex
Added revised paper folder.

--- 2020-08-21 v0.2.1/assets/NetworkModel/network.tex
@@
-\documentclass[convert={density=900,size=1080x800,outext=.png}]{standalone}
+\documentclass[margin=5mm]{standalone}
 \usepackage[utf8]{inputenc}
@@
 
-\def\mw{2cm}
-\def\mh{1.75cm}
+\def\mw{1.25cm}
+\def\mh{1cm}
 \def\trianglecoordinate{2mm}
@@
         \matrix (m) [matrix of nodes, ampersand replacement=\&, column sep = 2cm, row sep = -0.75cm, nodes={anchor=center}]{
-            \draw pic (ds1) {Component={ODESystem $1$}}; \& \& \draw pic (ss1) {Component={StaticSystem $1$}}; \\
-            \draw node[]{\huge $\vdots$}; \& \draw pic (ss0) {Component={StaticSystem $0$}}; \& \draw[ultra thick] node[]{\huge $\vdots$}; \\
-            \draw pic (dsn) {Component={ODESystem $n$}}; \& \& \draw pic (ssn) {Component={Static\\System $n$}}; \\[1.5cm]
-             \& \draw pic (kutuk) {Component={Sink}}; \& \\
+            \draw pic (ds1) {Component={node $1$}}; \& \&  \\
+            \draw node[]{\huge $\vdots$}; \& \draw pic (ss0) {Component={coupler}}; \&  \\
+            \draw pic (dsn) {Component={node $n$}}; \& \& \\
+             \& \draw pic (kutuk) {Component={writer}}; \& \\
         };
-        % Glow the blocks
-        \foreach \x in {ds1, dsn, ss0, ss1, ssn, kutuk}{
-            \drawshadowbis{\x-edge};
-        }
         % Draw connections 
-        \begin{scope}[line width=2mm, >={Triangle[width=4mm,length=4mm]}]
+        \begin{scope}[line width=1.5mm, >={Triangle[width=3mm,length=3mm]}]
             \draw[-] (ds1-edge.east) -- ++(1cm, 0cm) coordinate(a);
             \draw[-] (dsn-edge.east) -- ++(1cm, 0cm) coordinate(b);
-            \draw[->] ([yshift=1mm] a) |- ([yshift=0.5cm] ss0-edge.west);
-            \draw[->] ([yshift=-1mm] b) |- ([yshift=-0.5cm] ss0-edge.west);
-            \draw (ss0-edge.west) node [xshift=-0.75cm]{\huge $\vdots$};
-            \draw (ss0-edge.east) node [xshift=0.75cm]{\huge $\vdots$};
-            \draw[-] ([yshift=0.5cm] ss0-edge.east) -- ++(0.5cm, 0cm) coordinate(c);
-            \draw[-] ([yshift=-0.5cm] ss0-edge.east) -- ++(0.5cm, 0cm) coordinate(d);
-            \draw[->] ([yshift=-1mm] c) |- (ss1-edge.west);
-            \draw[->] ([yshift=1mm] d) |- (ssn-edge.west);
+            \draw[->] ([yshift=0.75mm] a) |- ([yshift=0.4cm] ss0-edge.west);
+            \draw[->] ([yshift=-0.75mm] b) |- ([yshift=-0.4cm] ss0-edge.west);
+            \draw (ss0-edge.west) node [xshift=-0.75cm, yshift=0.1cm]{\huge $\vdots$};
+            \draw (ss0-edge.east) node [xshift=0.75cm, yshift=0.1cm]{\huge $\vdots$};
+            \draw[-] ([yshift=0.4cm] ss0-edge.east) -- ++(0.5cm, 0cm) coordinate(c);
+            \draw[-] ([yshift=-0.4cm] ss0-edge.east) -- ++(0.5cm, 0cm) coordinate(d);
+            \draw[->] ([yshift=-0.75mm] c) |- ++(1cm, 0.75cm)  node[anchor=west]{$u_1$};
+            \draw[->] ([yshift=0.75mm] d) |- ++ (1cm, -0.75cm)  node[anchor=west]{$u_n$};
             \draw[-] (ds1-edge.east) -- ++(0.75cm, 0cm) coordinate(e);
             \draw[-] (dsn-edge.east) -- ++(0.25cm, 0cm) coordinate(f);
-            \draw[->] (e) |- ([yshift=0.5cm] kutuk-edge.west);
-            \draw[->] (f) |- ([yshift=-0.5cm] kutuk-edge.west);
-            \draw (kutuk-edge.west) node [xshift=-0.75cm]{\huge $\vdots$};
+            \draw[->] (e) |- ([yshift=0.4cm] kutuk-edge.west);
+            \draw[->] (f) |- ([yshift=-0.4cm] kutuk-edge.west);
+            \draw (kutuk-edge.west) node [xshift=-0.75cm, yshift=0.1cm]{\huge $\vdots$};
             \draw[->] ([xshift=-1cm] ds1-edge.west) node[anchor=east]{$u_1$} -- (ds1-edge.west);
             \draw[->] ([xshift=-1cm] dsn-edge.west) node[anchor=east]{$u_n$} -- (dsn-edge.west);
-            \draw[->] (ss1-edge.east) -- ([xshift=1cm] ss1-edge.east) node[anchor=west]{$u_1$};
-            \draw[->] (ssn-edge.east) -- ([xshift=1cm] ssn-edge.east) node[anchor=west]{$u_n$};
+            % \draw[->] (c.east) -- ([xshift=1cm] c) node[anchor=west]{$u_1$};
+            % \draw[->] (ssn-edge.east) -- ([xshift=1cm] ssn-edge.east) node[anchor=west]{$u_n$};
         \end{scope}
@@
         % Draw rectangle for network
-        \draw[thick, dashed] ([xshift=-1.75cm, yshift=0.25cm] ds1-edge.north west) rectangle ([xshift=1.75cm, yshift=-1.25cm] ssn-edge.south east);
-        \draw (ssn-edge.south) node[yshift=-1cm, xshift=1.7cm]{SubSystem};
+        \draw[thick, dashed] ([xshift=-2cm, yshift=0.25cm] ds1-edge.north west) rectangle ([xshift=2.5cm, yshift=-1.25cm] kutuk-edge.south east);
 
         % \Place clock 
-        \begin{scope}[shift={(-5.75cm, -5cm)}]
+        \begin{scope}[shift={(-5cm, -2.25cm)}]
             \draw pic(clk) {Clock={T}} ;
@@
         %  Draw rectangle 
-        \draw[dashed, thick] ([xshift=-0.5*\mw, yshift=-0.25*\mh] clk-clockedge.south west) rectangle ([xshift=1*\mw, yshift=0.5*\mh] ss1-edge.north east);
-        \draw (clk-clockedge.east) node[yshift=0*\mh, xshift=5.75*\mw]{Model};
+        % \draw[dashed, thick] ([xshift=-0.5*\mw, yshift=-0.25*\mh] clk-clockedge.south west) rectangle ([xshift=1*\mw, yshift=0.5*\mh] ss1-edge.north east);
+        \draw (clk-clockedge.east) node[yshift=0*\mh, xshift=5.75*\mw]{model};
     \end{tikzpicture}

### 2020-10-21 paper/figures/NetworkModel/network.tex
Added revised paper folder.

--- 2020-08-21 v0.2.1/assets/NetworkModel/network.tex
@@
         \matrix (m) [matrix of nodes, ampersand replacement=\&, column sep = 2cm, row sep = -0.75cm, nodes={anchor=center}]{
-            \draw pic (ds1) {Component={ODESystem $1$}}; \& \& \draw pic (ss1) {Component={StaticSystem $1$}}; \\
-            \draw node[]{\huge $\vdots$}; \& \draw pic (ss0) {Component={StaticSystem $0$}}; \& \draw[ultra thick] node[]{\huge $\vdots$}; \\
-            \draw pic (dsn) {Component={ODESystem $n$}}; \& \& \draw pic (ssn) {Component={Static\\System $n$}}; \\[1.5cm]
-             \& \draw pic (kutuk) {Component={Sink}}; \& \\
+            \draw pic (ds1) {Component={ODE\\Dinamik\\Sistem $1$}}; \& \& \draw pic (ss1) {Component={Hafıza $1$}}; \\
+            \draw node[]{\huge $\vdots$}; \& \draw pic (ss0) {Component={Statik\\Sistem}}; \& \draw[ultra thick] node[]{\huge $\vdots$}; \\
+            \draw pic (dsn) {Component={ODE\\Dinamik\\Sistem $n$}}; \& \& \draw pic (ssn) {Component={Hafıza $n$}}; \\[1.5cm]
+             \& \draw pic (kutuk) {Component={Kütük}}; \& \\
         };
-        % Glow the blocks
-        \foreach \x in {ds1, dsn, ss0, ss1, ssn, kutuk}{
-            \drawshadowbis{\x-edge};
-        }
+        % % Glow the blocks
+        % \foreach \x in {ds1, dsn, ss0, ss1, ssn, kutuk}{
+        %     \drawshadowbis{\x-edge};
+        % }
         % Draw connections 
@@
         \draw[thick, dashed] ([xshift=-1.75cm, yshift=0.25cm] ds1-edge.north west) rectangle ([xshift=1.75cm, yshift=-1.25cm] ssn-edge.south east);
-        \draw (ssn-edge.south) node[yshift=-1cm, xshift=1.7cm]{SubSystem};
+        \draw (ssn-edge.south) node[yshift=-1cm, xshift=1.7cm]{Alt Sistem};
 

### 2020-10-21 paper/header.tex
Added revised paper folder.

% **************GENERATED FILE, DO NOT EDIT**************

\title{Causal.jl:\\A Modeling and Simulation Framework for Causal Models}

\author[1]{Zekeriya Sarı}
\author[1]{Serkan Günel}
\affil[1]{Deparment of Electrical and Electronics Engineering, Dokuz Eylül University, İzmir, TURKEY}

\keywords{System Modeling, Causal Modeling, System Simulation, Dynamical Systems, Julia Programming Language}

\hypersetup{
pdftitle = {Causal.jl:\\A Modeling and Simulation Framework for Causal Models},
pdfsubject = {JuliaCon 2019 Proceedings},
pdfauthor = {Zekeriya Sarı, Serkan Günel},
pdfkeywords = {System Modeling, Causal Modeling, System Simulation, Dynamical Systems, Julia Programming Language},
}

### 2020-10-21 paper/paper.tex
Added revised paper folder.

% JuliaCon proceedings template
\documentclass{juliacon}
\setcounter{page}{1}

% Packages added to the template
\usepackage{subfig}
\usepackage{amsmath}
\usepackage{tikz}
\usepackage{cite}

\begin{document}

\input{header}

\maketitle

\begin{abstract}

    This paper introduces a modeling and simulation framework, Causal.jl,  that enables fast and effective system simulations and online and offline data analyzes. Causal.jl adopts a causal modeling approach in which a model consists of components that process data and the connections that transfer the data flowing between these components. The framework developed makes it possible to simulate discrete time or continuous time, static or dynamical systems. In particular, it is possible to simulate dynamical systems modeled by various types of equations such as the ordinary, random ordinary, stochastic, delayed differential, differential-algebraic equations, and discrete-time difference equations. During the simulation, the data flowing through the connections can be processed online and offline, and specialized analyzes can be performed. These analyzes can also be enriched with plugins that can be easily defined using the standard Julia library or various Julia packages. The simulation is performed by evolving the model components between sampling time intervals individually and in parallel. The independent evolution of the components allows the simulation of the models consisting of the components represented by different mathematical equations, while the parallel evolution of components increases the simulation performance.

\end{abstract}

\section{Introduction}

Numerical simulations can be expressed as solving the mathematical equations derived from modeling physical systems. Based on the system's properties at hand and abstraction level in the modeling, mathematical equations may be ordinary, stochastic, delay differential, or difference equations. High-speed performance and the ability to offer useful analysis tools are other typical features expected from an effective simulation environment.

Many simulation environments are available for numerical analysis of systems\cite{elmqvist1978structured,nytsch2006advanced,zimmer2008introducing,mosterman2002hybrsim,van2001variables,giorgidze2009higher,pfeiffer2012pysimulator,simulink}. They are capable of allowing simulations that are represented by ordinary differential equations and differential algebraic equations, mostly. This is restrictive given the variety of mathematical equations that can be derived from the modeling\cite{rackauckas2017differentialequations}. Besides, many of the existing simulation environments lack modern computational methods such as parallel computing.

In this study, Causal.jl, a modeling and simulation framework for causal models, is introduced \cite{causal}. The aim is to model large scale complex system networks easily and to provide fast and effective simulations. For this purpose, Julia, an open-source, high level, general purpose dynamical programming language designed for high-performance numerical analysis and computational science, has been used. Although Julia is a dynamical language, owing to its Just-in-Time(JIT) compiler developed on Low Level Virtual Machine(LLVM), it can reach the high-speed performance of static languages such as C\cite{bezanson2017julia,julialang}. It supports various parallel computing techniques at thread and process levels. In addition to Julia's standard library, numerous specialized packages developed for different fields such as data science, scientific computing, are also available. Julia's high-speed performance and parallel computing support are essential in meeting the need to design a  fast and effective simulation environment. Julia's syntax can be enlarged purposefully using its metaprogramming support. The analyzes scope of the simulation framework can be extended with new plugins that can be easily defined. It is possible to analyze discrete or continuous-time, static, or dynamical systems. In particular, it is possible to simulate dynamical systems modeled by ordinary, random ordinary, stochastic, delay differential, differential-algebraic, and/or discrete difference equations simultaneously. Unlike its counterparts, the models do not evolve at once for the whole simulation duration. Instead, the model components evolve between sampling time intervals individually. While individual evolution of the components enables the simulation of systems consisting of components represented by different mathematical models, parallel evolution of components increases the simulation performance.

\section{Modeling and Simulation}

\subsection{Modeling}
Causal.jl adopts causal modeling\footnote{Causal modeling is also known as signal flow modeling or block diagram modeling} approach in modeling systems. In causal modeling approach, a model consists of components and connections (Figure \ref{fig: simple model})\cite{matei2012modeling}. The simulation of the model is performed in a clocked environment. That is, the model is not simulated in one shot by solving a single mathematical equation system that represents the whole model, but instead, it is simulated by evolving the components between sampling intervals in parallel, individually.

The components interact with each other through the connections that are bound to their input/output ports. The components are data processing agents, and their behavior determines how the data is processed. Depending upon the nature of the system and the modeling, these equations may differ, i.e., they may or may not contain derivative terms, or they may contain the continuous or discrete-time variable, etc. The dataflow through the connections is unidirectional, i.e., a component is driven by other components that write data to its input port.

The model simulation is performed by evolving the components individually. A reference clock is used to make the components have a common time base. The clock generates pulses at simulation sampling intervals. These pulses are used to trigger the components during the run stage of the simulation. Each triggered component reads its input data from its input port, calculates its output according to its mathematical model, and writes the result to its output port.

\begin{figure}
    \centering
    \includegraphics[width=0.75\linewidth]{figures/Model/model.pdf}
    \caption{A model consisting of the components B1, $\ldots$, B5 and the connections L1, $\ldots$, L6. T is the common time reference of the model.}
    \label{fig: simple model}
\end{figure}

\subsection{Components}

The component types in Causal.jl are shown in Figure \ref{fig: component types}. The components can be classified as sources, sinks, and systems.

The sources are the components that generate outputs as functions of time only. When triggered, a source computes its output according to its readout function and writes the result to its output port. The sources do not have input ports.

The sinks are data processing units. Their primary goal is to process the data flowing through the connections online. When triggered, a sink reads its input data from its input port and processes it. The data can be visualized by being plotted on a graphical user interface, can be observed by being printed on a console, or can be recorded in data files. The sinks' data processing scope can be enriched by integrating new plugins that can be developed using the standard Julia library or various available Julia packages. Invariants, spectral properties, or statistical information can be extracted from the data. Parameter estimation can be performed, or various signal processing techniques can be applied. Causal.jl has been designed to be flexible enough to allow the users to extend its data analyzes scope by integrating newly-defined plugins.

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{figures/ComponentsCompressed/components_compresses.pdf}
    \caption{Component types in Causal.jl. $u, x, y$ signify the input, state, output of a system, respectively. $t$ and $k$ are continuous and discrete time variable, respectively. $W$ is the stochastic process corresponding to the noise and $x_\tau$ is the state $x$ delayed by $\tau$ seconds in time. $f$(and $h$) is the right-hand-side function of the differential equation representing the system and $g$ is the readout function.}
    \label{fig: component types}
\end{figure}

A static system is described by a readout equation solely. When triggered, a static system reads its input data from its input port, calculates its output according to its readout function, and writes the result to its output port. In dynamic systems, however, the system behavior is characterized by the states. The output of a dynamical system depends on its input, previous state(s), and time. Therefore, a dynamical system is described by a differential equation and a readout equation, classically. When triggered, a dynamical system reads its input from its input port, updates its state according to the differential equation, calculates its output according to its readout function, and writes the result to its output port. Being developed on top of DifferentialEquations.jl, Causal.jl is capable of simulating the dynamical systems represented by differential equations in the form of the ordinary differential equations(ODE), differential-algebraic equations(DAE), random ordinary differential equations(RODE), stochastic differential equations(SDE), delay differential equations(DDE) or discrete difference equations \cite{rackauckas2017differentialequations}. Most of the available simulation environments allow the systems represented by ordinary differential equations or differential-algebraic equations\cite{elmqvist1978structured,nytsch2006advanced,zimmer2008introducing,mosterman2002hybrsim,van2001variables,giorgidze2009higher,pfeiffer2012pysimulator,simulink}. Therefore, analyzes such as noise or delay analysis or unexpected change of system parameters cannot be performed in these simulation environments, easily. On the contrary, Causal.jl makes it possible for all these analyses to be performed owing to its ability to solve such a wide range of differential equations.

\subsection{Ports and Connections}
A port is a bunch of pins to which the connections are bound. There are two types of pins: an output pin that transfers data from the inside of the component to its outside, and an input pin that transfers data from the outside of the component to its inside. There are two types of ports: an output port that consists of output pins and an input port that consists of input pins.

\begin{figure}
    \centering
    \subfloat[]{\includegraphics[width=0.225\linewidth]{figures/Tasks/reader_task.pdf} \label{subfig: reader task}} \hfil 
    \subfloat[]{\includegraphics[width=0.225\linewidth]{figures/Tasks/writer_task.pdf} \label{subfig: writer task}} \hfil 
    \subfloat[]{\includegraphics[width=0.4\linewidth]{figures/Tasks/reader_writer_task.pdf} \label{subfig: reader writer task}} 
    \caption{\protect\subref{subfig: reader task} A readable connection, \protect\subref{subfig: writer task} A writable connection, \protect\subref{subfig: reader writer task} A readable and writable connection}
    \label{fig: tasks}
\end{figure}

The data transferred to a port are transferred to its connections. The data transfer through the connections is performed over the links of the connections. The links are built on top Julia channels. The data written to(read from) a link is written to(read from) its channel. Running Julia tasks bound to the channels must exist for the data to flow through these channels. Julia tasks are the control flow features that allow calculations to be flexibly suspended and maintained without directly communicating the task scheduler of the operating system\cite{julialang}. The communication and the data exchange between the tasks are carried out through Julia's channels to which they are bound.

Figure \ref{fig: tasks} depicts the tasks that must be bound to a connection to make it readable, writable, and both readable and writable, symbolically. The writer(the reader) task is the task that writes(reads) data to(from) the connection. A running writer task must be bound to the connection on the opposite side to read data from one side of a connection. This connection is called a readable connection. Similarly, to write data to one side of a connection, a running reader task must be bound to the connection at the other side. This connection is called a writable connection. If both running writer and reader tasks are bound to both sides of a connection, then the data can both be read from and written to the connection. Such a connection is called a readable and writable connection. The dataflow through a connection is only allowed if the connection is both readable and writable connection. The data read from a readable connection is the data written to the connection by the writer task of the connection. If the data have not been written to the connection by its writer task during a reading process yet, then reading does not occur, and the writer task is waited to put data to the connection. Similarly, if the data on a connection has not been read from the connection by its reader task during a writing process yet, then the reader task is waited to take data from the connection.

In the modeling approach adopted, the components reading data from a connection are driven by other components writing data to the connection. Therefore, all of the model's connections must be readable and writable so that data can flow through the connections. This necessitates that all the connections of the model must be connected to a component from both ends. Otherwise, the simulation gets stuck and does not terminate.

\subsection{Simulation}
A model to be simulated consists of components connected to each other and a time reference. The time reference is used to sample the continuous-time signals flowing through the model's connections and trigger the components. The simulation is performed by triggering the components with pulses generated by the time reference of the model at sampling time instants. When triggered, the components evolve to compute their outputs.

The simulation stages are shown in Figure \ref{fig: flowchart} basically. Performing, inspecting, and reporting all the simulation stages is carried out automatically without requiring any user intervention.

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{figures/FlowChart/flowchart.pdf}
    \caption{Flowchart of the simulation stages.}
    \label{fig: flowchart}
\end{figure}

\begin{figure}
    \centering
    \subfloat[]{\includegraphics[width=0.49\linewidth]{figures/AlgebraicLoop/unbrokenloop.pdf} \label{subfig: unbroken algebraic loop}}
    \subfloat[]{\includegraphics[width=0.49\linewidth]{figures/AlgebraicLoop/brokenloop.pdf} \label{subfig: broken algebraic loop}}
    \caption{\protect\subref{subfig: unbroken algebraic loop} An algebraic loop consisting of the components Static System, Dynamical System I and Dynamical System II. \protect\subref{subfig: broken algebraic loop} Breaking of the loop with a Memory component. }
    \label{fig: algebraic loop}
\end{figure}

In the \textit{inspection} stage, the model is inspected to see whether the model is suitable for simulation. If connections having any unconnected terminals are detected, the simulation is terminated at this stage. The model is not suitable for simulation when algebraic loops exist\cite{lamego2001adaptive}. An algebraic loop is a closed-loop consisting of one or more components whose outputs are directly dependent on their inputs. Almost every system that includes feedbacks has algebraic loops. The simulation does not proceed because none of the components in the loop can generate output to break the loop. Such a problem can be solved by redesigning the model so that the model has no algebraic loops, solving the feed-forward algebraic equation of the loop, or inserting a memory component with a particular initial condition anywhere in the loop. Causal.jl provides all these loop-breaking solutions. During the \textit{inspection}, when algebraic loops are detected, all the loops are broken, if possible, automatically. Otherwise, a report is printed to notify the user to insert memory components to break the loops.

\begin{figure}
    \centering
    \subfloat[]{\includegraphics[width=0.5\linewidth]{figures/TaskForComponents/components.pdf} \label{subfig: components}} \\
    \subfloat[]{\includegraphics[width=.75\linewidth]{figures/TaskForComponents/tasks.pdf} \label{subfig: tasks}}
    \caption{Launching tasks for the connections. \protect\subref{subfig: components} An example model part consisting of the components B1 and B2 and the connections L1, L2 and L3. \protect\subref{subfig: tasks} Tasks launched corresponding to the connections.}
    \label{fig: tasks for components}
\end{figure}

If the model passes the \textit{inspection}, the writer and reader tasks are launched in the \textit{initialization} stage to ensure the data flow through the model connections. At this point, a writer and a reader task are bound to each connection. In Figure \ref{subfig: components} model part consisting of components B1, B2, and the connections L1, L2, L3 are shown. When triggered, the B1 reads data from L1, calculates its output, and writes to L2. Similarly, when triggered, B2 reads data from the L2, calculates its output, and writes to the L3. The tasks bounded to L1, L2, and L3 corresponding to B1 and B2 are shown in Figure \ref{subfig: tasks}. Since B1 reads the data from L1 and writes data to L2, a reader task is bounded to L1, and a writer task is bounded L2. Similarly, since B2 reads the data from L2 and writes data to L3, a reader task is bounded to L2, and a writer task is bounded L3. Since both a writer and a reader task are bound to the L2, data can flow from B1 to B2 through L2. A task manager is constructed to check whether the tasks launched during the \textit{initialization} are running correctly throughout the simulation.

The \textit{initialization} is followed by the \textit{run} stage. The tasks that are launched corresponding to the components during the \textit{initialization} expect the components to be triggered through their trigger pins. These triggers are generated in the sampling instants by the model clock during the \textit{run} stage. It is possible to sample the signals flowing through the connections at equal or independent time intervals. The generated triggers are put into the trigger pins of the components.

When the \textit{run} stage is completed, the tasks launched at the \textit{initialization} stage are closed in the \textit{termination} stage and the simulation ends.

The sampled values are interpolated for a duration of one sampling period so that the components can evolve independently. The sampling period is an essential factor that affects the accuracy of the simulation results directly.

\section{Illustrative Examples}

\subsection{Simulation of Models Having Different Component Types}
\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{figures/CoupledChuaModel/coupled_chua_model.pdf}
    \caption{A model consisting of components represented by different equation types.}
    \label{fig: coupled model}
\end{figure}

In Causal.jl, it is possible to simulate models that include components represented by different types of equations. In Figure \ref{fig: coupled model} is given such an example model.`odeds` is a dynamical system represented by the ordinary differential equation in (\ref{eq: coupled ode}) where where $x_1, y_1, z_1$ are the state variables and $a=35, b=3, c = 28$ are system parameters.
\begin{equation}
    \begin{split}
        \dot{x}_1 &= a (y_1 - x_1) \\
        \dot{y}_1 &= (c - 1) x_1 + c y_1 - x_1 z_1 \\
        \dot{z}_1 &= x_1 y_1 - b z_1
    \end{split}
    \label{eq: coupled ode}
\end{equation}
`sdsds` is dynamical system that is represented by the stochastic differential equation in (\ref{eq: coupled sde}) where $x_2, y_2, z_2$ are the state variables, $u=[u_1,u_2, u_3]$ is the input, $\eta$ is noise strength, $W_t$ is the Wiener process corresponding to the noise and $a, b, c$ are the same as those in (\ref{eq: coupled ode}).
\begin{equation}
    \begin{split}
        dx_2 &= (a (y_1 - x_1) + u_1) dt + \eta dW_t \\
        dy_2 &= ((c - 1) x_1 + c y_1 - x_1 z_1)dt + \eta dW_t \\
        dz_2 &= (x_1 y_1 - b z_1 + u_3) dt + \eta dW_t 
    \end{split}
    \label{eq: coupled sde}
\end{equation}
`gain` is a static system whose input output relation is given in (\ref{eq: gain}) where $u, y, \epsilon$ are the input, output and gain coefficient of the system. 
\begin{equation}
    y = \epsilon u
    \label{eq: gain}
\end{equation}
`writer1` and `writer2` are used to record the outputs of `odeds` and `sdeds`, respectively, while `writer3` is used to record the fast Fourier transform(FFT) of the data flowing out of `odeds`\cite{proakis2004digital}.

Being a domain-specific-language, Causal.jl provides a syntax for handy model construction. The program written using Causal.jl to construct and simulate the model in Figure \ref{fig: coupled model} is given in Listing \ref{lst: coupled codes}. The program first starts with the type definitions of the components `odeds`, `sdeds`, and `gain`, together with their fields' default values. Note that the types of components are defined as subtypes of the corresponding abstract component types, which shows how the user-defined component types can enrich the standard library of Causal.jl. `writer1` and `writer2` are used directly to record the data without further processing, so they do not need additional data processing plugins.
On the other hand, rather than directly recording the data, `writer3` is used to process the data online, so it needs an additional plugin. `FFTPlug` is defined for this purpose, and `writer3` is equipped with an instance. For the sake of this example, we used the `fft` function \cite{fftw}. The model is constructed and simulated for $100$ seconds with a step size of $0.001$ seconds. After the simulation, the data in `write1` and `writer2` are read back and plotted in Figure \ref{fig: coupled simulation results}. From Figure \ref{subfig: coupled simulation sde}, the presence of the noise is apparent in the trajectory of `sdeds`.

The individual evolution of components makes it possible to simulate such models that include components represented by different equations.

Causal.jl adopts a causal modeling approach in which the data flow through the connections is unidirectional. Components that write data to a connection drives other components that read data from the same connection. Thus, the topological structure of a model can be extracted by following the components that read data from the connections bound to the output ports of model components.

The order in which the connections are specified is arbitrary. One does not need to follow the true data flow directions through the connections. Therefore, complex topologies with many components can be defined concisely.

\begin{figure}
    \centering
    \subfloat[]{
        \begin{tikzpicture}
            \node[](plt){\includegraphics[scale=0.25]{figures/ChenSystemSimulations/odeds.pdf}};
            \node[] at (plt.south) {$x_1$};
            \node[] at (plt.west) {$y_1$};
        \end{tikzpicture}
        \label{subfig: coupled simulation ode}
        }\\
    \subfloat[]{
        \begin{tikzpicture}
            \node[](plt){\includegraphics[scale=0.25]{figures/ChenSystemSimulations/sdeds.pdf}};
            \node[] at (plt.south) {$x_2$};
            \node[] at (plt.west) {$y_2$};
            \end{tikzpicture}
        \label{subfig: coupled simulation sde}
    }
    \caption{\protect\subref{subfig: coupled simulation ode} $x_1 - y_1$ trajectory of `odeds`. \protect\subref{subfig: coupled simulation sde} $x_2 - y_2$ trajectory of `sdeds`.}
    \label{fig: coupled simulation results}
\end{figure}

\subsection{Simulation of Models Consisting of a Large Number of Nodes}
In Causal.jl, its is possible to simulate large scale complex models consisting of a large number of dynamical system nodes. As an example, a network of continuous time identical dynamical systems is given Figure \ref{fig: network graph}. The nodes of the network evolve by 
\begin{equation}
    \dot{\bm{x}}_i = f(\bm{x}_i) + \bm{u}_i, \quad i = 1, \ldots, n
    \label{eq: network equation}
\end{equation}
where 
\begin{equation}
    \bm{u}_i = \sum_{i = 1}^n \epsilon_{ij} \bm{P} \bm{x}_j, \quad i = 1, \ldots, n,
    \label{eq: network node inputs}
\end{equation}
$n$ is the number of nodes, $\bm{x}_i \in \mathbb{R}^d$ is the state vector of node $i$, $f: \mathbb{R} \mapsto \mathbb{R}^d$ is the function corresponding to the individual node dynamics, $\epsilon_{ij} \geq 0 $ is the coupling strength between the nodes $i$ and $j$. The diagonal matrix $\bm{P} = diag(p_1, \ldots, p_d)$ determines by which state variables the nodes are connected to each other. The matrix $\bm{E} = [\epsilon_{ij}] \in \mathbb{R}^{n, n}, \; \epsilon_{ij} = \epsilon_{ji} \geq 0, \; \sum_{j = 1}^n \epsilon_{ij} = 0, i = 1, \ldots, n$ determines the network topology: if $\epsilon_{ij} > 0$, there is a connection between the nodes $i$ and $j$, if $\epsilon_{ij} = 0$, there is no connection between the nodes $i$ and $j$.

In the network given in Figure \ref{fig: network graph}, $n=50$,  $f$ is the Lorenz dynamics given by,
\begin{equation}
    \begin{split}
        \dot{x}_{i,1} &= \sigma (x_{i, 2} - x_{i, 1}) \\
        \dot{x}_{i,2} &= x_{i, 1} (\rho -  x_{i, 3}) - x_{i, 2} \\
        \dot{x}_{i,3} &= x_{i, 1} x_{i, 2} - \beta x_{i, 3}
    \end{split}
\end{equation}
where $\sigma=10, \beta=8/3, \rho=28$ are system parameters, $\bm{P} = diag(1, 0, 0)$. The network has Wattz-Strogatz topology that has a vertex degree of $10$ and that is randomized with a probability of $0.5$\cite{watts1998collective}.

\begin{figure}
    \centering
    \includegraphics[width=0.5\linewidth]{figures/Networks/wattz_strogatz.pdf}    
    \caption{A network consisting of identical dynamical system nodes The spheres and the line segments represent the dynamical system nodes and the connection between them, respectively.}
    \label{fig: network graph}
\end{figure}

The model in Figure \ref{fig: network graph} is given in Figure \ref{fig: network model}. `node $k$` for $k =1, \ldots, n$ correspond to the dynamical system nodes of the network.  From (\ref{eq: network equation}) and (\ref{eq: network node inputs}), we see that the states of the nodes are taken as their outputs, weighted by the coupling strengths and fed back to their inputs. Hence, `coupler` is used to construct the weighted outputs. `writer` records the nodes' outputs. The model has algebraic loops $L_k$ for $k = 1, \ldots, n$, where the algebraic loop $L_k$ consists of `node $k$` and `coupler`.

\begin{figure}
    \centering
    \includegraphics[width=0.8\linewidth]{figures/NetworkModel-WattzStrogatz/network_wattz_strogratz.pdf}
    \caption{Block diagram model of the network in Figure \ref{fig: network graph}.}
    \label{fig: network model}
\end{figure}

The program written using Causal.jl to construct and simulate the model in Figure \ref{fig: network model} is given in Listing \ref{lst: network codes}. Having defined the types of dynamical system nodes and the coupler, the model is constructed and simulated for $100$ seconds with a sampling period of $0.005$ seconds. After the simulation, the simulation data is read back from the writer and the mean square error (MSE) 
\begin{equation}
    MSE(t) = \dfrac{1}{n} \sum_{i = 2}^n \Vert \bm{x}_{1,1}(t) - \bm{x}_{i,1}(t) \Vert
\end{equation}
is computed and plotted. It is seen from Figure \ref{subfig: network error} that the all the nodes in the network synchronize with each other as the MSE goes to zero as time evolves.

Note from the program in Listing \ref{lst: network codes} that memory components are not used to break algebraic loops of the model. Causal.jl is capable of detecting and breaking these algebraic loops automatically without requiring any user intervention.

\begin{figure}
    \centering
    \subfloat[]{
        \begin{tikzpicture}
            \node[](plt){\includegraphics[scale=0.25]{figures/NetworkSimulation-WattzStrogatz/waveform.pdf}};
            \node[] at (plt.south) {$t$ [seconds]};
            \node[] at (plt.west) {$x_{1,1}$};
        \end{tikzpicture}
        \label{subfig: network timewaveform}
        }\\[-0.1cm]
    \subfloat[]{
        \begin{tikzpicture}
            \node[](plt){\includegraphics[scale=0.25]{figures/NetworkSimulation-WattzStrogatz/trajectory.pdf}};
            \node[] at (plt.south) {$x_{1,1}$};
            \node[] at (plt.west) {$x_{1, 2}$};
            \end{tikzpicture}
        \label{subfig: network trajectory}
    } \\[-0.1cm]
    \subfloat[]{
        \begin{tikzpicture}
            \node[](plt){\includegraphics[scale=0.25]{figures/NetworkSimulation-WattzStrogatz/error.pdf}};
            \node[] at (plt.south) {$t$ [seconds]};
            \node[xshift=-0.25cm] at (plt.west) {MSE};
            \end{tikzpicture}
        \label{subfig: network error}
    }
    \caption{Simulation results the model given in Figure \ref{fig: network model}. \protect\subref{subfig: network timewaveform} Time waveform of $x_{1,1}$. \protect\subref{subfig: network trajectory} $x_{1,1} - x_{1,2}$ trajectory. \protect\subref{subfig: network trajectory} MSE.}
    \label{fig: network simulation results}
\end{figure}

\section{Conclusion}
In this paper, we introduced Causal.jl. In Causal.jl, the simulation is performed by evolving the components according to their mathematical equations between the sampling intervals in parallel and independently. The components can be static or dynamical or represented by mathematical equations having continuous or discrete-time variables. The simulation of the models consisting of components defined by ordinary, random ordinary, stochastic, delay differential, differential-algebraic, or difference equations is possible. It is not an obligation to describe all the model components with the same type of mathematical equation.

The data flowing through the connections can be directly recorded or visualized during the simulation. In addition to the offline analyzes, with user-defined plugins, it is also possible to carry out online data analysis such as extracting statistical or spectral properties, applying different signal processing techniques, etc.

The model components evolve in parallel and simultaneously. The tasks of the Julia programming language is used for this parallel evolution. The tasks allow switching between the evolution of the components during the simulation. Using the Julia programming language's distributed computing tools, it is possible to distribute computation workload on multiple processors.

Especially when considering extensive system networks consisting of thousands of system nodes, it is an important advantage that the system models can be created easily and quickly, that such models can be simulated in multiple microprocessor cores with distributed programming tools and that the proposed tool can provide this with an easy syntax.

\section{Acknowledgements}
This work was supported by Scientific Research Projects Funding Program of Dokuz Eylül University (project no: 2020.KB.FEN.007).

\input{bib.tex}

\onecolumn
\appendix

\begin{lstlisting}[caption={Program using Causal.jl for the simulation of the system in Figure \ref{fig: coupled model}. Plots.jl is used to plot the simulation data while FFTW.jl is used to compute the FFT of the simulation data \cite{plots, fftw}.}, label={lst: coupled codes}, language=Julia]
using Causal, Plots, FFTW

# Define ODE system type under AbstractODESystem
@def_ode_system mutable struct ODESys{RH, RO, IP, OP} <: AbstractODESystem
    righthandside::RH = function fode(dx, x, u, t, a=35., b=3., c=28.)
        dx[1] = a * (x[2] - x[1])
        dx[2] = (c - a) * x[1] + c * x[2] - x[1] * x[3]
        dx[3] = x[1] * x[2] - b * x[3]
    end
    readout::RO = (x, u, t) -> x 
    state::Vector{Float64} = rand(3)
    input::IP = nothing
    output::OP = Outport(3)
end

# Define SDE system type under AbstractSDESystem
@def_sde_system mutable struct SDESys{DR, DF, RO, IP, OP} <: AbstractSDESystem
    drift::DR = function fsde(dx, x, u, t, a=35., b=3., c=28.)
        dx[1] = a * (x[2] - x[1]) + u[1](t)
        dx[2] = (c - a) * x[1] + c * x[2] - x[1] * x[3] + u[2](t)
        dx[3] = x[1] * x[2] - b * x[3] + u[3](t)
    end
    diffusion::DF = (dx, x, u, t, η=10.) -> (dx .= η) 
    readout::RO = (x, u, t) -> x
    state::Vector{Float64} = rand(3)
    input::IP = Inport(3)
    output::OP = Outport(3)
end

# Define Gain system type under AbstractStaticSystem
@def_static_system struct GainSys{RO,IP,OP} <: AbstractStaticSystem 
    readout::RO = (u,t, ϵ=0.1) -> ϵ * u 
    input::IP = Inport(3)
    output::OP = Outport(3)
end

# Define plugin type under AbstractPlugin
@def_plugin struct FFTPlug{PR} <: AbstractPlugin 
    process::PR = x -> fft(x, 2)    # Computes FFT of the data `x`
end

# Construct model
@defmodel model begin 
    @nodes begin 
        odeds = ODESys()    # Add odeds component  
        gain = GainSys()    # Add gain  component   
        sdeds = SDESys()    # Add sde components
        writer1 = Writer(input=Inport(3))                   # Add writer without plugin
        writer2 = Writer(input=Inport(3))                   # Add writer without plugin
        writer3 = Writer(input=Inport(3), plugin=FFTPlug()) # Add writer with `FFTPlug` plugin
    end
    @branches begin 
        odeds => gain       # Add connection from `odeds` to `gain`.
        gain => sdeds       # Add connection from `gain` to `sdeds`.
        odeds => writer1    # Add connection from `odeds` to `writer1`.
        sdeds => writer2    # Add connection from `sdeds` to `writer2`.
        odeds => writer3    # Add connection from `odeds` to `writer3`.
    end 
end

# Simulate model 
sim = simulate!(model, 0, 0.001, 100) # Simulate from 0 to 100 seconds with a step size of 0.001 seconds

# Plot simulation data 
t, x1 = read(getnode(model, :writer1).component)
t, x2 = read(getnode(model, :writer2).component)
x3 = read(getnode(model, :writer3).component, flatten=false)
plot(x1[:, 1], x1[:, 2], subplot=1, label="")
plot(x2[:, 1], x2[:, 2], subplot=2, label="")   
println(x3)  
\end{lstlisting}

\begin{lstlisting}[caption={Program using Causal.jl for the simulation of the system in Figure \ref{fig: network graph}. Plots.jl is used to plot the simulation data while LightGraphs.jl is used to construct the connectiviy matrix of the network topology \cite{plots, lightgraphs}}, label={lst: network codes}, language=Julia]
using Causal, Plots
using LightGraphs: watts_strogatz, laplacian_matrix

# Define DynamicSystem type under AbstractODESystem
@def_ode_system mutable struct DynamicSystem{RH, RO, IP, OP} <: AbstractODESystem
    righthandside::RH = function f(dx, x, u, t, σ=10., β=8/3, ρ=28)
        dx[1] = σ * (x[2] - x[1]) + u[1](t)
        dx[2] = x[1] * (ρ - x[3]) - x[2] + u[2](t)
        dx[3] = x[1] * x[2] - β * x[3] + u[3](t)
    end
    readout::RO = (x, u, t) -> x
    state::Vector{Float64} = rand(3)
    input::IP = Inport(3)
    output::OP = Outport(3) 
end

# Define Coupler type under AbstractStaticSystem
@def_static_system struct CouplerSystem{ET, CT, IP, OP, RO} <: AbstractStaticSystem
    E::ET
    P::CT
    input::IP = Inport(size(E, 1) * size(P, 1))
    output::OP = Outport(size(E, 1) * size(P, 1))
    readout::RO =  (u, t, E=E, P=P) ->  kron(E, P) * u
end

# Construct network parameters 
n = 50      # Number of nodes 
d = 3       # Dimension of each node
ϵ = 20.     # Coupling strength 
components = [DynamicSystem() for i in 1 : n]
E = ϵ * collect(-laplacian_matrix(watts_strogatz(n, 10, 0.5)))  # Connectivity matrix of network topology
P = [1 0 0; 0 0 0; 0 0 0]   # Systems are coupled by their first state variable.

# Construct model 
model = Model()

# Add components
for (i, component) in enumerate(components)
    addnode!(model, component, label=Symbol("node$i"))
end
addnode!(model, CouplerSystem(E=E, P=P), label=Symbol("coupler"))
addnode!(model, Writer(input=Inport(n * d)), label=Symbol("writer"))

# Add connections
m = n + 1
for (j, k) in zip(1:n, map(i -> i : i + d - 1, 1 : d : n * d))
    addbranch!(model, j => m, 1 : d => k)
    addbranch!(model, m => j, k => 1 : d)
end
p = n + 2
for (j, k) in zip(1:n, map(i -> i : i + d - 1, 1 : d : n * d))
    addbranch!(model, j => p, 1 : d => k)
end

# Simulate model 
sim = simulate!(model, 0, 0.001, 100.)

# Read and plot the simulation data 
t, x = read(getnode(model, :writer).component)

# Compute mean square error
mse = sqrt.(sum(diff(x[:, 1 : d : end],dims=2).^2/n, dims=2))

# Plot results
k = 3000 
plot(t, x[:, 1] , label="")
plot(x[:, 1], x[:,2], label="")
plot(t[1:k], mse[1:k], label="")
\end{lstlisting}

\end{document}

% Inspired by the International Journal of Computer Applications template

### 2021-04-25 paper/paper.tex
Reviewed article according to the comments by the reviewers.

@@
 
-\begin{figure}
-    \centering
-    \subfloat[]{\includegraphics[width=0.225\linewidth]{figures/Tasks/reader_task.pdf} \label{subfig: reader task}} \hfil 
-    \subfloat[]{\includegraphics[width=0.225\linewidth]{figures/Tasks/writer_task.pdf} \label{subfig: writer task}} \hfil 
-    \subfloat[]{\includegraphics[width=0.4\linewidth]{figures/Tasks/reader_writer_task.pdf} \label{subfig: reader writer task}} 
-    \caption{\protect\subref{subfig: reader task} A readable connection, \protect\subref{subfig: writer task} A writable connection, \protect\subref{subfig: reader writer task} A readable and writable connection}
-    \label{fig: tasks}
-\end{figure}
+% \begin{figure}
+%     \centering
+%     \subfloat[]{\includegraphics[width=0.225\linewidth]{figures/Tasks/reader_task.pdf} \label{subfig: reader task}} \hfil 
+%     \subfloat[]{\includegraphics[width=0.225\linewidth]{figures/Tasks/writer_task.pdf} \label{subfig: writer task}} \hfil 
+%     \subfloat[]{\includegraphics[width=0.4\linewidth]{figures/Tasks/reader_writer_task.pdf} \label{subfig: reader writer task}} 
+%     \caption{\protect\subref{subfig: reader task} A readable connection, \protect\subref{subfig: writer task} A writable connection, \protect\subref{subfig: reader writer task} A readable and writable connection}
+%     \label{fig: tasks}
+% \end{figure}
 
@@
 The data transfer through the connections is performed over the links of the connections.
-The links are built on top Julia channels.
+The links are built on top of unbuffered Julia channels.
 The data written to(read from) a link is written to(read from) its channel.
@@
 
-Figure \ref{fig: tasks} depicts the tasks that must be bound to a connection to make it readable, writable, and both readable and writable, symbolically.
+% Figure \ref{fig: tasks} depicts the tasks that must be bound to a connection to make it readable, writable, and both readable and writable, symbolically.
 The writer(the reader) task is the task that writes(reads) data to(from) the connection.
@@
 Otherwise, the simulation gets stuck and does not terminate.
+
+There exist other tools developed in Julia for parallel execution of computations.
+Dagger.jl is such an example of those tools \cite{dagger}.
+Dagger.jl distributes the computations that can be represented by a directed acyclic graph (DAG) to available worker processes to execute them in parallel.
+A DAG is a directed graph with no directed cycles (loops).
+The DAG modeling approach brings restrictions to the simulation of the models that include loops, which is a case commonly encountered e.g.
+in feedback control systems.
+However, Causal.jl is capable of simulating the systems that include loops in their models.
 
@@
 In Causal.jl, it is possible to simulate models that include components represented by different types of equations.
-In Figure \ref{fig: coupled model} is given such an example model.`odeds` is a dynamical system represented by the ordinary differential equation in (\ref{eq: coupled ode}) where where $x_1, y_1, z_1$ are the state variables and $a=35, b=3, c = 28$ are system parameters.
+In Figure \ref{fig: coupled model} is given such an example model.
+\texttt{odeds} is a dynamical system represented by the ordinary differential equation in (\ref{eq: coupled ode}) where where $x_1, y_1, z_1$ are the state variables and $a=35, b=3, c = 28$ are system parameters.
 \begin{equation}
@@
 \end{equation}
-`sdsds` is dynamical system that is represented by the stochastic differential equation in (\ref{eq: coupled sde}) where $x_2, y_2, z_2$ are the state variables, $u=[u_1,u_2, u_3]$ is the input, $\eta$ is noise strength, $W_t$ is the Wiener process corresponding to the noise and $a, b, c$ are the same as those in (\ref{eq: coupled ode}).
+\texttt{sdeds} is dynamical system that is represented by the stochastic differential equation in (\ref{eq: coupled sde}) where $x_2, y_2, z_2$ are the state variables, $u=[u_1,u_2, u_3]$ is the input, $\eta$ is noise strength, $W_t$ is the Wiener process corresponding to the noise and $a, b, c$ are the same as those in (\ref{eq: coupled ode}).
 \begin{equation}
@@
 \end{equation}
-`gain` is a static system whose input output relation is given in (\ref{eq: gain}) where $u, y, \epsilon$ are the input, output and gain coefficient of the system. 
+\texttt{gain} is a static system whose input output relation is given in (\ref{eq: gain}) where $u, y, \epsilon$ are the input, output and gain coefficient of the system. 
 \begin{equation}
@@
 \end{equation}
-`writer1` and `writer2` are used to record the outputs of `odeds` and `sdeds`, respectively, while `writer3` is used to record the fast Fourier transform(FFT) of the data flowing out of `odeds`\cite{proakis2004digital}.
+\texttt{writer1} and \texttt{writer2} are used to record the outputs of \texttt{odeds} and \texttt{sdeds}, respectively, while \texttt{writer3} is used to record the fast Fourier transform(FFT) of the data flowing out of \texttt{odeds}\cite{proakis2004digital}.
 
@@
 The program written using Causal.jl to construct and simulate the model in Figure \ref{fig: coupled model} is given in Listing \ref{lst: coupled codes}.
-The program first starts with the type definitions of the components `odeds`, `sdeds`, and `gain`, together with their fields' default values.
+The program first starts with the type definitions of the components \texttt{odeds}, \texttt{sdeds}, and \texttt{gain}, together with their fields' default values.
 Note that the types of components are defined as subtypes of the corresponding abstract component types, which shows how the user-defined component types can enrich the standard library of Causal.jl.
-`writer1` and `writer2` are used directly to record the data without further processing, so they do not need additional data processing plugins.
-On the other hand, rather than directly recording the data, `writer3` is used to process the data online, so it needs an additional plugin.
-`FFTPlug` is defined for this purpose, and `writer3` is equipped with an instance.
-For the sake of this example, we used the `fft` function \cite{fftw}.
-The model is constructed and simulated for $100$ seconds with a step size of $0.001$ seconds.
-After the simulation, the data in `write1` and `writer2` are read back and plotted in Figure \ref{fig: coupled simulation results}.
-From Figure \ref{subfig: coupled simulation sde}, the presence of the noise is apparent in the trajectory of `sdeds`.
+\texttt{writer1} and \texttt{writer2} are used directly to record the data without further processing, so they do not need additional data processing plugins.
+On the other hand, rather than directly recording the data, \texttt{writer3} is used to process the data online, so it needs an additional plugin.
+\texttt{FFTPlug} is defined for this purpose, and \texttt{writer3} is equipped with an instance.
+For the sake of this example, we used the \texttt{fft} function \cite{fftw}.
+The model is constructed and simulated for $15$ seconds with a step size of $0.001$ seconds.
+After the simulation, the data in \texttt{write1} and \texttt{writer2} are read back and plotted in Figure \ref{fig: coupled simulation results}.
+From Figure \ref{subfig: coupled simulation sde}, the presence of the noise is apparent in the trajectory of {\texttt{sdeds}.
 
@@
 Components that write data to a connection drives other components that read data from the same connection.
-Thus, the topological structure of a model can be extracted by following the components that read data from the connections bound to the output ports of model components.
+Thus, the dependency structure of a model can be extracted by following the components that read data from the connections bound to the output ports of model components.
 
@@
     }
-    \caption{\protect\subref{subfig: coupled simulation ode} $x_1 - y_1$ trajectory of `odeds`. \protect\subref{subfig: coupled simulation sde} $x_2 - y_2$ trajectory of `sdeds`.}
+    \caption{\protect\subref{subfig: coupled simulation ode} $x_1 - y_1$ trajectory of \texttt{odeds}. \protect\subref{subfig: coupled simulation sde} $x_2 - y_2$ trajectory of \texttt{sdeds}.}
     \label{fig: coupled simulation results}
@@
 \begin{equation}
-    \bm{u}_i = \sum_{i = 1}^n \epsilon_{ij} \bm{P} \bm{x}_j, \quad i = 1, \ldots, n,
+    \bm{u}_i = \sum_{i = 1}^n \epsilon_{ij} \bm{\Gamma} \bm{x}_j, \quad i = 1, \ldots, n,
     \label{eq: network node inputs}
@@
 $n$ is the number of nodes, $\bm{x}_i \in \mathbb{R}^d$ is the state vector of node $i$, $f: \mathbb{R} \mapsto \mathbb{R}^d$ is the function corresponding to the individual node dynamics, $\epsilon_{ij} \geq 0 $ is the coupling strength between the nodes $i$ and $j$.
-The diagonal matrix $\bm{P} = diag(p_1, \ldots, p_d)$ determines by which state variables the nodes are connected to each other.
+The diagonal matrix $\bm{\Gamma} = diag(\gamma_1, \gamma_2,  \ldots, \gamma_d)$ determines by which state variables the nodes are connected to each other.
 The matrix $\bm{E} = [\epsilon_{ij}] \in \mathbb{R}^{n, n}, \; \epsilon_{ij} = \epsilon_{ji} \geq 0, \; \sum_{j = 1}^n \epsilon_{ij} = 0, i = 1, \ldots, n$ determines the network topology: if $\epsilon_{ij} > 0$, there is a connection between the nodes $i$ and $j$, if $\epsilon_{ij} = 0$, there is no connection between the nodes $i$ and $j$.
@@
 \end{equation}
-where $\sigma=10, \beta=8/3, \rho=28$ are system parameters, $\bm{P} = diag(1, 0, 0)$.
+where $\sigma=10, \beta=8/3, \rho=28$ are system parameters, $\bm{\Gamma} = diag(1, 0, 0)$.
 The network has Wattz-Strogatz topology that has a vertex degree of $10$ and that is randomized with a probability of $0.5$\cite{watts1998collective}.
@@
     \centering
-    \includegraphics[width=0.5\linewidth]{figures/Networks/wattz_strogatz.pdf}    
-    \caption{A network consisting of identical dynamical system nodes The spheres and the line segments represent the dynamical system nodes and the connection between them, respectively.}
+    \includegraphics[width=\linewidth]{figures/Networks/wattz_strogatz.pdf}    
+    \caption{A network consisting of identical dynamical system nodes. The spheres and the line segments represent the dynamical system nodes and the connection between them, respectively.}
     \label{fig: network graph}
@@
 The model in Figure \ref{fig: network graph} is given in Figure \ref{fig: network model}.
-`node $k$` for $k =1, \ldots, n$ correspond to the dynamical system nodes of the network.
+\texttt{node $k$} for $k =1, \ldots, n$ correspond to the dynamical system nodes of the network.
 From (\ref{eq: network equation}) and (\ref{eq: network node inputs}), we see that the states of the nodes are taken as their outputs, weighted by the coupling strengths and fed back to their inputs.
-Hence, `coupler` is used to construct the weighted outputs.
-`writer` records the nodes' outputs.
-The model has algebraic loops $L_k$ for $k = 1, \ldots, n$, where the algebraic loop $L_k$ consists of `node $k$` and `coupler`.
+Hence, \texttt{coupler} is used to construct the weighted outputs.
+\texttt{writer} records the nodes' outputs.
+The model has algebraic loops $L_k$ for $k = 1, \ldots, n$, where the algebraic loop $L_k$ consists of \texttt{node $k$} and \texttt{coupler}.
 
@@
 # Simulate model 
-sim = simulate!(model, 0, 0.001, 100) # Simulate from 0 to 100 seconds with a step size of 0.001 seconds
+sim = simulate!(model, 0, 0.001, 15) # Simulate from 0 to 15 seconds with a step size of 0.001 seconds
 
@@
 x3 = read(getnode(model, :writer3).component, flatten=false)
-plot(x1[:, 1], x1[:, 2], subplot=1, label="")
-plot(x2[:, 1], x2[:, 2], subplot=2, label="")   
+plot(x1[:, 1], x1[:, 2])
+plot(x2[:, 1], x2[:, 2])   
 println(x3)  

### 2021-07-03 paper/paper.tex
Added answers2.

@@
 The generated triggers are put into the trigger pins of the components.
+
+It is possible for the users to determine the time instants at which the components are sampled.
+The user-specified sampling time instants can be regularly or irregularly spaced.
+However, although the sampling time instants are determined by the user, the solvers of the systems take adaptive steps while the systems evolve from one sampling instant to the next.
+Therefore, the sampling time instants determined by the user do not force the systems to evolve with the specified time intervals but to sample the outputs of the systems at those specified instants.
 

### 2021-07-03 paper/paper.tex
Added white space before left paranthesis.

@@
 For this purpose, Julia, an open-source, high level, general purpose dynamical programming language designed for high-performance numerical analysis and computational science, has been used.
-Although Julia is a dynamical language, owing to its Just-in-Time(JIT) compiler developed on Low Level Virtual Machine(LLVM), it can reach the high-speed performance of static languages such as C\cite{bezanson2017julia,julialang}.
+Although Julia is a dynamical language, owing to its Just-in-Time (JIT) compiler developed on Low Level Virtual Machine (LLVM), it can reach the high-speed performance of static languages such as C\cite{bezanson2017julia,julialang}.
 It supports various parallel computing techniques at thread and process levels.
@@
 $W$ is the stochastic process corresponding to the noise and $x_\tau$ is the state $x$ delayed by $\tau$ seconds in time.
-$f$(and $h$) is the right-hand-side function of the differential equation representing the system and $g$ is the readout function.}
+$f$ (and $h$) is the right-hand-side function of the differential equation representing the system and $g$ is the readout function.}
     \label{fig: component types}
@@
 When triggered, a dynamical system reads its input from its input port, updates its state according to the differential equation, calculates its output according to its readout function, and writes the result to its output port.
-Being developed on top of DifferentialEquations.jl, Causal.jl is capable of simulating the dynamical systems represented by differential equations in the form of the ordinary differential equations(ODE), differential-algebraic equations(DAE), random ordinary differential equations(RODE), stochastic differential equations(SDE), delay differential equations(DDE) or discrete difference equations \cite{rackauckas2017differentialequations}.
+Being developed on top of DifferentialEquations.jl, Causal.jl is capable of simulating the dynamical systems represented by differential equations in the form of the ordinary differential equations (ODE), differential-algebraic equations (DAE), random ordinary differential equations (RODE), stochastic differential equations (SDE), delay differential equations (DDE) or discrete difference equations \cite{rackauckas2017differentialequations}.
 Most of the available simulation environments allow the systems represented by ordinary differential equations or differential-algebraic equations\cite{elmqvist1978structured,nytsch2006advanced,zimmer2008introducing,mosterman2002hybrsim,van2001variables,giorgidze2009higher,pfeiffer2012pysimulator,simulink}.
@@
 The links are built on top of unbuffered Julia channels.
-The data written to(read from) a link is written to(read from) its channel.
+The data written to (read from) a link is written to (read from) its channel.
 Running Julia tasks bound to the channels must exist for the data to flow through these channels.
@@
 \end{equation}
-\texttt{writer1} and \texttt{writer2} are used to record the outputs of \texttt{odeds} and \texttt{sdeds}, respectively, while \texttt{writer3} is used to record the fast Fourier transform(FFT) of the data flowing out of \texttt{odeds}\cite{proakis2004digital}.
+\texttt{writer1} and \texttt{writer2} are used to record the outputs of \texttt{odeds} and \texttt{sdeds}, respectively, while \texttt{writer3} is used to record the fast Fourier transform (FFT) of the data flowing out of \texttt{odeds}\cite{proakis2004digital}.
 

### 2021-12-05 paper/paper.tex
Added doi.

@@
 \end{equation}
-\texttt{writer1} and \texttt{writer2} are used to record the outputs of \texttt{odeds} and \texttt{sdeds}, respectively, while \texttt{writer3} is used to record the fast Fourier transform (FFT) of the data flowing out of \texttt{odeds}\cite{proakis2004digital}.
+\texttt{writer1} and \texttt{writer2} are used to record the outputs of \texttt{odeds} and \texttt{sdeds}, respectively, while \texttt{writer3} is used to record the fast Fourier transform (FFT) of the data flowing out of \texttt{odeds}\cite{proakis2001digital}.
 

### 2022-01-29 paper/header.tex
Removed backslashes from the paper.yml file.

@@
 
-\title{Causal.jl:\\A Modeling and Simulation Framework for Causal Models}
+\title{Causal.jl: A Modeling and Simulation Framework for Causal Models}
 
@@
 \hypersetup{
-pdftitle = {Causal.jl:\\A Modeling and Simulation Framework for Causal Models},
+pdftitle = {Causal.jl: A Modeling and Simulation Framework for Causal Models},
 pdfsubject = {JuliaCon 2019 Proceedings},
